### 2020-03-11 manuscript/manuscript.tex
SoftwareX template added to manuscript folder

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt, a4paper]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}

\usepackage{float}
\restylefloat{table}

\journal{SoftwareX}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Title/Name of your software}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{A. Author}

\address{Your institute, some address}

\begin{abstract}
%% Text of abstract 
Ca. 100 words

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
keyword 1 \sep keyword 2 \sep keyword 3

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

\section*{Required Metadata}
\label{}

\section*{Current code version}
\label{}

Ancillary data table required for subversion of the codebase. Kindly replace examples in right column with the correct information about your current code, and leave the left column as it is.

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version & For example v42 \\
\hline
C2 & Permanent link to code/repository used for this code version & For example: $https://github.com/mozart/mozart2$ \\
\hline
C3 & Code Ocean compute capsule & For example: $https://codeocean.com/2017/07/30/neurospeech-colon-an-open-source-software-for-parkinson-apos-s-speech-analysis/code$\\
\hline
C4 & Legal Code License   & List one of the approved licenses \\
\hline
C5 & Code versioning system used & For example svn, git, mercurial, etc. put none if none \\
\hline
C6 & Software code languages, tools, and services used & For example C++, python, r, MPI, OpenCL, etc. \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & \\
\hline
C8 & If available Link to developer documentation/manual & For example: $http://mozart.github.io/documentation/$ \\
\hline
C9 & Support email for questions & \\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{} 
\end{table}

\linenumbers

%% main text

The permanent link to code/repository or the zip archive should include the following requirements:

README.txt and LICENSE.txt.

Source code in a src/ directory, not the root of the repository.

Tag corresponding with the version of the software that is reviewed.

Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.

\section{Motivation and significance}
\label{}

Introduce the scientific background and the motivation for developing the software. \cite{Lignell_2018}

Explain why the software is important, and describe the exact (scientific) problem(s) it solves.

Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.

Provide a description of the experimental setting (how does the user use the software?).

Introduce related work in literature (cite or list algorithms used, other software etc.).

\section{Software description}
\label{}

Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.

\subsection{Software Architecture}
\label{}

Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.

\subsection{Software Functionalities}
\label{}

Present the major functionalities of the software.

\subsection{Sample code snippets analysis (optional)}
\label{}

\section{Illustrative Examples}
\label{}

Provide at least one illustrative example to demonstrate the major functions.

Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel. (Please upload any video as a single supplementary file with your article. Only one MP4 formatted, with 50MB maximum size, video is possible per article. Recommended video dimensions are 640 x 480 at a maximum of 30 frames/second. Prior to submission please test and validate your .mp4 file at $ http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification$. This tool will display your video exactly in the same way as it will appear on ScienceDirect.).

\section{Impact}
\label{}

\textbf{This is the main section of the article and the reviewers weight the description here appropriately}

Indicate in what way new research questions can be pursued as a result of the software (if any).

Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).

Indicate in what way the software has changed the daily practice of its users (if so).

Indicate how widespread the use of the software is within and outside the intended user group.

Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).

\section{Conclusions}
\label{}

Set out the conclusion of this original software publication.

\section{Conflict of Interest}
Please select the appropriate text:

Potential conflict of interest exists:
We wish to draw the attention of the Editor to the following facts, which may be considered as potential conflicts of interest, and to significant financial contributions to this work. The nature of potential conflict of interest is described below: [Describe conflict of interest]

No conflict of interest exists:
We wish to confirm that there are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.

\section*{Acknowledgements}
\label{}

Optionally thank people and institutes you need to acknowledge.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References:
%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
\bibliographystyle{elsarticle-num} 
\bibliography{references}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

%\begin{thebibliography}{00}

%% \bibitem{label}
%% Text of bibliographic item

%\bibitem{}

%\end{thebibliography}
Please add the reference to the software repository if DOI for software is available.

\section*{Current executable software version}
\label{}

Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.

\begin{table}[!h]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{(Executable) software metadata description} & \textbf{Please fill in this column} \\
\hline
S1 & Current software version & For example 1.1, 2.4 etc. \\
\hline
S2 & Permanent link to executables of this version  & For example: $https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
\hline
S3 & Legal Software License & List one of the approved licenses \\
\hline
S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS, Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based etc. \\
\hline
S5 & Installation requirements \& dependencies & \\
\hline
S6 & If available, link to user manual - if formally published include a reference to the publication in the reference list & For example: $http://mozart.github.io/documentation/$ \\
\hline
S7 & Support email for questions & \\
\hline
\end{tabular}
\caption{Software metadata (optional)}
\label{} 
\end{table}

\end{document}
\endinput
%%
%% End of file `SoftwareX_article_template.tex'.

### 2020-03-21 manuscript/manuscript.tex
Starting to fill in template; metadata, title, authors, acknowledgements, etc.

@@
 
-\title{Title/Name of your software}
+\title{One-dimensional turbulence (ODT): computationally efficient modeling of turbulent reacting flows}
 
@@
 
-\author{A. Author}
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+\author{Victoria B. Stephens, David O. Lignell\footnote{Corresponding author.\\ \indent \textit{Email address}: davidlignell@byu.edu}}
 
-\address{Your institute, some address}
+\address{Department of Chemical Engineering, Brigham Young University, Provo, UT 84602, United States}
 
@@
 %% keywords here, in the form: keyword \sep keyword
-keyword 1 \sep keyword 2 \sep keyword 3
+turbulence \sep reacting flows \sep one-dimensional turbulence
 
@@
 \hline
-C1 & Current code version & For example v42 \\
+C1 & Current code version & 2.1 \\
 \hline
-C2 & Permanent link to code/repository used for this code version & For example: $https://github.com/mozart/mozart2$ \\
+C2 & Permanent link to code/repository used for this code version & $github.com/BYUignite/ODT$ \\
 \hline
-C3 & Code Ocean compute capsule & For example: $https://codeocean.com/2017/07/30/neurospeech-colon-an-open-source-software-for-parkinson-apos-s-speech-analysis/code$\\
+C3 & Code Ocean compute capsule & \\
 \hline
-C4 & Legal Code License   & List one of the approved licenses \\
+C4 & Legal Code License   & MIT license (MIT) \\
 \hline
-C5 & Code versioning system used & For example svn, git, mercurial, etc. put none if none \\
+C5 & Code versioning system used & Git \\
 \hline
-C6 & Software code languages, tools, and services used & For example C++, python, r, MPI, OpenCL, etc. \\
+C6 & Software code languages, tools, and services used & C++, Python 3 \\
 \hline
-C7 & Compilation requirements, operating environments \& dependencies & \\
+C7 & Compilation requirements, operating environments \& dependencies & CMake 3.12+, Cantera, Git, Doxygen (optional) \\
 \hline
-C8 & If available Link to developer documentation/manual & For example: $http://mozart.github.io/documentation/$ \\
+C8 & If available Link to developer documentation/manual &  \\
 \hline
-C9 & Support email for questions & \\
+C9 & Support email for questions & davidlignell@byu.edu \\
 \hline
@@
 The permanent link to code/repository or the zip archive should include the following requirements: 
-
-README.txt and LICENSE.txt.
-
-Source code in a src/ directory, not the root of the repository.
-
-Tag corresponding with the version of the software that is reviewed.
-
-Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
+\begin{itemize}
+	\item README.txt and LICENSE.txt.
+	\item Source code in a src/ directory, not the root of the repository.
+	\item TO DO: Tag corresponding with the version of the software that is reviewed.
+	\item TO DO: Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
+\end{itemize}
 
@@
 \section{Conflict of Interest}
-Please select the appropriate text:
-
-Potential conflict of interest exists:
-We wish to draw the attention of the Editor to the following facts, which may be considered as potential conflicts of interest, and to significant financial contributions to this work.
+%Please select the appropriate text:
+%
+%Potential conflict of interest exists:
+%We wish to draw the attention of the Editor to the following facts, which may be considered as potential conflicts of interest, and to significant financial contributions to this work.
 The nature of potential conflict of interest is described below: [Describe conflict of interest]
 
-No conflict of interest exists:
+%No conflict of interest exists:
 We wish to confirm that there are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.
@@
 
-Optionally thank people and institutes you need to acknowledge.
+This work was supported by the funding from the National Science Foundation under Grant Number CBET-1403403.
+
+Special thanks to Alan R.
+Kerstein for his significant contributions to model development.
+Additional thanks to Heiko Schmidt, Juan Medina, and Marten Klein of Brandenburg University of Technology Cottbus-Senftenberg, Michael Oevermann and Marco Fistler of Chalmers University of Technology, and Vladimir P.
+Solovjov of Brigham Young University.
 

### 2020-03-21 manuscript/manuscript.tex
Metadata and formatting updates

@@
 
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-\author{Victoria B. Stephens, David O. Lignell\footnote{Corresponding author.\\ \indent \textit{Email address}: davidlignell@byu.edu}}
+%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+\author{Victoria B. Stephens}
+\author{David O. Lignell\corref{cor1}}
+
+\cortext[cor1]{Corresponding author. \ead{davidlignell@byu.edu}}
 
@@
 %% References:
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
+
 \bibliographystyle{elsarticle-num} 
 \bibliography{references}
-
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
-
-%\begin{thebibliography}{00}
-
-%% \bibitem{label}
-%% Text of bibliographic item
-
-%\bibitem{}
-
-%\end{thebibliography}
-Please add the reference to the software repository if DOI for software is available.
 
@@
 \hline
-S1 & Current software version & For example 1.1, 2.4 etc. \\
+S1 & Current software version & 2.1 \\
 \hline
@@
 \hline
-S3 & Legal Software License & List one of the approved licenses \\
+S3 & Legal Software License & MIT license (MIT) \\
 \hline
-S4 & Computing platforms/Operating Systems & For example Android, BSD, iOS, Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based etc. \\
+S4 & Computing platforms/Operating Systems & Linux, OS X, Microsoft Windows\\
 \hline
-S5 & Installation requirements \& dependencies & \\
+S5 & Installation requirements \& dependencies & CMake 3.12+, Cantera, Git, Doxygen (optional) \\
 \hline
@@
 \hline
-S7 & Support email for questions & \\
+S7 & Support email for questions & davidlignell@byu.edu \\
 \hline
@@
 \endinput
-%%
-%% End of file `SoftwareX_article_template.tex'.

### 2020-04-07 manuscript/manuscript.tex
Brain dump draft. Not for general consumption. Contains copied/pasted text from elsewhere for reference.

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frontmatter}
@@
 
-\title{One-dimensional turbulence (ODT): computationally efficient modeling of turbulent reacting flows}
+\title{One-dimensional turbulence (ODT): computationally efficient modeling and simulation of turbulent reacting flows}
 
@@
 %\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-\author{Victoria B. Stephens}
-\author{David O. Lignell\corref{cor1}}
+\author[label1]{Victoria B. Stephens}
+\author[label2]{John C. Hewson}
+\author[label1]{David O. Lignell\corref{cor1}}
 
@@
 
-\address{Department of Chemical Engineering, Brigham Young University, Provo, UT 84602, United States}
+\address[label1]{Department of Chemical Engineering, Brigham Young University, Provo, UT 84602, USA}
+\address[label2]{Fire Science and Technology Department, Sandia National Laboratories, Albuquerque, NM, USA}
 
 \begin{abstract}
-%% Text of abstract 
-Ca. 100 words
-
+Write this last. About 100 words. 
 \end{abstract}
@@
 
-\section*{Required Metadata}
-\label{}
-
-\section*{Current code version}
-\label{}
-
-Ancillary data table required for subversion of the codebase. Kindly replace examples in right column with the correct information about your current code, and leave the left column as it is.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Code Metadata}
+\label{metadata}
 
@@
 \hline
-C3 & Code Ocean compute capsule & \\
+C3 & Code Ocean compute capsule & N/A\\
 \hline
-C4 & Legal Code License   & MIT license (MIT) \\
+C4 & Legal Code License   & MIT \\
 \hline
@@
 \hline
-C6 & Software code languages, tools, and services used & C++, Python 3 \\
+C6 & Software code languages, tools, and services used & C++, Python \\
 \hline
-C7 & Compilation requirements, operating environments \& dependencies & CMake 3.12+, Cantera, Git, Doxygen (optional) \\
+C7 & Compilation requirements, operating environments \& dependencies & CMake 3.12+, Cantera, Git, Python 3.x, Doxygen (optional) \\
 \hline
-C8 & If available Link to developer documentation/manual &  \\
+C8 & If available Link to developer documentation/manual & N/A \\
 \hline
-C9 & Support email for questions & davidlignell@byu.edu \\
+C9 & Support email for questions & davidlignellbyu.edu \\
 \hline
@@
 \caption{Code metadata (mandatory)}
-\label{} 
 \end{table}
@@
 
-%% main text
+%The permanent link to code/repository or the zip archive should include the following requirements: 
+%\begin{itemize}
+%	\item README.txt and LICENSE.txt.
+%	\item Source code in a src/ directory, not the root of the repository.
+%	\item TO DO: Tag corresponding with the version of the software that is reviewed.
+%	\item TO DO: Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
+%\end{itemize}
 
-The permanent link to code/repository or the zip archive should include the following requirements: 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Motivation and significance}
+\label{sec:motivation}
+
+Questions to answer in this section (from SoftwareX template)
+\begin{enumerate}
+	\item What's the scientific background and motivation for this software?
+	\item Why is this important? What problems does it solve?
+	\item How has the software contributed (and/or how will it contribute in the future) to the process of scientific discovery? Cite papers using the software.
+	\item In what experimental setting might someone use this software?
+	\item What related work is there in the literature?
+	\item What algorithms, other code/software, or ideas are used? Cite them. 
+\end{enumerate}
+
+Brain dump notes for this section
 \begin{itemize}
-	\item README.txt and LICENSE.txt.
-	\item Source code in a src/ directory, not the root of the repository.
-	\item TO DO: Tag corresponding with the version of the software that is reviewed.
-	\item TO DO: Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
+	\item TO DO MAYBE: divide into two subsections: (1) motivation/significance and (2) model history and development
 \end{itemize}
 
-\section{Motivation and significance}
-\label{}
+TEXT COPIED FROM CYLINDRICAL ODT PAPER
 
-Introduce the scientific background and the motivation for developing the software. \cite{Lignell_2018}
+The one-dimensional turbulence (ODT) model was introduced by Kerstein in 1999 \cite{Kerstein_1999}.
+ODT is computationally efficient because it only resolves flows in a single dimension.
+Turbulent advection is modeled through stochastic eddy events that are implemented by mapping processes on the domain using triplet maps.
+Eddy events occur concurrently with the solution of unsteady one-dimensional transport equations for momentum and other scalar quantities.
+A full range of turbulent length scales is modeled.
+Eddy event locations, sizes, and occurrence rates are specified dynamically and locally using the momentum fields that evolve with the flow; temperature or scalar fields are also used for buoyant flows.
+Because the model is one-dimensional, it is limited to homogeneous or boundary layer flows such as jets, wakes, mixing layers, and channel flows.
+These flows, however, are extremely common in turbulence research, and ODT's computational efficiency and resolution of a full range of scales make it a valuable tool that complements experimental and other simulation methods such as direct numerical simulation (DNS).
+Unlike ODT, DNS resolves all flow structures in three dimensions, but is computationally expensive.
+ODT is currently formulated for planar simulations, and the model can be run in temporal or spatial modes.
+In the temporal mode, the unsteady evolution equations evolve on a one-dimensional domain.
+In the spatial mode, the flow is assumed steady state (though punctuated with eddy events), and one-dimensional ODT line profiles evolve along a streamwise coordinate that replaces the time coordinate, as is done in steady boundary layer flows.
 
-Explain why the software is important, and describe the exact (scientific) problem(s) it solves.
+All of these simulated flows used the planar formulation of ODT, even when comparing to experiments of round jets.
+This comparison is reasonable for jets because the Reynolds number is axially invariant in both constant-property spatial round jets and constant-property temporal planar jets \cite{Sun_2017}.
+To compare temporal ODT simulations to spatial experimental simulations, however, time on the ODT line must be converted to the experimental axial spatial location.
+This is normally done using a mean line velocity (such as the ratio of the integrated momentum flux to the integrated mass flux) \cite{Sun_2017}, but this implies that all fluid parcels on the line have the same axial location time history.
+This assumption is not ideal for phenomena that are sensitive to time history, such as soot formation, flame extinction and reignition processes, and particle-turbulence interactions.
 
-Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.
+These limitations in applying the planar ODT formulation to cylindrical flows motivate the work presented here.
+In this paper, we extend the ODT model from the planar formulation to include cylindrical and spherical formulations.
+There have been some previous efforts to implement cylindrical and spherical ODT formulations.
+Krishnamoorthy \cite{Niveditha_thesis} implemented a cylindrical ODT formulation and applied the model in pipe and jet configurations.
+Lackmann et al.
+\cite{Lackmann_2017} implemented a spherical formulation of the linear eddy model (LEM) for engine applications.
+Here, we give a detailed description of cylindrical and spherical formulations of ODT.
+While the spherical formulation is included for completeness, we focus on the cylindrical formulation because it is most directly applicable to current and previous ODT research efforts.
+We defer to the literature for much of the existing ODT model formulation, e.g., \cite{Lignell_2013,Ashurst_2005,Kerstein_2001}, and focus on the new cylindrical and spherical geometries.
+For completeness, however, we include summary information of the ODT model formulation.
+We present results of the cylindrical formulation applied to pipe flow, a round nonreacting spatial jet, and a round jet flame.
+A more detailed study of round pipe flow than is possible in this paper is presented by Medina et al.
+\cite{Medina_2017}.
 
-Provide a description of the experimental setting (how does the user use the software?).
+TEXT COPIED FROM ABANDONED JOSS DRAFT
 
-Introduce related work in literature (cite or list algorithms used, other software etc.).
+The Stochastic Eddy Cascade (SEC) package is a set of models and tools used to simulate turbulent flow systems in which turbulence is modeled by stochastic processes that map so-called "eddy events" onto the domain.
+Most notably, SEC includes the most current implementation of the one-dimensional turbulence model (ODT), which has been successfully used to simulate turbulent reacting and nonreacting flows with high accuracy and relatively low computational cost.
+In addition to ODT, SEC also offers a flamelet model for combustion systems, which is useful for model validation and testing.
 
+Turbulent flows characterize the vast majority of fluid flows in practical engineering applications, and simulations of turbulent flows provide researchers with valuable insights into complex systems, particularly reacting turbulent flows such as combustion processes \cite{Pope2000}.
+Turbulence is a complex phemonenon that occurs over the full range of the flow's length and time scales.
+As a result, resolving the entire flow field by numerically solving the Navier-Stokes equations of fluid flow, as is done in direct numerical simulations (DNS), requires intense computational resources.
+DNS is a powerful research tool, but its high computational cost makes this approach intractable for most practical engineering flows.
+In order to achieve solutions to practical flow problems, turbulence is most often modeled.
+For example, large-eddy simulation (LES) approaches directly resolve large-scale flow structures but model small-scale motion, which often results in accurate, computationally efficient simulation data.
+Unfortunately, LES approaches can introduce empiricism into flow simulations, and errors can be difficult to isolate and quantify.
+The one-dimensional turbulence model (ODT) functionally reverses the LES approach, modeling large-scale turbulent advection (which is relatively well-understood) and directly resolving small-scale flow structures.
+In previous studies, ODT has been shown capable of attaining accuracy comparable to DNS at a fraction of the computational cost \cite{Lignell2015,Abboud2015}, making it an attractive model for simulating turbulent flows, particularly in combustion systems.
+
+ODT has been applied to a wide range of flows.
+Early applications focused on homogenous turbulence, wakes, and mixing layers (Kerstein1999,Kerstein2000,Kerstein2001).
+Later extension to variable-density flows and a spatial downstream coordinate system facilitated its growth and application to more complex flows, including combustion in jet flames (Echekki2001; Hewson2001; Hewson2002; Lignell2012; Punati2011; Abdelsamie2017; Lignell2017; Goshayeshi2015), counterflow flames  (Jozefik2015), wall fires (Monson2016), and sooting flames, (Lignell2015; Hewson2006; Hewson2009; Lignell2015b, Ricks2010), as well as other particle flows (Sun2017; Schmidt2009; Sun2014; Fistler2017).
+ODT has also served to complement LES through subgrid modeling studies (Cao2008; Schmidt2003; Schmidt2010) and has been applied to various other flow configurations such as double-diffusive interfaces (GonzalezJuez2011), Rayleigh-Taylor mixing (GonzalezJuez2013), and stratified turbulence (Wunsch2001).
+Most recently, the ODT code was extended to include cylindrical and spherical coordinate systems (Lignell2018; Klein2018; Klein2019).
+During this implementation, the ODT code was drastically overhauled, resulting in the SEC package presented here.
+Further detail on the current ODT model formulation and implementation can be found in the literature (Ashurst2005; Kerstein2001; Lignell2013; Lignell2018).
+
+Ongoing research involving ODT and SEC spans multiple research groups and subject areas.
+ODT is currently being used to investigate soot formation and destruction in ethylene jet flames via parametric modeling studies (Hewson2015; Lansinger2015b).
+The SEC package framework is also being used to develop the hierarchical parcel swapping model (HiPS), which models turbulence with an economical, hierarchical network that represents the fluid as individual parcels capable of switching positions within the tree (Kerstein2013; Kerstein2014).
+In the future, SEC may also be extended to include the linear eddy model (LEM) (Kerstein1991) and LES approaches.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Software description}
-\label{}
+\label{sec:description}
 
-Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.
+\subsection{Model description}
+\label{sub:model_description}
 
+Describe how ODT works here.
+Turbulent advection via eddy events implemented by triplet maps.
+Planar vs.
+cylindrical configurations.
+Eddy events happen concurrently with solution of transport equations.
+Evolution of transport equations in only one dimension.
+Limited to one-dimensional flows: jets, wakes, mixing layers.
+This is fine though because those are common in nature and important to research.
+
+TEXT COPIED FROM UNFINISHED CONFERENCE PAPER
+
+This study employs the most current version of the ODT code as in Lignell et.
+al.
+\cite{Lignell_2018}, and the ODT model in general is described in detail in the literature \cite{Lignell_2018,Lignell_2013,Kerstein_1999,Kerstein_2001,Ashurst_2005}.
+The ODT code uses a Lagrangian finite-volume formulation for diffusive advancement, including adaptive mesh refinement \cite{Lignell_2013}.
+In this approach, combustion dilation causes grid cells to increase or decrease in volume while mass remains constant within each cell.
+Turbulent advection is modeled with stochastic processes called "eddy events" that map functions on the domain via triplet maps.
+These eddy events occur concurrently with the solution of unsteady one-dimensional transport equations for mass, momentum, and enthalpy.
+In sooting flame cases, we also transport species mass fractions and soot particle size distribution properties.
+Because the ODT model is one-dimensional, it is limited to homogeneous or boundary-layer flows, such as jets, wakes, and mixing layers; these types of flows, however, are common in nature and central to turbulence research.
+
+ and whose sizes are drawn randomly from a sample distribution.
+A given eddy of size $l$ and location $x_0$ has an eddy timescale $t$ and an associated eddy rate $1=t$.
+Eddies occur as a Poisson process in accordance with their given rates.
+Three ODT parameters control the eddy event process: the eddy rate parameter $C$ scales the rate of occurrence of the eddies; the viscous penalty parameter $Z$ suppresses small eddies; and the large eddy suppression parameter $\beta$ constrains eddies such that they do not reach over the elapsed simulation time.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Software Architecture}
-\label{}
+\label{sub:architecture}
 
-Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
+Things to put in this section (from SoftwareX template)
+\begin{itemize}
+	\item overview of overall software architecture
+	\item optional: pictorial overview
+	\item implementation details
+	\begin{itemize}
+		\item software dependencies?
+		\item how to build and run (or leave this in the code README files? maybe brief description here with full details in README.)
+		\item how to use post processing tools? (TODO: prune post processing tools as much as possible so there's no excess)
+	\end{itemize}
+\end{itemize}
 
-\subsection{Software Functionalities}
-\label{}
+Summary of directory structure:
+\begin{itemize}
+	\item source: source code lives here; yaml files generated by building yaml in build folder get put here as well
+		\begin{itemize}
+			\item more details on directory structure necessary here? not sure if relevant
+		\end{itemize}
+	\item build: go here to build the code
+		\begin{itemize}
+			\item Run: make yaml (only need to do this once, the first time you download/build the code)
+			\item set options/paths for cmake in user\_config file
+			\item Run: cmake -C user\_config ../source
+			\item Run: make -j8
+		\end{itemize}
+	\item input: input files live here; change input files to specify case details
+		\begin{itemize}
+			\item each case type has its own folder; make your own if necessary
+			\item within each case folder, you should see file input.yaml. this is your all-important input file that makes each case unique
+			\begin{itemize}
+				\item talk about most important ODT parameters/options here? or leave to documentation?
+			\end{itemize}
+		\end{itemize}
+	\item run: go here to actually run the code; don't forget to make your changes to the input file first
+		\begin{itemize}
+			\item after building, you'll see odt.x in this folder. you can run it directly (not recommended) or from within one of the bash scripts (better)
+			\item don't forget to give your case a name; this name will be used to label data files dumped to the data directory
+		\end{itemize}
+	\item data: data and runtime files dumped here, organized by case name and individual realizations
+		\begin{itemize}
+			\item TO DO: raw/processed file types and what they contain, how to use them effectively
+		\end{itemize}
+	\item post: post processing tools located here, organized by case type
+	\item doc: doxygen documentation (if generated) lives here
+
+\end{itemize}
+
+%Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Software Functionalities and Example Cases}
+\label{sec:examples}
 
 Present the major functionalities of the software. 
+\begin{itemize}
+	\item simulating turbulent flow cases, reacting or nonreacting flows
+	\item can simulate laminar flow cases too
+	\item does these things a whole lot faster than other methods do (LES, DNS especially)
+	\item testing LES subgrid modeling assumptions
+	\item simulating cases that DNS can't get to because needed simulation length is too long (i.e. late-flame phenomena)
+\end{itemize}
 
-\subsection{Sample code snippets analysis (optional)}
-\label{}
+Example cases:
+\begin{itemize}
+	\item From cylindrical ODT paper:
+	\begin{enumerate}
+		\item pipe flow
+		\item nonreacting round jet
+		\item round jet flame
+	\end{enumerate}
+	\item Other possible example cases:
+	\begin{itemize}
+		\item something to compare with DNS/LES results to illustrate efficiency
+		\item no sooting cases since no soot in the code
+		\item planar vs. cylindrical comparison
+	\end{itemize}
+\end{itemize}
 
-\section{Illustrative Examples}
-\label{}
+Things to talk about with example cases:
+\begin{itemize}
+	\item compare to DNS/LES cases; computational efficiency, accuracy
+	\item how data looks before post processing, how post processing works
+\end{itemize}
 
-Provide at least one illustrative example to demonstrate the major functions.
+Future functionalities here?
+\begin{itemize}
+	\item soot stuff
+	\item radiation models
+	\item easier switching between chemistry models?
+\end{itemize}
 
-Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel.
+%\subsection{Sample code snippets analysis (optional)}
+
+%Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel.
 (Please upload any video as a single supplementary file with your article.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Impact}
-\label{}
+\label{sec:impact}
 
-\textbf{This is the main section of the article and the reviewers weight the description here appropriately}
+Questions to answer in this section (from SoftwareX template)
+\begin{enumerate}
+	\item How can new research questions be pursued with this software?
+		\begin{itemize}
+			\item possibility of parametric studies (much harder with DNS/LES/RANS)
+			\item study of late-flame soot and radiation interactions, soot emissions as smoke
+			\item comparative radiation model studies?
+		\end{itemize}
+	\item How does the software improve pursuit of existing research questions?
+		\begin{itemize}
+			\item late-flame behavior becomes easier to study
+			\item validation of LES subgrid models
+			\item soot stuff, especially late in the flame (because soot moves slowly compared to gas species and therefore short simulation times like in DNS aren't enough to study it effectively)
+		\end{itemize}
+	\item How does the software change the daily practice of its users?
+		\begin{itemize}
+			\item cases take hours or days rather than weeks using supercomputer resources
+			\item test cases can be run on local computers (unlike something like DNS) and as background tasks without disrupting other tasks
+			\item ODT as a tool complements other approaches, can cover blind spots and be used in validation
+		\end{itemize}
+	\item How widespread is the software? Who uses it? (Within and outside of intended research area and/or group.)
+		\begin{itemize}
+			\item BYU group
+			\item JCH at Sandia
+			\item Chalmers group in Sweden (Marco Fistler, etc.)
+			\item German university group (Heiko Schmidt, Juan Media, Marten Klein, etc.)
+			\item TO DO: find other groups who have used or currently use ODT
+		\end{itemize}
+	\item How is the software used in commercial settings (if any)? Has it led to creation of spin-off companies?
+		\begin{itemize}
+			\item No commercial use (I think). 
+		\end{itemize}
+\end{enumerate}
 
-Indicate in what way new research questions can be pursued as a result of the software (if any).
+COPIED/PASTED FROM CYLINDRICAL ODT PAPER
+ODT has been applied by a number of researchers to a wide range of flows.
+These include homogeneous turbulence \cite{Kerstein_1999,Sun_2014}, wakes \cite{Kerstein_2000}, mixing layers \cite{Kerstein_1999,Kerstein_2001,Ashurst_2003,Ashurst_2005}, stratified flows \cite{Wunsch_2001}, Rayleigh-Benard flows \cite{Wunsch_2005}, buoyant wall flows \cite{Dreeben_2000,Shihn_2007}, and channel flows \cite{Schmidt_2009,Schmidt_2003,Lignell_2013}.
+Schmidt et al.
+\cite{Schmidt_2013} studied buoyantly-driven cloud-top entrainment with comparisons to water tank experiments.
+Gonzalez-Juez et al.
+\cite{Esteban_2013} studied reactive Rayleigh-Taylor mixing.
+A number of ODT simulations of turbulent jet flames have been performed \cite{Echekki_2001,Hewson_2001,Hewson_2002,Punati_2011,Lignell_2012b,Lignell_2015}.
+Other combustion applications include wall fires \cite{Monson_2016,Shihn_2004}, buoyant pool fires \cite{Ricks_2010,Hewson_2006,Hewson_2009}, and opposed jet flames \cite{Jozefik_2015}.
+Several studies used DNS to validate ODT for combustion in temporal planar jets \cite{Punati_2011,Lignell_2012b,Lignell_2015}.
+ODT has also been applied as a subgrid model for large eddy simulations (LES) \cite{Cao_2008,Schmidt_2003,Schmidt_2010} and in particle dynamics simulations in channel flows \cite{Schmidt_2009}, homogeneous turbulence \cite{Sun_2014}, and jets \cite{Sun_2017,Goshayeshi_2015}.
 
-Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
+Brain dump stuff to include here:
+\begin{itemize}
+	\item future functionalities and plans go here instead of last section?
+\end{itemize}
 
-Indicate in what way the software has changed the daily practice of its users (if so).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+\label{sec:conclusion}
 
-Indicate how widespread the use of the software is within and outside the intended user group.
+Write this part next to last
+%Set out the conclusion of this original software publication.
 
-Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).
-
-\section{Conclusions}
-\label{}
-
-Set out the conclusion of this original software publication.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conflict of Interest}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Acknowledgements}
-\label{}
+\label{acknoledgements}
 
-This work was supported by the funding from the National Science Foundation under Grant Number CBET-1403403.
+This work is supported in part by the National Science Foundation under Grant No. CBET-1403403
+and in part by the Sandia National Laboratories Advanced Simulation and Computing Physics and
+Engineering Models program. Sandia National Laboratories is a multi-program laboratory
+managed and operated by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
+Corporation, for the U.S. Department of Energy’s National Nuclear Security Administration
+under contract DE-AC04-94AL85000.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% The Appendices part is started with the command \appendix;
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% References:
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Current executable software version}
-\label{}
+\label{software_version}
 
@@
 \caption{Software metadata (optional)}
-\label{} 
 \end{table}

### 2020-04-24 manuscript/manuscript.tex
Motivation section drafted. Metadata updated.

--- 2020-03-21 manuscript/manuscript.tex
@@
 
-\title{One-dimensional turbulence (ODT): computationally efficient modeling of turbulent reacting flows}
+\title{One-dimensional turbulence (ODT): computationally efficient modeling and simulation of turbulent  flows}
 
@@
 
-\address{Department of Chemical Engineering, Brigham Young University, Provo, UT 84602, United States}
+\address{Chemical Engineering Department, Brigham Young University, Provo, UT 84602, USA}
 
 \begin{abstract}
-%% Text of abstract 
-Ca. 100 words
-
+Write this last. About 100 words. 
 \end{abstract}
@@
 \hline
-C1 & Current code version & 2.1 \\
+C1 & Current code version & 1.0 \\
 \hline
@@
 \hline
-C6 & Software code languages, tools, and services used & C++, Python 3 \\
+C6 & Software code languages, tools, and services used & C++, Python 3.x, Yaml,  \\
 \hline
@@
 \hline
-C8 & If available Link to developer documentation/manual &  \\
+C8 & If available Link to developer documentation/manual & N/A \\
 \hline
-C9 & Support email for questions & davidlignell@byu.edu \\
+C9 & Support email for questions & davidlignellbyu.edu \\
 \hline
@@
 
-%% main text
+%The permanent link to code/repository or the zip archive should include the following requirements: 
+%\begin{itemize}
+%	\item README.txt and LICENSE.txt.
+%	\item Source code in a src/ directory, not the root of the repository.
+%	\item TO DO: Tag corresponding with the version of the software that is reviewed.
+%	\item TO DO: Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
+%\end{itemize}
 
-The permanent link to code/repository or the zip archive should include the following requirements: 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Motivation and significance}
+\label{sec:motivation}
+
+Turbulent flows characterize the vast majority of fluid flows in practical engineering applications, and simulations of turbulent flows provide researchers with valuable insights into complex systems, particularly reacting turbulent flows such as combustion processes.
+Turbulence is a complex phemonenon that affects the full range of a flow's length and time scales.
+As a result, resolving the entire flow field by numerically solving the Navier-Stokes equations of fluid flow, as is done in direct numerical simulations (DNS), requires substantial computational resources.
+DNS is a powerful research tool, but its high computational cost makes it intractable for simulating most practical engineering flows.
+In order to achieve numerical solutions to practical flow problems, researchers can use alternative frameworks that model turbulence rather than resolving it directly.
+
+Large-eddy simulations (LES) address the problem of wide-ranging length and time scales by combining  direct resolution of grid-scale quantities, as in DNS, with subgrid modeling of smaller turbulence structures.
+The more complex the flow, the more modeling is required; for example, a jet flame simulation might require subgrid modeling for the combustion chemistry, radiative heat transfer, or soot chemistry in addition to turbulence structures, all of which form a tightly coupled system in which each model interacts heavily with the others.
+While subgrid modeling makes LES more computationally affordable than DNS, it can introduce empiricism into simulations, which can lead to inaccurate results.
+Additionally, unresolved quantities are often parameterized in state space with empirical relationships or assumed distributions that lack universal applicability.
+LES is a valuable simulation tool, but its approach to turbulence modeling can introduce unwanted empiricism and make errors difficult to isolate and quantify.
+
+The one-dimensional turbulence model (ODT) functionally reverses the LES approach, modeling large-scale turbulent advection and directly resolving small-scale flow structures, simulating the full range of length and time scales in a single dimension.
+Because large-scale structures are much easier to study and model than small-scale structures, ODT mitigates or sidesteps many of the subgrid modeling issues that complicate LES.
+Previous studies show that ODT can attain accuracy comparable to DNS at a fraction of the computational cost \cite{Lignell_2015,Abboud_2015}, making it an attractive tool for simulating turbulent flows.
+Because the model is one-dimensional, it is limited to homogeneous or boundary layer flows such as jets, wakes, and mixing layers; such flows, however, are extremely common in both nature and turbulence research.
+ODT's computational efficiency and resolution of a full range of scales make it a valuable tool that complements experimental studies and other simulation tools like DNS and LES.
+
+%
+%Questions to answer in this section (from SoftwareX template)
+%\begin{enumerate}
+%	\item What's the scientific background and motivation for this software?
+%	\item Why is this important? What problems does it solve?
+%	\item How has the software contributed (and/or how will it contribute in the future) to the process of scientific discovery? Cite papers using the software.
+%	\item In what experimental setting might someone use this software?
+%	\item What related work is there in the literature?
+%	\item What algorithms, other code/software, or ideas are used? Cite them. 
+%\end{enumerate}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Software description}
+\label{sec:description}
+
+\subsection{Model description}
+\label{sub:model_description}
+
+Describe how ODT works here.
+Turbulent advection via eddy events implemented by triplet maps.
+Planar vs.
+cylindrical configurations.
+Eddy events happen concurrently with solution of transport equations.
+Evolution of transport equations in only one dimension.
+Limited to one-dimensional flows: jets, wakes, mixing layers.
+This is fine though because those are common in nature and important to research.
+
+%TEXT COPIED FROM UNFINISHED CONFERENCE PAPER
+%
+%This study employs the most current version of the ODT code as in Lignell et.
+al.
+\cite{Lignell_2018}, and the ODT model in general is described in detail in the literature \cite{Lignell_2018,Lignell_2013,Kerstein_1999,Kerstein_2001,Ashurst_2005}.
+%The ODT code uses a Lagrangian finite-volume formulation for diffusive advancement, including adaptive mesh refinement \cite{Lignell_2013}.
+In this approach, combustion dilation causes grid cells to increase or decrease in volume while mass remains constant within each cell.
+%Turbulent advection is modeled with stochastic processes called "eddy events" that map functions on the domain via triplet maps.
+These eddy events occur concurrently with the solution of unsteady one-dimensional transport equations for mass, momentum, and enthalpy.
+In sooting flame cases, we also transport species mass fractions and soot particle size distribution properties.
+Because the ODT model is one-dimensional, it is limited to homogeneous or boundary-layer flows, such as jets, wakes, and mixing layers; these types of flows, however, are common in nature and central to turbulence research.
+%
+% and whose sizes are drawn randomly from a sample distribution.
+A given eddy of size $l$ and location $x_0$ has an eddy timescale $t$ and an associated eddy rate $1=t$.
+Eddies occur as a Poisson process in accordance with their given rates.
+Three ODT parameters control the eddy event process: the eddy rate parameter $C$ scales the rate of occurrence of the eddies; the viscous penalty parameter $Z$ suppresses small eddies; and the large eddy suppression parameter $\beta$ constrains eddies such that they do not reach over the elapsed simulation time.
+
+%-----------------------------------------------------------------------------------
+\subsection{Software Architecture}
+\label{sub:architecture}
+
+Things to put in this section (from SoftwareX template)
 \begin{itemize}
-	\item README.txt and LICENSE.txt.
-	\item Source code in a src/ directory, not the root of the repository.
-	\item TO DO: Tag corresponding with the version of the software that is reviewed.
-	\item TO DO: Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
+	\item overview of overall software architecture
+	\item optional: pictorial overview
+	\item implementation details
+	\begin{itemize}
+		\item software dependencies?
+		\item how to build and run (or leave this in the code README files? maybe brief description here with full details in README.)
+		\item how to use post processing tools? (TODO: prune post processing tools as much as possible so there's no excess)
+	\end{itemize}
 \end{itemize}
 
-\section{Motivation and significance}
-\label{}
+Summary of directory structure:
+\begin{itemize}
+	\item source: source code lives here; yaml files generated by building yaml in build folder get put here as well
+		\begin{itemize}
+			\item more details on directory structure necessary here? not sure if relevant
+		\end{itemize}
+	\item build: go here to build the code
+		\begin{itemize}
+			\item Run: make yaml (only need to do this once, the first time you download/build the code)
+			\item set options/paths for cmake in user\_config file
+			\item Run: cmake -C user\_config ../source
+			\item Run: make -j8
+		\end{itemize}
+	\item input: input files live here; change input files to specify case details
+		\begin{itemize}
+			\item each case type has its own folder; make your own if necessary
+			\item within each case folder, you should see file input.yaml. this is your all-important input file that makes each case unique
+			\begin{itemize}
+				\item talk about most important ODT parameters/options here? or leave to documentation?
+			\end{itemize}
+		\end{itemize}
+	\item run: go here to actually run the code; don't forget to make your changes to the input file first
+		\begin{itemize}
+			\item after building, you'll see odt.x in this folder. you can run it directly (not recommended) or from within one of the bash scripts (better)
+			\item don't forget to give your case a name; this name will be used to label data files dumped to the data directory
+		\end{itemize}
+	\item data: data and runtime files dumped here, organized by case name and individual realizations
+		\begin{itemize}
+			\item TO DO: raw/processed file types and what they contain, how to use them effectively
+		\end{itemize}
+	\item post: post processing tools located here, organized by case type
+	\item doc: doxygen documentation (if generated) lives here
 
-Introduce the scientific background and the motivation for developing the software. \cite{Lignell_2018}
+\end{itemize}
 
-Explain why the software is important, and describe the exact (scientific) problem(s) it solves.
+%Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
 
-Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.
-
-Provide a description of the experimental setting (how does the user use the software?).
-
-Introduce related work in literature (cite or list algorithms used, other software etc.).
-
-\section{Software description}
-\label{}
-
-Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.
-
-\subsection{Software Architecture}
-\label{}
-
-Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
-
-\subsection{Software Functionalities}
-\label{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Example Cases}
+\label{sec:examples}
 
 Present the major functionalities of the software. 
+\begin{itemize}
+	\item simulating turbulent flow cases, reacting or nonreacting flows
+	\item can simulate laminar flow cases too
+	\item does these things a whole lot faster than other methods do (LES, DNS especially)
+	\item testing LES subgrid modeling assumptions
+	\item simulating cases that DNS can't get to because needed simulation length is too long (i.e. late-flame phenomena)
+\end{itemize}
 
-\subsection{Sample code snippets analysis (optional)}
-\label{}
+Example cases:
+\begin{itemize}
+	\item From cylindrical ODT paper:
+	\begin{enumerate}
+		\item pipe flow
+		\item nonreacting round jet
+		\item round jet flame
+	\end{enumerate}
+	\item Other possible example cases:
+	\begin{itemize}
+		\item something to compare with DNS/LES results to illustrate efficiency
+		\item no sooting cases since no soot in the code
+		\item planar vs. cylindrical comparison
+	\end{itemize}
+\end{itemize}
 
-\section{Illustrative Examples}
-\label{}
+Things to talk about with example cases:
+\begin{itemize}
+	\item compare to DNS/LES cases; computational efficiency, accuracy
+	\item how data looks before post processing, how post processing works
+\end{itemize}
 
-Provide at least one illustrative example to demonstrate the major functions.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Impact}
+\label{sec:impact}
 
-Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel.
-(Please upload any video as a single supplementary file with your article.
-Only one MP4 formatted, with 50MB maximum size, video is possible per article.
-Recommended video dimensions are 640 x 480 at a maximum of 30 frames/second.
-Prior to submission please test and validate your .mp4 file at $ http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification$.
-This tool will display your video exactly in the same way as it will appear on ScienceDirect.).
+Questions to answer in this section (from SoftwareX template)
+\begin{enumerate}
+	\item How can new research questions be pursued with this software?
+		\begin{itemize}
+			\item possibility of parametric studies (much harder with DNS/LES/RANS)
+			\item study of late-flame soot and radiation interactions, soot emissions as smoke
+			\item comparative radiation model studies?
+		\end{itemize}
+	\item How does the software improve pursuit of existing research questions?
+		\begin{itemize}
+			\item late-flame behavior becomes easier to study
+			\item validation of LES subgrid models
+			\item soot stuff, especially late in the flame (because soot moves slowly compared to gas species and therefore short simulation times like in DNS aren't enough to study it effectively)
+		\end{itemize}
+	\item How does the software change the daily practice of its users?
+		\begin{itemize}
+			\item cases take hours or days rather than weeks using supercomputer resources
+			\item test cases can be run on local computers (unlike something like DNS) and as background tasks without disrupting other tasks
+			\item ODT as a tool complements other approaches, can cover blind spots and be used in validation
+		\end{itemize}
+	\item How widespread is the software? Who uses it? (Within and outside of intended research area and/or group.)
+		\begin{itemize}
+			\item BYU group
+			\item JCH at Sandia
+			\item Chalmers group in Sweden (Marco Fistler, etc.)
+			\item German university group (Heiko Schmidt, Juan Media, Marten Klein, etc.)
+			\item TO DO: find other groups who have used or currently use ODT
+		\end{itemize}
+	\item How is the software used in commercial settings (if any)? Has it led to creation of spin-off companies?
+		\begin{itemize}
+			\item No commercial use (I think). 
+		\end{itemize}
+\end{enumerate}
 
-\section{Impact}
-\label{}
+%COPIED/PASTED FROM CYLINDRICAL ODT PAPER
+%ODT has been applied by a number of researchers to a wide range of flows.
+These include homogeneous turbulence \cite{Kerstein_1999,Sun_2014}, wakes \cite{Kerstein_2000}, mixing layers \cite{Kerstein_1999,Kerstein_2001,Ashurst_2003,Ashurst_2005}, stratified flows \cite{Wunsch_2001}, Rayleigh-Benard flows \cite{Wunsch_2005}, buoyant wall flows \cite{Dreeben_2000,Shihn_2007}, and channel flows \cite{Schmidt_2009,Schmidt_2003,Lignell_2013}.
+Schmidt et al.
+\cite{Schmidt_2013} studied buoyantly-driven cloud-top entrainment with comparisons to water tank experiments.
+Gonzalez-Juez et al.
+\cite{Esteban_2013} studied reactive Rayleigh-Taylor mixing.
+A number of ODT simulations of turbulent jet flames have been performed \cite{Echekki_2001,Hewson_2001,Hewson_2002,Punati_2011,Lignell_2012b,Lignell_2015}.
+Other combustion applications include wall fires \cite{Monson_2016,Shihn_2004}, buoyant pool fires \cite{Ricks_2010,Hewson_2006,Hewson_2009}, and opposed jet flames \cite{Jozefik_2015}.
+Several studies used DNS to validate ODT for combustion in temporal planar jets \cite{Punati_2011,Lignell_2012b,Lignell_2015}.
+ODT has also been applied as a subgrid model for large eddy simulations (LES) \cite{Cao_2008,Schmidt_2003,Schmidt_2010} and in particle dynamics simulations in channel flows \cite{Schmidt_2009}, homogeneous turbulence \cite{Sun_2014}, and jets \cite{Sun_2017,Goshayeshi_2015}.
 
-\textbf{This is the main section of the article and the reviewers weight the description here appropriately}
+%TEXT COPIED FROM ABANDONED JOSS DRAFT
 
-Indicate in what way new research questions can be pursued as a result of the software (if any).
+%ODT has been applied to a wide range of flows.
+Early applications focused on homogenous turbulence, wakes, and mixing layers (Kerstein1999,Kerstein2000,Kerstein2001).
+Later extension to variable-density flows and a spatial downstream coordinate system facilitated its growth and application to more complex flows, including combustion in jet flames (Echekki2001; Hewson2001; Hewson2002; Lignell2012; Punati2011; Abdelsamie2017; Lignell2017; Goshayeshi2015), counterflow flames  (Jozefik2015), wall fires (Monson2016), and sooting flames, (Lignell2015; Hewson2006; Hewson2009; Lignell2015b, Ricks2010), as well as other particle flows (Sun2017; Schmidt2009; Sun2014; Fistler2017).
+ODT has also served to complement LES through subgrid modeling studies (Cao2008; Schmidt2003; Schmidt2010) and has been applied to various other flow configurations such as double-diffusive interfaces (GonzalezJuez2011), Rayleigh-Taylor mixing (GonzalezJuez2013), and stratified turbulence (Wunsch2001).
+Most recently, the ODT code was extended to include cylindrical and spherical coordinate systems (Lignell2018; Klein2018; Klein2019).
+During this implementation, the ODT code was drastically overhauled, resulting in the SEC package presented here.
+Further detail on the current ODT model formulation and implementation can be found in the literature (Ashurst2005; Kerstein2001; Lignell2013; Lignell2018).
 
-Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
+%Ongoing research involving ODT and SEC spans multiple research groups and subject areas.
+ODT is currently being used to investigate soot formation and destruction in ethylene jet flames via parametric modeling studies (Hewson2015; Lansinger2015b).
+The SEC package framework is also being used to develop the hierarchical parcel swapping model (HiPS), which models turbulence with an economical, hierarchical network that represents the fluid as individual parcels capable of switching positions within the tree (Kerstein2013; Kerstein2014).
+In the future, SEC may also be extended to include the linear eddy model (LEM) (Kerstein1991) and LES approaches.
 
-Indicate in what way the software has changed the daily practice of its users (if so).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+\label{sec:conclusion}
 
-Indicate how widespread the use of the software is within and outside the intended user group.
+Write this part next to last
+%Set out the conclusion of this original software publication.
 
-Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).
-
-\section{Conclusions}
-\label{}
-
-Set out the conclusion of this original software publication.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conflict of Interest}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Acknowledgements}
-\label{}
+\label{acknoledgements}
 
-This work was supported by the funding from the National Science Foundation under Grant Number CBET-1403403.
+This work is supported in part by the National Science Foundation under Grant No. CBET-1403403.
 
-Special thanks to Alan R.
+%Special thanks to Alan R.
 Kerstein for his significant contributions to model development.
@@
 \hline
-S3 & Legal Software License & MIT license (MIT) \\
+S3 & Legal Software License & MIT \\
 \hline

### 2020-04-27 manuscript/manuscript.tex
Drafted model description section, started software architechture section, outlining impact section. Added triplet map figure.

@@
 
-%
 %Questions to answer in this section (from SoftwareX template)
@@
 
-Describe how ODT works here.
-Turbulent advection via eddy events implemented by triplet maps.
-Planar vs.
-cylindrical configurations.
-Eddy events happen concurrently with solution of transport equations.
-Evolution of transport equations in only one dimension.
-Limited to one-dimensional flows: jets, wakes, mixing layers.
-This is fine though because those are common in nature and important to research.
+The ODT model is described in detail in the literature \cite{Kerstein_1999,Kerstein_2001,Ashurst_2005,Lignell_2018,Lignell_2013}; only a brief explanation will be given here.
+In ODT, turbulent advection is modeled with stochastic processes called eddy events, which punctuate the solution of unsteady, one-dimensional transport equations for mass, momentum, and enthalpy.
+The ODT code uses a Lagrangian finite-volume formulation for diffusive advancement that includes adaptive mesh refinement \cite{Lignell_2013}.
+In this approach, mass remains constant inside each grid cell while cell volumes increase or decrease according to dilation.
+Because the ODT model is one-dimensional, it is limited to homogeneous or boundary-layer flows, such as jets, wakes, and mixing layers; these types of flows, however, are common in nature and central to turbulence research.
 
-%TEXT COPIED FROM UNFINISHED CONFERENCE PAPER
-%
-%This study employs the most current version of the ODT code as in Lignell et.
-al.
-\cite{Lignell_2018}, and the ODT model in general is described in detail in the literature \cite{Lignell_2018,Lignell_2013,Kerstein_1999,Kerstein_2001,Ashurst_2005}.
-%The ODT code uses a Lagrangian finite-volume formulation for diffusive advancement, including adaptive mesh refinement \cite{Lignell_2013}.
-In this approach, combustion dilation causes grid cells to increase or decrease in volume while mass remains constant within each cell.
-%Turbulent advection is modeled with stochastic processes called "eddy events" that map functions on the domain via triplet maps.
-These eddy events occur concurrently with the solution of unsteady one-dimensional transport equations for mass, momentum, and enthalpy.
-In sooting flame cases, we also transport species mass fractions and soot particle size distribution properties.
-Because the ODT model is one-dimensional, it is limited to homogeneous or boundary-layer flows, such as jets, wakes, and mixing layers; these types of flows, however, are common in nature and central to turbulence research.
-%
-% and whose sizes are drawn randomly from a sample distribution.
-A given eddy of size $l$ and location $x_0$ has an eddy timescale $t$ and an associated eddy rate $1=t$.
-Eddies occur as a Poisson process in accordance with their given rates.
-Three ODT parameters control the eddy event process: the eddy rate parameter $C$ scales the rate of occurrence of the eddies; the viscous penalty parameter $Z$ suppresses small eddies; and the large eddy suppression parameter $\beta$ constrains eddies such that they do not reach over the elapsed simulation time.
+Eddy events occur as a Poisson process in accordance with their eddy rates, where a given eddy event of size $l$ and location $x_0$ has an eddy timescale $t$ and an associated eddy rate $1/t$.
+Three user-defined ODT parameters control the eddy event process: the eddy rate parameter $C$ scales the rate of occurrence of the eddies; the viscous penalty parameter $Z$ suppresses small eddies; and the large eddy suppression parameter $\beta$ constrains eddies such that they do not reach over the elapsed simulation time.
+
+Eddy events modify domain variables using triplet maps, as illustrated for a cylindrical domain in Figure \ref{fig:tripletmap}.
+For a region of eddy size $l$, the domain is copied to create three map images; the three images are then placed back to back with the middle image inverted to maintain continuity, and the composite is reapplied to the domain.
+This process applies to all transported variables on the domain.
+Applied properly, the triplet map increases scalar gradients and decreases length scales consistent with the application of turbulent eddies in real flows, conserves all quantities and their statistical moments, and maintains continuity in property profiles.
+Subsequent eddies in the same region will result in a cascade of scales, and eddy rates depend on eddy size and the local kinetic energy such that they follow turbulent cascade scaling laws.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../figures/tripletmap/tripletmap.png} 
+	\caption{Schematic diagram of a cylindrical triplet map, adapted from \cite{Lignell_2018}.
+Before the triplet map, the domain contains three grid cells of equal volume, while after the triplet map has been applied, the domain contains nine cells.
+The nine final cells are labeled according to the cells from which they originated and shaded to indicate that three map images were combined to create the final composite.}
+	\label{fig:tripletmap}
+\end{figure}
 
@@
 
-Things to put in this section (from SoftwareX template)
-\begin{itemize}
-	\item overview of overall software architecture
-	\item optional: pictorial overview
-	\item implementation details
-	\begin{itemize}
-		\item software dependencies?
-		\item how to build and run (or leave this in the code README files? maybe brief description here with full details in README.)
-		\item how to use post processing tools? (TODO: prune post processing tools as much as possible so there's no excess)
-	\end{itemize}
-\end{itemize}
+The ODT code is a relatively self-contained C++ package.
+The system of nonlinear ODEs is solved using CVODE \cite{Hindmarsh_2020} and user input files are processed with YAML \cite{Beder_2008}, both of which are installed locally during the ODT build process.
+For reacting flow cases, chemical kinetics and transport are handled by Cantera \cite{Goodwin_2018}, which must be previously installed by the user.
 
-Summary of directory structure:
-\begin{itemize}
-	\item source: source code lives here; yaml files generated by building yaml in build folder get put here as well
-		\begin{itemize}
-			\item more details on directory structure necessary here? not sure if relevant
-		\end{itemize}
-	\item build: go here to build the code
-		\begin{itemize}
-			\item Run: make yaml (only need to do this once, the first time you download/build the code)
-			\item set options/paths for cmake in user\_config file
-			\item Run: cmake -C user\_config ../source
-			\item Run: make -j8
-		\end{itemize}
-	\item input: input files live here; change input files to specify case details
-		\begin{itemize}
-			\item each case type has its own folder; make your own if necessary
-			\item within each case folder, you should see file input.yaml. this is your all-important input file that makes each case unique
-			\begin{itemize}
-				\item talk about most important ODT parameters/options here? or leave to documentation?
-			\end{itemize}
-		\end{itemize}
-	\item run: go here to actually run the code; don't forget to make your changes to the input file first
-		\begin{itemize}
-			\item after building, you'll see odt.x in this folder. you can run it directly (not recommended) or from within one of the bash scripts (better)
-			\item don't forget to give your case a name; this name will be used to label data files dumped to the data directory
-		\end{itemize}
-	\item data: data and runtime files dumped here, organized by case name and individual realizations
-		\begin{itemize}
-			\item TO DO: raw/processed file types and what they contain, how to use them effectively
-		\end{itemize}
-	\item post: post processing tools located here, organized by case type
-	\item doc: doxygen documentation (if generated) lives here
-
-\end{itemize}
-
-%Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
+%Things to put in this section (from SoftwareX template)
+%\begin{itemize}
+%	\item overview of overall software architecture
+%	\item optional: pictorial overview
+%	\item implementation details
+%\end{itemize}
 
@@
 
-Present the major functionalities of the software. 
-\begin{itemize}
-	\item simulating turbulent flow cases, reacting or nonreacting flows
-	\item can simulate laminar flow cases too
-	\item does these things a whole lot faster than other methods do (LES, DNS especially)
-	\item testing LES subgrid modeling assumptions
-	\item simulating cases that DNS can't get to because needed simulation length is too long (i.e. late-flame phenomena)
-\end{itemize}
+%Present the major functionalities of the software. 
+%\begin{itemize}
+%	\item simulating turbulent flow cases, reacting or nonreacting flows
+%	\item can simulate laminar flow cases too
+%	\item does these things a whole lot faster than other methods do (LES, DNS especially)
+%	\item testing LES subgrid modeling assumptions
+%	\item simulating cases that DNS can't get to because needed simulation length is too long (i.e. late-flame phenomena)
+%\end{itemize}
 
-Example cases:
-\begin{itemize}
-	\item From cylindrical ODT paper:
-	\begin{enumerate}
-		\item pipe flow
-		\item nonreacting round jet
-		\item round jet flame
-	\end{enumerate}
-	\item Other possible example cases:
-	\begin{itemize}
-		\item something to compare with DNS/LES results to illustrate efficiency
-		\item no sooting cases since no soot in the code
-		\item planar vs. cylindrical comparison
-	\end{itemize}
-\end{itemize}
-
-Things to talk about with example cases:
-\begin{itemize}
-	\item compare to DNS/LES cases; computational efficiency, accuracy
-	\item how data looks before post processing, how post processing works
-\end{itemize}
+%Example cases:
+%\begin{itemize}
+%	\item From cylindrical ODT paper:
+%	\begin{enumerate}
+%		\item pipe flow
+%		\item nonreacting round jet
+%		\item round jet flame
+%	\end{enumerate}
+%	\item Other possible example cases:
+%	\begin{itemize}
+%		\item something to compare with DNS/LES results to illustrate efficiency
+%		\item no sooting cases since no soot in the code
+%		\item planar vs. cylindrical comparison
+%	\end{itemize}
+%\end{itemize} 
+%
+%Things to talk about with example cases:
+%\begin{itemize}
+%	\item compare to DNS/LES cases; computational efficiency, accuracy
+%	\item how data looks before post processing, how post processing works
+%\end{itemize}
 

### 2020-04-29 manuscript/manuscript.tex
Additions to motivation section. Lots of references added. Added commented text for example section.

@@
 
+Early applications of ODT focused on homogenous turbulence, wakes, and mixing layers \cite{Kerstein_1999,Kerstein_2000,Kerstein_2001}.
+Later extension to variable-density flows and a spatial downstream coordinate system facilitated its growth and application to more complex flows, including combustion in jet flames \cite{Echekki_2001,Hewson_2001,Hewson_2002,Lignell_2012,Punati_2011,Abdelsamie_2017,Lignell_2017, Goshayeshi_2015}, counterflow flames \cite{Jozefik_2015}, wall fires \cite{Monson_2016}, and sooting flames \cite{Lignell_2015,Hewson_2006,Hewson_2009,Lignell_2015b,Ricks_2010}, as well as other particle flows \cite{Sun_2017,Schmidt_2009,Sun_2014,Fistler_2017}.
+ODT has also served to complement LES through subgrid modeling studies \cite{Cao_2008,Schmidt_2003,Schmidt_2010} and has been applied to various other flow configurations such as double-diffusive interfaces \cite{GonzalezJuez_2011}, Rayleigh-Taylor mixing \cite{GonzalezJuez_2013}, and stratified turbulence \cite{Wunsch_2001}.
+Most recently, the ODT code was extended to include cylindrical and spherical coordinate systems \cite{Lignell_2018,Klein_2018,Klein_2019}.
+
+During the implementation of the cylindrical and spherical model formulations, the ODT code was drastically overhauled and reorganized, resulting in the current development version of the code.
+The ODT code presented here is a pared down version of the development code, representing the most fundamental aspects of the ODT model.
+To this end, the code presented here does not include all of the development code's functionalities.
+The example cases in Section \ref{sec:examples} represent a good sampling of the ODT code's capabilities as it is presented here.
+
 %Questions to answer in this section (from SoftwareX template)
@@
 
+\subsection{Pipe Flow}
+\label{sub:pipeflow}
+
+% TEXT COPIED FROM CYLINDRICAL ODT PAPER
+%We present results for incompressible pipe flow simulations using the temporal, cylindrical ODT formulation.
+Results for three different friction Reynolds numbers Reτ = 550, 1000, 2000 are compared to DNS results f Kh t l [26](R 550 1000) d Chi t l [6](R 2000) Silti lt from Khoury et al.
+[26](Reτ = 550, 1000) and Chin et al.
+[6](Reτ = 2000).
+Simulation results were dd i i dit f D 2 0 d fl dit f 1 0k −3 F fll d ld i fl it produced using a pipe diameter of D = 2.0 m and flow density of 1.0kg m−3.
+For fully developed pipe flow, it is possible to estimate the value of a constant mean pressure gradient driving the flow based on the value of the friction velocity, the pipe radius and the density.
+Friction velocity values of 1 (Reτ = 550, 1000) and 2 ms−1 (R 2000) d d d t llt th dit di i th fl Silti (Reτ = 2000) were assumed and used to calculate the mean pressure gradient driving the flow.
+Simulation results achieving statistical convergence for the friction velocity were verified afterward as a check on the input parameters.
+The simulations used initial conditions with constant velocity profiles.
+The simulations were run to a developed flow state, after which simulation data were gathered until statistical convergence for the root mean square (RMS) velocity difference from the mean profiles occurred.
+The total normalized run time trun/τpipe = trunu/D was 20200, 25070, and 28140 for Reτ = 550, 1000, and 2000, respectively, where u is the average velocity and D is the pipe diameter.
+
+%The simulations were performed with parameters ofC = 5and Z = 350 for the temporalODTformulation.
+Additionally, a restriction was imposed on the eddy size range by selecting eddies only up to a maximum normalized size of Le,max/D = 1/3.
+This restriction limits the eddy size by construction, as opposed to the large-eddy suppression mechanism commonly used in ODT simulations [27,45].
+The values of C, Z,and Le,max/D were adjusted to give good agreement of the ODT results compared to the DNS.
+Schmidt et al.
+[45].
+showed that higher Z results in the buffer-layer being located further from the wall; increasing C results in a lower slope of the mean streamwise velocity in the log-layer; and higher Le,max/D gives a smaller mean streamwise velocity in the wake region.
+
+%Figure 6a shows results of the mean streamwise velocity profiles in wall units for each of the three Reτ considered.
+The profiles are shifted vertically by 10 and 20 units in the figure for presentation.
+The Reτ = 550 case shows a comparison of the TMA, TMB, and the hybrid planar/cylindrical approach of the TMB eddy event implementation (PTMB).
+As seen in the figure, the differences between TMA, TMB, and PTMB are negligible, and so were not considered for the higher Reτ cases.
+The agreement between the ODT and DNS for the mean velocity is excellent for all three Reτ values.
+
+%Figure 6b shows the streamwise root mean square (RMS) velocity profiles for each Reτ .
+These profiles are shifted vertically by 2 and 4 units in the figure for presentation.
+The ODT RMS velocity profiles deviate from the DNS more strongly than the mean velocity profiles, with the ODT value at the peak approximately 20% lower than the DNS.
+The qualitative shape of the profiles, however, is the same as expected from previous ODT channel flow simulations performed with the planar formulation [33,37].
+The small double peak structure of the ODTwas described in [33] and arises from alignment of the triplet map images in the near-wall region.
+The slight depression between the ODT peaks aligns with the DNS peak, resulting in a larger difference between the RMS profiles than an extrapolation of the surrounding ODT profiles to the peak region would give.
+As for the mean profiles, the differences between TMA, TMB, and PTMB for the RMS velocity profiles are negligible.
+Small differences appear only for the RMS profiles near the centerline.
+We expect this because of the eddy timescale behavior seen in Fig.
+5.
+
+\subsection{Non-reacting Jet }
+\label{sub:nonreactingjet}
+
+% TEXT COPIED FROM CYLINDRICAL ODT PAPER
+%The new cylindrical ODT formulation is demonstrated in a nonreacting round turbulent jet.
+Results are compared to the experimental data of Hussein et al.
+[18].
+The jet consists of air issuing into air through a 1 in (0.0254 m) diameter duct.
+The jet exit velocity is 56.2 ms−1 and is well-approximated by a top-hat profile.
+The reported Reynolds number is 95,500, where Re = Dv0/ν,and D is the jet exit diameter, v0 is the jet exit velocity, and ν is the kinematic viscosity.
+The ODT simulations use the same diameter and velocity, but a kinematic viscosity of 1.534×10−5 m2 s−1, giving a Reynolds number of 93,056.
+The initial velocity profile i th ODT ilti i difid t ht fil i hih h bli ttfti f idth δ 0 1D in the ODT simulations is a modified top-hat profile in which a hyperbolic tangent function ofwidth δ = 0.1D is used on either side of the jet to smooth the transition between the jet and the free stream.
+Here, xc1 and xc2 are the center locations of the tanh transition, −D/2and D/2, respectively.
+In the spatial formulation ofODT, the streamwise velocity must be positive everywhere on the line due to v in the denominator on the right hand side of the evolution equations (see Sect.
+2.4.1).
+As such, a small vmin = 0.1ms−1 is added uniformly to the velocity profile.
+v is taken to be the jet velocity of 56.2 ms−1.
+
+%ODT simulations were performed using the TMB triplet map with parameters C = 5.25, βles = 3.5, and Z=400.
+The value of Z is the same as the spatial simulations in [38] and was not adjusted.
+The values ofC and βles were adjusted to give good agreement of the jet evolution with the experimental data.
+Note the very close agreement of the C and Z parameters here to the optimal values used for the pipe flow simulations where C = 5and Z = 350.
+This illustrates a level of robustness in the ODT parameters between the two configurations and suggests that intermediate values could be successfully applied in both configurations.
+The pipe flow is sensitive to Z, as noted above, but the jet is not, so Z = 350 would be preferred.
+Figure 7 shows results of the simulations.
+
+%Here, 1024 independent ODT realizations were performed and results were ensemble averaged.
+All quantities are normalized consistent with jet similarity scaling.
+Downstream locations are normalized by the jet diameter D, and radial locations are normalized by (y − y0)where y is the downstream location and y0 = 4D is the virtual origin used in [18].
+In the figure, v0 is the jet exit velocity and vcL is the local mean axial centerline velocity.
+Here, r is used to denote both the experimental radial location and the ODT line position x.
+
+%Figure 7ashows v0/vcL versus y/D; the similarity scaling gives a nominally linear profile where v decays as 1/y.
+The ODT simulation compares very well with the stationary wire data in [18] after an initial induction period for y/D < 20.
+The dashed line in the plot is the linear curve fit reported by Hussein et al.
+Figure 7b shows radial profiles of the mean axial velocity normalized by the local centerline value.
+Profiles at three axial locations, 50D,70D, and 90D, are shown.
+The experimental data points shown are the laser Doppler some spread in the profiles at higher r/(y − y0), with the simulation results relaxing toward the experimental values with downstream distance.
+Figure 7c shows radial profiles of the axial root mean square (RMS) velocity anemometer (LDA) data in [18].
+TheODT results show a similarity collapse of the data at r/(y−y0)< 0.1, but normalized by the local centerline velocity at the same three positions.
+Here again, the profiles tend to relax toward the experimental (LDA) data at higher r/(y − y0) with downstream distance.
+
+%the quantitative agreement of vrms velocity is generally good, especially for r/(y − y0)> 0.03.
+At lower values, near the centerline, the ODT vrms increases, whereas the experimental data decrease slightly.
+We attribute this to the so-called centerline anomaly of the cylindrical ODT formulation due to the geometric stretching associated with the cylindrical triplet maps.
+This stretching is shown in Figs.
+2 and 3.Infact,the motivation for developing TMB was to minimize the degree of this geometric stretching.
+The stretching effect was present for both maps TMA and TMB, but it is largest near the centerline, where curvature is large.
+With increasing distance from the centerline, that is, for large distances compared to the eddy size, the geometric stretching effect becomes negligible for both maps, and they both approach the planar limit.
+
+%For comparison to the ODT results with TMB shown in Fig.
+7, similar simulations were performed with TMA, and corresponding results are shown in Fig.
+8.
+Here, βles and Z are the same as for the previous case with TMB, but C = 7.
+Again, we see good agreement for the centerline velocity decay in Fig.
+8a.
+A somewhat better similarity collapse than for TMB occurs in the radial velocity profiles, though they are slightly lower than the experimental data at r/(y − y0)< 0.13 and slightly higher than the experimental data at r/(y − y0)> 0.13.
+The vrms profiles also show strong similarity scaling.
+Compared with TMB, however, the simulations show a much higher centerline anomaly, and the vrms profile departs from the experiments much further from the centerline and has a higher rise in the region r/(y − y0)< 0.05.
+
+%It is worth noting that the vrms profile depends somewhat on the ODT parameters selected.
+Hewson and Kerstein [15] demonstrated that mean centerline values of mixture fraction were insensitive to C and βles provided their ratio was kept constant.
+In these simulations, however, higher values of RMS fluctuations were observed at lower values of βles.
+Figure 9 shows results for TMA similar to those in Fig.
+8 with varying C and βles.
+Each of the three cases has C/βles = 2, with C = 7, 5, and 3.
+Plots (b) and (c) show axial location
+
+%The centerline velocity decay and radial profiles show good agreement, as with the previous cases, with a slight improvement in the radial velocity profile.
+The vrms profiles are significantly improved along the centerline compared to TMA and TMB.
+The centerline anomaly is not completely removed, however, since implemented eddies are still subject to the geometric distortion of the TMB map, whose influence is felt by the τ−1 calculation for subsequent eddy events.
+e
+
+\subsection{Jet Flame}
+\label{sub:jetflame}
+
+% TEXT COPIED FROM CYLINDRICAL ODT PAPER
+%The newcylindrical ODTformulation is demonstrated in a round, reacting, turbulent jet flame.Results are compared to the experimental DLR-Aflame ofMeier et al.
+[19,36].
+Heat release and temperature- and compositiondependent transport and thermodynamic properties are key characteristics of this flow.
+This canonical flame configuration has been used extensively to study and validate turbulent combustion models.
+Pitsch [41] studied differential diffusion effects in this flame using a classical unsteady flamelet model.
+Lindstedt and Ozarivsky [35] investigated it using a joint PDF approach, while Wang and Pope [52] used an LES/PDF model combined with a flamelet/progress-variable (FPV) model.
+Fairweather and Woolley [10] studied several chemical mechanisms using the DLR flame and a first-order conditional moment closure (CMC) model, and Lee and Choi [29,30] studied NO emissions using an Eulerian particle flamelet model.
+These studies consisted of computational fluid dynamics (CFD) simulations with subgrid modeling of the turbulent combustion process.
+In contrast, ODT is a low-dimensional representation of the entire flow, not just the subgrid scales.
+Previous ODT studies of turbulent jet flames have employed the temporal planar formulation, so we expect that the model may improve with a spatial cylindrical formulation that more closely matches the experimental configuration.
+%The DLR-A fuel stream is mixture of 22.1% CH4, 33.2% H2, and 44.7% N2 (by volume) that issues into dry air.
+The fuel stream exits a nozzle with an inner diameter of 8 mm at a mean exit velocity of 42.2 ms−1.
+The coflowing air stream issues from a nozzle of diameter 140 mm at a velocity of 0.3 ms−1.
+The reported Reynolds number is 15,200.
+%The ODT simulation uses these diameters and the experimentally reported velocity profile at the jet exit.
+In the nonreacting case, a small velocity was added uniformly to the profile, no velocity addition is needed here because of the slow-moving coflow air stream present alongside the reacting jet.
+The ODT simulation includes the buoyant source term but not the streamwise pressure gradient in Eq.
+(25).
+The fuel was diluted with N2 in the experimental flame to minimize radiative heat losses, and radiation is ignored in the simulation.
+This flame has a low Reynolds number, and the combustion chemistry proceeds quickly.
+The ODT simulation transports the following species: O2, N2, CH4, H2, H2O, CO2.
+Reactions are assumed to proceed to products of complete combustion:
+%H2 + 1/2O2 → H2O, CH4 + 2O2 → CO2 + 2H2O,
+%(38) (39)
+%and simple, fast reaction rates are applied.
+These assumptions are not reasonable for the DLR-A flame.
+The primary purpose of these simulations is to illustrate ODT in a reacting jet with variable properties and heat release.
+%Z = 400.
+The values of C and βles were adjusted to give good agreement of the jet evolution with the experimental data, while the value of Z was taken as the same value as for the jet in Sect.
+3.2.
+Results of ODT simulations were performed using the TMB triplet map with parameters C = 20, βles = 17, and 400 Th l f C d β djtd t i d t f th jt lti ith th
+%the simulation are presented in Figs.
+11 and 12.
+One thousand independent flow realizations were performed, and the results ensemble averaged.
+Downstream distance, y, and radial position, r, are normalized by the jet diameter D.
+
 %Present the major functionalities of the software. 
@@
 %	\item simulating cases that DNS can't get to because needed simulation length is too long (i.e. late-flame phenomena)
-%\end{itemize}
-
-%Example cases:
-%\begin{itemize}
-%	\item From cylindrical ODT paper:
-%	\begin{enumerate}
-%		\item pipe flow
-%		\item nonreacting round jet
-%		\item round jet flame
-%	\end{enumerate}
-%	\item Other possible example cases:
-%	\begin{itemize}
-%		\item something to compare with DNS/LES results to illustrate efficiency
-%		\item no sooting cases since no soot in the code
-%		\item planar vs. cylindrical comparison
-%	\end{itemize}
-%\end{itemize} 
-%
-%Things to talk about with example cases:
-%\begin{itemize}
-%	\item compare to DNS/LES cases; computational efficiency, accuracy
-%	\item how data looks before post processing, how post processing works
 %\end{itemize}
@@
 \end{enumerate}
-
-%COPIED/PASTED FROM CYLINDRICAL ODT PAPER
-%ODT has been applied by a number of researchers to a wide range of flows.
-These include homogeneous turbulence \cite{Kerstein_1999,Sun_2014}, wakes \cite{Kerstein_2000}, mixing layers \cite{Kerstein_1999,Kerstein_2001,Ashurst_2003,Ashurst_2005}, stratified flows \cite{Wunsch_2001}, Rayleigh-Benard flows \cite{Wunsch_2005}, buoyant wall flows \cite{Dreeben_2000,Shihn_2007}, and channel flows \cite{Schmidt_2009,Schmidt_2003,Lignell_2013}.
-Schmidt et al.
-\cite{Schmidt_2013} studied buoyantly-driven cloud-top entrainment with comparisons to water tank experiments.
-Gonzalez-Juez et al.
-\cite{Esteban_2013} studied reactive Rayleigh-Taylor mixing.
-A number of ODT simulations of turbulent jet flames have been performed \cite{Echekki_2001,Hewson_2001,Hewson_2002,Punati_2011,Lignell_2012b,Lignell_2015}.
-Other combustion applications include wall fires \cite{Monson_2016,Shihn_2004}, buoyant pool fires \cite{Ricks_2010,Hewson_2006,Hewson_2009}, and opposed jet flames \cite{Jozefik_2015}.
-Several studies used DNS to validate ODT for combustion in temporal planar jets \cite{Punati_2011,Lignell_2012b,Lignell_2015}.
-ODT has also been applied as a subgrid model for large eddy simulations (LES) \cite{Cao_2008,Schmidt_2003,Schmidt_2010} and in particle dynamics simulations in channel flows \cite{Schmidt_2009}, homogeneous turbulence \cite{Sun_2014}, and jets \cite{Sun_2017,Goshayeshi_2015}.
-
-%TEXT COPIED FROM ABANDONED JOSS DRAFT
-
-%ODT has been applied to a wide range of flows.
-Early applications focused on homogenous turbulence, wakes, and mixing layers (Kerstein1999,Kerstein2000,Kerstein2001).
-Later extension to variable-density flows and a spatial downstream coordinate system facilitated its growth and application to more complex flows, including combustion in jet flames (Echekki2001; Hewson2001; Hewson2002; Lignell2012; Punati2011; Abdelsamie2017; Lignell2017; Goshayeshi2015), counterflow flames  (Jozefik2015), wall fires (Monson2016), and sooting flames, (Lignell2015; Hewson2006; Hewson2009; Lignell2015b, Ricks2010), as well as other particle flows (Sun2017; Schmidt2009; Sun2014; Fistler2017).
-ODT has also served to complement LES through subgrid modeling studies (Cao2008; Schmidt2003; Schmidt2010) and has been applied to various other flow configurations such as double-diffusive interfaces (GonzalezJuez2011), Rayleigh-Taylor mixing (GonzalezJuez2013), and stratified turbulence (Wunsch2001).
-Most recently, the ODT code was extended to include cylindrical and spherical coordinate systems (Lignell2018; Klein2018; Klein2019).
-During this implementation, the ODT code was drastically overhauled, resulting in the SEC package presented here.
-Further detail on the current ODT model formulation and implementation can be found in the literature (Ashurst2005; Kerstein2001; Lignell2013; Lignell2018).
-
-%Ongoing research involving ODT and SEC spans multiple research groups and subject areas.
-ODT is currently being used to investigate soot formation and destruction in ethylene jet flames via parametric modeling studies (Hewson2015; Lansinger2015b).
-The SEC package framework is also being used to develop the hierarchical parcel swapping model (HiPS), which models turbulence with an economical, hierarchical network that represents the fluid as individual parcels capable of switching positions within the tree (Kerstein2013; Kerstein2014).
-In the future, SEC may also be extended to include the linear eddy model (LEM) (Kerstein1991) and LES approaches.
 

### 2020-04-30 manuscript/manuscript.tex
Drafting text of example cases sections, updating references, formatting equations. Miscellaneous other updates.

--- 2020-04-27 manuscript/manuscript.tex
@@
 \usepackage{amssymb}
+\usepackage{amsmath}
 %% The amsthm package provides extended theorem environments
@@
 
+Early applications of ODT focused on homogenous turbulence, wakes, and mixing layers \cite{Kerstein_1999,Kerstein_2000,Kerstein_2001}.
+Later extension to variable-density flows and a spatial downstream coordinate system facilitated its growth and application to more complex flows, including combustion in jet flames \cite{Echekki_2001,Hewson_2001,Hewson_2002,Lignell_2012,Punati_2011,Abdelsamie_2017,Lignell_2017, Goshayeshi_2015}, counterflow flames \cite{Jozefik_2015}, wall fires \cite{Monson_2016}, and sooting flames \cite{Lignell_2015,Hewson_2006,Hewson_2009,Lignell_2015b,Ricks_2010}, as well as other particle flows \cite{Sun_2017,Schmidt_2009,Sun_2014,Fistler_2017}.
+ODT has also served to complement LES through subgrid modeling studies \cite{Cao_2008,Schmidt_2003,Schmidt_2010} and has been applied to various other flow configurations such as double-diffusive interfaces \cite{GonzalezJuez_2011}, Rayleigh-Taylor mixing \cite{GonzalezJuez_2013}, and stratified turbulence \cite{Wunsch_2001}.
+Most recently, the ODT code was extended to include cylindrical and spherical coordinate systems \cite{Lignell_2018,Klein_2018,Klein_2019}.
+
+During the recent implementation of the cylindrical and spherical model formulations, the ODT code was drastically overhauled and reorganized, resulting in its current configuration.
+The ODT code presented here is a pared down version of the development code, representing the fundamental aspects of the ODT model and its most reliable functions.
+The example cases in Section \ref{sec:examples} are a representative sample of the ODT code's capabilities as it is presented here.
+Future releases will expand this code's functionality with additional features currently in development.
+
 %Questions to answer in this section (from SoftwareX template)
@@
 
+\subsection{Pipe Flow}
+\label{sub:pipeflow}
+
+% TEXT COPIED/MODIFIED FROM CYLINDRICAL ODT PAPER
+First, we present an incompressible pipe flow simulation using the temporal, cylindrical ODT formulation.
+Results for three different friction Reynolds numbers ($Re_\tau$ = 550, 1000, 2000) are compared to DNS results from El Khoury et al.
+\cite{ElKhoury_2013} ($Re_\tau$ = 550, 1000) and Chin et al.
+\cite{Chin_2014} ($Re_\tau$ = 2000) for a pipe diameter of $D=2.0$ m and flow density of 1.0 kg$\cdot$m$^{-3}$.
+Friction velocity values of 1 m$\cdot$s$^{-1}$ ($Re_\tau = 550, 1000$) and 2 m$\cdot$s$^{-1}$ ($Re_\tau = 2000$) were assumed and used to calculate the mean pressure gradient driving the flow.
+Using initial conditions with uniform velocity profiles, simulations were run until a state of developed flow was achieved, at which point data were gathered until statistical convergence for the root mean square (RMS) velocity difference from the mean profiles occurred.
+
+The simulations were performed with ODT parameters $C = 5$ and $Z = 350$ for the temporal ODT formulation. 
+%Additionally, a restriction was imposed on the eddy size range by selecting eddies only up to a maximum normalized size of Le,max/D = 1/3.
+This restriction limits the eddy size by construction, as opposed to the large-eddy suppression mechanism commonly used in ODT simulations [27,45].
+The values of C and Z
+%and Le,max/D 
+were adjusted to give good agreement of the ODT results compared to the DNS.
+Schmidt et al.
+\cite{Schmidt_2003} showed that higher $Z$ results in the buffer-layer being located further from the wall, and increasing $C$ results in a lower slope of the mean streamwise velocity in the log-layer.
+%and higher Le,max/D gives a smaller mean streamwise velocity in the wake region.
+
+RESULTS AND PLOTS GO HERE
+
+\subsection{Non-reacting Jet }
+\label{sub:nonreactingjet}
+
+% TEXT COPIED/MODIFIED FROM CYLINDRICAL ODT PAPER
+Here, we present ODT simulation results for a non-reacting round, turbulent jet compared to the experimental data of Hussein et al.
+\cite{Hussein_1994}.
+The jet consists of air issuing into air through a 1 in (0.0254 m) diameter duct with a uniform exit velocity of 56.2 m$\cdot$s$^{-1}$ and a reported Reynolds number of 95,500.
+The ODT simulations use this diameter and velocity with a kinematic viscosity of $1.534\cdot10^{-5}$ m$^2$s$^{-1}$, resulting in a Reynolds number of 93,056.
+The initial velocity profile in the ODT simulations is a modified top-hat profile in which a hyperbolic tangent function of width $\delta$ = 0.1D is used on either side of the jet to smooth the transition between the jet and the free stream.
+In the spatial formulation of ODT, the streamwise velocity must be positive everywhere on the line, so a small minimum velocity of $v_{min} = 0.1$m$\cdot$s$^{-1}$ is specified and added across the entire velocity profile.
+
+ODT simulations were performed with parameters $C = 5.25$, $\beta_{LES} = 3.5$, and $Z=400$.
+The value of $Z$ is the same as the spatial simulations in \cite{Monson_2016}, and the values of $C$ and $\beta_{LES}$ were adjusted to give good agreement with the experimental data.
+Note the close agreement of the $C$ and $Z$ parameters here to the optimal values used for the pipe flow simulations ($C = 5$ and $Z = 350$).
+This illustrates a level of robustness in the ODT parameters and suggests that intermediate values could be successfully applied in both configurations.
+
+1024 independent ODT realizations were performed and results were ensemble averaged.
+All quantities are normalized consistent with jet similarity scaling.
+Downstream locations are normalized by the jet diameter $D$, and radial locations are normalized by $(y-y_0)$, where $y$ is the downstream location and $y_0 = 4D$ is the virtual origin used in \cite{Hussein_1994}.
+
+RESULTS AND PLOTS GO HERE
+
+%In the figure, $v_0$ is the jet exit velocity and $v_{cL}$ is the local mean axial centerline velocity.
+Here, $r$ is used to denote both the experimental radial location and the ODT line position $x$.
+
+%It is worth noting that the vrms profile depends somewhat on the ODT parameters selected.
+Hewson and Kerstein [15] demonstrated that mean centerline values of mixture fraction were insensitive to C and βles provided their ratio was kept constant.
+In these simulations, however, higher values of RMS fluctuations were observed at lower values of βles.
+Figure 9 shows results for TMA similar to those in Fig.
+8 with varying C and βles.
+Each of the three cases has C/βles = 2, with C = 7, 5, and 3.
+Plots (b) and (c) show axial location
+
+%The centerline velocity decay and radial profiles show good agreement, as with the previous cases, with a slight improvement in the radial velocity profile.
+The vrms profiles are significantly improved along the centerline compared to TMA and TMB.
+The centerline anomaly is not completely removed, however, since implemented eddies are still subject to the geometric distortion of the TMB map, whose influence is felt by the τ−1 calculation for subsequent eddy events.
+e
+
+\subsection{Jet Flame}
+\label{sub:jetflame}
+
+% TEXT COPIED FROM CYLINDRICAL ODT PAPER
+ODT is uniquely suited for reacting flow simulations.
+Here, we present illustrative ODT simulation results of a round, turbulent jet flame based on and compared to the experimental DLR-A flame of Meier et al.
+\cite{Meier_2000}.
+This canonical flame configuration has been used extensively to study and validate turbulent combustion models \cite{Pitsch_2000,Lindstedt_2005,Wang_2011,Fairweather_2004,Lee_2008,Lee_2009}.
+
+The DLR-A fuel stream is mixture of 22.1\% CH$_4$, 33.2\% H$_2$, and 44.7\% N$_2$ (by volume) that issues into dry air via a nozzle with an inner diameter of 8 mm at a mean exit velocity of 42.2 m$\cdot$s$^{-1}$.
+The coflow air stream issues from a concentric nozzle 140 mm in diameter at a velocity of 0.3 m$\cdot$s$^{-1}$.
+The reported jet Reynolds number is 15,200.
+
+Previous ODT studies of turbulent jet flames have used the temporal planar formulation, but the spatial cylindrical formulation developed recently \cite{Lignell_2018} more closely matches the experimental configuration.
+This simulation uses the experimentally reported velocity profiles and jet dimensions.
+In the non-reacting case, a small minimum velocity was added uniformly to the velocity profile; no such addition is required here because of the slow-moving coflow air stream that issues alongside the reacting jet.
+%The ODT simulation includes the buoyant source term but not the streamwise pressure gradient in Eq. (25). 
+The fuel was diluted with N$_2$ in the experimental flame to minimize radiative heat losses, and radiation is ignored in the simulation.
+This flame has a low Reynolds number, and the combustion chemistry proceeds quickly.
+The ODT simulation transports the chemical species O$_2$, N$_2$, CH$_4$, H$_2$, H$_2$O, and CO$_2$.
+We assume that reactions proceed to the products of complete combustion and apply simple, fast reaction rates according to the following chemical equations:
+\begin{align}
+	\mathrm{CH}_4 + 2\mathrm{O}_2 & \rightarrow \mathrm{CO}_2 + 2\mathrm{H}_2\mathrm{O}, \\
+	\mathrm{H}_2+\frac{1}{2}\mathrm{O}_2 & \rightarrow \mathrm{H}_2\mathrm{O}.
+\end{align}
+These assumptions are not reasonable for the DLR-A flame, but they allow us to illustrate ODT in a reacting jet configuration with variable properties and heat release, which is the primary purpose of this example case.
+More complex combustion reaction mechanisms are available within the source code and can be accessed by changing the appropriate input file parameter.
+
+This simulation uses ODT parameters $C=20$, $\beta_{LES}=17$, and $Z=400$.
+The values of $C$ and $\beta_{LES}$ were adjusted to give good agreement with the experimental data, and the value of $Z$ is the same as it was for the non-reacting jet in Section \ref{sub:nonreactingjet}.
+1024 independent flow realizations were performed in parallel and the results ensemble averaged.
+Downstream distance $y$ and radial position $r$ are normalized by the jet diameter $D$.
+
+RESULTS AND PLOTS GO HERE
+
 %Present the major functionalities of the software. 

### 2020-05-23 manuscript/manuscript.tex
Updated text of model description section. Working on software architecture section. Flow chart in progress elsewhere.

@@
 Previous studies show that ODT can attain accuracy comparable to DNS at a fraction of the computational cost \cite{Lignell_2015,Abboud_2015}, making it an attractive tool for simulating turbulent flows.
-Because the model is one-dimensional, it is limited to homogeneous or boundary layer flows such as jets, wakes, and mixing layers; such flows, however, are extremely common in both nature and turbulence research.
+Because the ODT model is one-dimensional, it is limited to homogeneous or boundary-layer flows, such as jets, wakes, and mixing layers; these types of flows, however, are common in nature and central to turbulence research.
 ODT's computational efficiency and resolution of a full range of scales make it a valuable tool that complements experimental studies and other simulation tools like DNS and LES.
@@
 In ODT, turbulent advection is modeled with stochastic processes called eddy events, which punctuate the solution of unsteady, one-dimensional transport equations for mass, momentum, and enthalpy.
-The ODT code uses a Lagrangian finite-volume formulation for diffusive advancement that includes adaptive mesh refinement \cite{Lignell_2013}.
-In this approach, mass remains constant inside each grid cell while cell volumes increase or decrease according to dilation.
-Because the ODT model is one-dimensional, it is limited to homogeneous or boundary-layer flows, such as jets, wakes, and mixing layers; these types of flows, however, are common in nature and central to turbulence research.
+The ODT code uses a Lagrangian finite-volume formulation for diffusive advancement in which mass stays constant within each grid cell while cell volumes increase or decrease according to cell dilation via an adaptive mesh refinement \cite{Lignell_2013}.
+
+Transport equations for mass, momentum, and enthalpy in the temporal formulation of ODT take the following generic form, derived from the Reynolds Transport Theorem \cite{Cengel_2010} for a given scalar quantity per unit mass $\beta$:
+\begin{equation} 
+\label{eq:transport}
+	\frac{\mathrm{d}\beta}{\mathrm{d}t} = -\frac{j_{\beta,e}A_{x,e}-j_{\beta,w}A_{x,w}}{\rho V} + \frac{S_{\beta}}{\rho V}.
+\end{equation}
+Here, $j_{\beta}$ is the diffusion flux of scalar $\beta$ across the cell face area $A_x$ where the subscripts $e$ and $w$ refer to the "east" and "west" faces of the grid cell, respectively.
+$S_{\beta}$ is the Lagrangian source term derived from the conservation law for $\beta$, $\rho$ represents mass density, and $V$ represents cell volume.
+In practice, we refer to the left hand term on the right side of Equation~\ref{eq:transport} as the "mixing term" and the right hand term on the right side of Equation~\ref{eq:transport} as the "source term".
+The generic transport equation differs slightly in the spatial formulation of ODT, but its form is the same, so we omit it here for brevity.
+The system of ordinary differential equations (ODEs) that results is well behaved at all grid points and in all geometries in their finite-volume forms.
+For details on transport equation derivation and use in both the temporal and spatial formulations of ODT, see Lignell et al.
+\cite{Lignell_2018}.
 
@@
 Three user-defined ODT parameters control the eddy event process: the eddy rate parameter $C$ scales the rate of occurrence of the eddies; the viscous penalty parameter $Z$ suppresses small eddies; and the large eddy suppression parameter $\beta$ constrains eddies such that they do not reach over the elapsed simulation time.
+Sampled eddies that do not fit the defined parameters are rejected and not applied to the domain.
 
@@
 
+Eddy events occur concurrently with diffusive advancement via solution of the system of unsteady one-dimensional transport equations.
+In this way, the ODT code marches in time or space until it reaches its end point.
+Due to the stochastic nature of eddy events, each ODT simulation, or realization, is different, even when it is provided with the same input parameters.
+In order to obtain statistically stable data for a given set of parameters, we run many realizations with the same input parameters and time-average them.
+This is done via post-processing tools, which are provided in the ODT package.
+
 %-----------------------------------------------------------------------------------
@@
 
-The ODT code is a relatively self-contained C++ package.
+The ODT package consists primarily of an object-oriented C++ code responsible for running flow simulation cases and generating data.
+The package also contains auxiliary data processing and visualization tools, written mostly in Python.
+Within the main download package, several directories organize the code:
+\begin{itemize} \itemsep0em
+	\item \texttt{source}: ODT source code
+	\item \texttt{build}: compiles and builds source code via CMake
+	\item \texttt{run}: ODT executable and run scripts
+	\item \texttt{data}: data generated by source code
+	\item \texttt{input}: input files used to specify case variables
+	\item \texttt{post}: data post-processing and visualization scripts
+	\item \texttt{doc}: code documentation generated by Doxygen
+\end{itemize}
+
+% source code stuff
+In an individual simulation, variables live within in the \texttt{domain} class; wherever these variables are used within the code, pointers refer back to these locations.
+Key quantities are referred to as line variables, and their individual properties and functions exist within child classes of the \texttt{domainvariables} parent class.
+
 The system of nonlinear ODEs is solved using CVODE \cite{Hindmarsh_2020} and user input files are processed with YAML \cite{Beder_2008}, both of which are installed locally during the ODT build process.
 For reacting flow cases, chemical kinetics and transport are handled by Cantera \cite{Goodwin_2018}, which must be previously installed by the user.
+
+% You can talk about the basic structure: domain.cc is the main object that holds pointers to everything else.
+There are back pointers to the domain, so that everyone can see everyone else, as needed.
+The key quantities are line variables (arrays stored at each point).
+These are the domainvariables.
+The domain class has a vector of pointers to these, and also pointers to specific variables to access them by name.
+This enables both generic looping over variables to have each variable compute, for example, its source term, and also allow specific access to needed variables like the grid positions, etc.
+The variables are either transported or not.
+The variables needed for a given simulation are set up in the domaincases class.
+In addition, there are general parameters.
+You could discuss the main classes, or maybe show a class flow diagram.
+These can be easily generated, and doxygen also does some of this.
 
@@
 \label{sec:examples}
+
+%\subsection{General Workflow}
+%\label{sub:workflow}
+%
+%Every ODT simulation shares common steps to a successful run. 
+%\begin{enumerate}
+%	\item Build and compile the code. 
+%	\item Choose a case type and chemical mechanism (when required) and alter the appropriate input file(s). 
+%	\item Within the \texttt{run} directory, alter the run script to be used with a case name and other required information.
+%	\item Run the case from the \texttt{run} directory using the chosen run script.
+%	\item Run the appropriate post-processing scripts, located in the \texttt{post} directory, on the raw data for interpretation and visualization.
+%\end{enumerate}
 

### 2020-05-26 manuscript/manuscript.tex
Added flow chart to software architecture section.
Finished drafting software architecture section. Added workflow subsection, unfinished. Other minor revisions and edits to existing text.

@@
 The ODT code presented here is a pared down version of the development code, representing the fundamental aspects of the ODT model and its most reliable functions.
-The example cases in Section \ref{sec:examples} are a representative sample of the ODT code's capabilities as it is presented here.
+The example cases in Section~\ref{sec:examples} are a representative sample of the ODT code's capabilities as it is presented here.
 Future releases will expand this code's functionality with additional features currently in development.
@@
 
-The ODT model is described in detail in the literature \cite{Kerstein_1999,Kerstein_2001,Ashurst_2005,Lignell_2018,Lignell_2013}; only a brief explanation will be given here.
+The ODT model is described in detail in the literature~\cite{Kerstein_1999,Kerstein_2001,Ashurst_2005,Lignell_2018,Lignell_2013}; only a brief explanation will be given here.
 In ODT, turbulent advection is modeled with stochastic processes called eddy events, which punctuate the solution of unsteady, one-dimensional transport equations for mass, momentum, and enthalpy.
-The ODT code uses a Lagrangian finite-volume formulation for diffusive advancement in which mass stays constant within each grid cell while cell volumes increase or decrease according to cell dilation via an adaptive mesh refinement \cite{Lignell_2013}.
+The ODT code uses a Lagrangian finite-volume formulation for diffusive advancement in which mass stays constant within each grid cell while cell volumes increase or decrease according to cell dilation via an adaptive mesh refinement~\cite{Lignell_2013}.
 
-Transport equations for mass, momentum, and enthalpy in the temporal formulation of ODT take the following generic form, derived from the Reynolds Transport Theorem \cite{Cengel_2010} for a given scalar quantity per unit mass $\beta$:
+Transport equations for mass, momentum, and enthalpy in the temporal formulation of ODT take the following generic form, derived from the Reynolds Transport Theorem~\cite{Cengel_2010} for a given scalar quantity per unit mass $\beta$:
 \begin{equation} 
@@
 The system of ordinary differential equations (ODEs) that results is well behaved at all grid points and in all geometries in their finite-volume forms.
-For details on transport equation derivation and use in both the temporal and spatial formulations of ODT, see Lignell et al.
-\cite{Lignell_2018}.
+For details on transport equation derivation and use in both the temporal and spatial formulations of ODT, see Lignell et al.~\cite{Lignell_2018}.
 
@@
 
-Eddy events modify domain variables using triplet maps, as illustrated for a cylindrical domain in Figure \ref{fig:tripletmap}.
+Eddy events modify domain variables using triplet maps, as illustrated for a cylindrical domain in Figure~\ref{fig:tripletmap}.
 For a region of eddy size $l$, the domain is copied to create three map images; the three images are then placed back to back with the middle image inverted to maintain continuity, and the composite is reapplied to the domain.
@@
 	\includegraphics[width=\textwidth]{../figures/tripletmap/tripletmap.png} 
-	\caption{Schematic diagram of a cylindrical triplet map, adapted from \cite{Lignell_2018}.
+	\caption{Schematic diagram of a cylindrical triplet map, adapted from~\cite{Lignell_2018}.
 Before the triplet map, the domain contains three grid cells of equal volume, while after the triplet map has been applied, the domain contains nine cells.
@@
 The package also contains auxiliary data processing and visualization tools, written mostly in Python.
-Within the main download package, several directories organize the code:
-\begin{itemize} \itemsep0em
-	\item \texttt{source}: ODT source code
-	\item \texttt{build}: compiles and builds source code via CMake
-	\item \texttt{run}: ODT executable and run scripts
-	\item \texttt{data}: data generated by source code
-	\item \texttt{input}: input files used to specify case variables
-	\item \texttt{post}: data post-processing and visualization scripts
-	\item \texttt{doc}: code documentation generated by Doxygen
-\end{itemize}
+The post-processing tools are case-specific but will be  addressed in Section~\ref{sub:workflow}.
 
-% source code stuff
-In an individual simulation, variables live within in the \texttt{domain} class; wherever these variables are used within the code, pointers refer back to these locations.
-Key quantities are referred to as line variables, and their individual properties and functions exist within child classes of the \texttt{domainvariables} parent class.
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../figures/odt_flow_chart/odt_flow_chart.png} 
+	\caption{Basic structure of the ODT code.
+For clarity and brevity, this diagram makes two major assumptions: first, that diffusion advancement in the \texttt{micromixer} uses an explicit solution method; and second, that the eddy event sampled by the \texttt{eddy} object passes all rejection tests before being applied to the domain.}
+	\label{fig:flowchart}
+\end{figure}
 
-The system of nonlinear ODEs is solved using CVODE \cite{Hindmarsh_2020} and user input files are processed with YAML \cite{Beder_2008}, both of which are installed locally during the ODT build process.
-For reacting flow cases, chemical kinetics and transport are handled by Cantera \cite{Goodwin_2018}, which must be previously installed by the user.
+Figure~\ref{fig:flowchart} illustrates the ODT code's most important objects and structural features.
+User inputs are provided to the executable in YAML \cite{Beder_2008} format via \texttt{input.yaml}; the location of the specific \texttt{input.yaml} file to be used is determined by the case name and case type specified in the run script.
+The \texttt{main} function defines storage for the main objects, but, once created, the \texttt{domain} object is responsible for object initialization as well as variable initialization and storage via a case-specific \texttt{domaincase} object.
 
-% You can talk about the basic structure: domain.cc is the main object that holds pointers to everything else.
-There are back pointers to the domain, so that everyone can see everyone else, as needed.
-The key quantities are line variables (arrays stored at each point).
-These are the domainvariables.
-The domain class has a vector of pointers to these, and also pointers to specific variables to access them by name.
-This enables both generic looping over variables to have each variable compute, for example, its source term, and also allow specific access to needed variables like the grid positions, etc.
-The variables are either transported or not.
-The variables needed for a given simulation are set up in the domaincases class.
-In addition, there are general parameters.
-You could discuss the main classes, or maybe show a class flow diagram.
-These can be easily generated, and doxygen also does some of this.
+Three primary objects handle the code's main functions: the \texttt{solver}, \texttt{micromixer}, and \texttt{eddy} objects.
+The \texttt{solver} coordinates the ODT solution process, marching along the simulation time and invoking diffusive advancement and eddy events when appropriate.
+The \texttt{micromixer} handles diffusive advancement by setting step sizes, interacting with the transported domain variables, and solving the system of ODEs defined by Equation~\ref{eq:transport} (or its equivalent in the spatial formulation).
+The \texttt{micromixer} includes three solution methods that can be specified in \texttt{input.yaml}, each appropriate for various case types: a first-order explicit Euler method (pictured in Figure~\ref{fig:flowchart}); a first-order semi-implicit method that uses CVODE~\cite{Hindmarsh_2020} to advance coupled ODEs in individual grid cells, integrated sequentially; and a second-order Strang splitting method \cite{Strang_1968} good for treating stiff chemistry.
+In reacting flow cases, chemical kinetics are handled by Cantera \cite{Goodwin_2018}, which uses transported variable values---enthalpy and gas species composition, for instance---to specify local scalar values such as gas temperature or density, which can affect flow properties.
+The \texttt{micromixer} is also the code's primary point of interaction with the \texttt{mesher} object (not pictured in Figure~\ref{fig:flowchart}), which manages the adaptive grid functions.
+Finally, the \texttt{eddy} object manages eddy event selection and implementation, which proceeds as described in Section~\ref{sub:model_description}.
 
@@
 %\end{itemize}
+
+%-----------------------------------------------------------------------------------
+\subsection{Workflow}
+\label{sub:workflow}
+
+Within the main download package, several directories organize the ODT package.
+The \texttt{source}, \texttt{build}, and \texttt{run} directories contain the ODT source code, compilation tools, and run scripts, respectively.
+The \texttt{input} directory contains subdirectories corresponding to several possible case types, each populated with an appropriate input files.
+The \texttt{data} directory, initially empty, holds the raw data files and runtime information generated by ODT, as well as post-processed data files generated from within the \texttt{post} directory.
+Finally, the \texttt{doc} directory contains documentation optionally generated by Doxygen \cite{vanHeesch_2018} during the build process.
+
+DETAILS GO HERE
+
+% reference video that we will eventually make?
 
@@
 
-This work is supported in part by the National Science Foundation under Grant No. CBET-1403403.
+This work was supported in part by the National Science Foundation under Grant No. CBET-1403403.
 

### 2020-05-30 manuscript/manuscript.tex
Drafting text of workflow section. Unfinished.

@@
 
+This section outlines the process a user would go through in order to successfully build the ODT code and run a simulation.
+For more details, please see the package documentation.
+ODT is a standalone, self-contained package, and users interact with its files primarily via the command line rather than a graphical interface.
+
 Within the main download package, several directories organize the ODT package.
@@
 Finally, the \texttt{doc} directory contains documentation optionally generated by Doxygen \cite{vanHeesch_2018} during the build process.
+
+\subsubsection{Building ODT}
+
+The ODT build process is relatively automated through CMake.
+First, navigate to the \texttt{build} directory and edit the CMake configuration file.
+Note that the user must specify which chemical mechanism to compile with before building the code.
+In order to run simulations with different chemical mechanisms, the code must be recompiled, including the CMake configuration files, between simulations, whereas this is not required when other variables are changed.
+This is a known inconsistency that will be changed in future code releases.
+The CMake configuration file also specifies Cantera's location and must be changed to reflect the local installation location.
+Once the settings are correct, the user runs CMake to apply these changes.
+
+YAML is required in order to process input files.
+If it has not yet been installed, it is built and installed at this point.
+For convenience, the ODT package includes the appropriate files and automates this process.
+YAML need only be installed once for a given instance of the ODT package.
+Rebuilding the ODT code with CMake does not affect the YAML installation.
+
+Once CMake and YAML have been prepared, the user can build the ODT code with the appropriate \texttt{make} command.
+There is no associated \texttt{install} command that needs to be run.
+The most common errors that occur during the build process concern incorrect file paths or incomplete installation of precursor packages.
+See the build documentation for troubleshooting help.
+
+Once the code is built, the user may optionally build a local copy of the documentation via Doxygen, which must be previously installed.
+This step is not required in order to run the ODT code.
+As an alternative, documentation can be accessed via \texttt{README} files within the code or at the code repository wiki.
+
+\subsubsection{Input files}
+
+User-modified input files are located within the \texttt{input} directory, which contains subdirectories that correspond to various case types that can be run with ODT.
+At minimum, a case's subdirectory contains an \texttt{input.yaml} file, but may contain other files or subfolders.
+ODT has the capability to restart a simulation from a specified time or state.
+To use this function, a raw data file at the required state must be copied to the input case directory and renamed \texttt{restart.dat}.
+For an example, please see the \texttt{jetFlame/flameD} case.
+Note that the user must also change the \texttt{Lrestart} parameter within the \texttt{input.yaml} file in order to use the restart feature.
+Input case directories may also contain subdirectories with supplemental information or input file examples; only the \texttt{input.yaml} file located in the base case input directory is used in a simulation.
+
+The \texttt{input} directory also contains the \texttt{gas\textunderscore mechanisms} subdirectory, which contains chemical mechanism files in XML format that can be used in reacting flow cases.
+For cases in which a chemical mechanism is not required, the \texttt{not\textunderscore used.xml} mechanism file is specified in the appropriate \texttt{input.yaml} file in place of other mechanisms.
+Note that the chemical mechanism chosen for the case and specified in the input file must match the mechanism specified in the Cmake configuration file during the ODT build process.
+
+Input files contain simulation parameters in a human-readable format parsed by YAML.
+Not all of the parameters in an input file may be used in a given simulation.
+An overview of possible ODT parameters will be covered here, but does not represent all the possibilities or functions of ODT; please see the associated documentation for more information.
+Input files are divided into sections, several of which are common to all \texttt{input.yaml} files; these are summarized in Table \ref{tab:input_sections}.
+Details about individual parameters, including usage and typical values, are covered in the documentation.
+
+\begin{table}
+\begin{tabular}{|l|p{4.1in}|}
+\hline
+Section 				& Description 	\\
+\hline
+\texttt{params}* 		& General parameters, including simulation length, domain size, and ODT parameters ($C$, $Z$, $\beta_{LES}$) \\
+\texttt{radParams}		& Radiation parameters; only relevant to reacting flow cases (i.e. jet flames) \\
+\texttt{streamProps}	& Stream properties; used when there are two or more separate streams (i.e. non-premixed jets)\\
+\texttt{bcCond}* 		& Boundary conditions for velocity and temperature (where required) \\
+\texttt{initParams} 	& Case-specific initialization parameters, usually flow geometry and stream velocities \\
+\texttt{dumpTimes}*		& List of simulation time steps at which to output data files \\
+\hline
+\end{tabular}
+\caption{Common sections present in \texttt{input.yaml} files.
+Sections marked with a * should be present in every \texttt{input.yaml} file regardless of case type.
+Sections usually appear in this order, but this is not required.}
+\label{tab:input_sections}
+\end{table}
+
+Prior to running a simulation, the user must select and modify the appropriate \texttt{input.yaml} file to reflect the desired conditions.
+The default values already present in the input files represent general parameters that may be used to run a successful simulation of that case type.
+
+\subsubsection{Running ODT}
 
@@
 
-%\subsection{General Workflow}
-%\label{sub:workflow}
-%
-%Every ODT simulation shares common steps to a successful run. 
-%\begin{enumerate}
-%	\item Build and compile the code. 
-%	\item Choose a case type and chemical mechanism (when required) and alter the appropriate input file(s). 
-%	\item Within the \texttt{run} directory, alter the run script to be used with a case name and other required information.
-%	\item Run the case from the \texttt{run} directory using the chosen run script.
-%	\item Run the appropriate post-processing scripts, located in the \texttt{post} directory, on the raw data for interpretation and visualization.
-%\end{enumerate}
-
+%-----------------------------------------------------------------------------------
 \subsection{Pipe Flow}

### 2020-06-06 manuscript/manuscript.tex
Finished drafting workflow section. Added figure for data directory structure.

--- 2020-05-26 manuscript/manuscript.tex
@@
 The package also contains auxiliary data processing and visualization tools, written mostly in Python.
-The post-processing tools are case-specific but will be  addressed in Section~\ref{sub:workflow}.
+The post-processing tools are case-specific but will be  addressed generally in Section~\ref{sub:workflow}.
 
@@
 	\includegraphics[width=\textwidth]{../figures/odt_flow_chart/odt_flow_chart.png} 
-	\caption{Basic structure of the ODT code.
-For clarity and brevity, this diagram makes two major assumptions: first, that diffusion advancement in the \texttt{micromixer} uses an explicit solution method; and second, that the eddy event sampled by the \texttt{eddy} object passes all rejection tests before being applied to the domain.}
+	\caption{Structural outline of the ODT code, including its major class objects.
+For brevity, this diagram makes two simplifications.
+First, it assumes that diffusive advancement in the \texttt{micromixer} uses an explicit solution method; in practice, users specify either an explicit, semi-implicit, or Strang split method.
+Second, it implies that all of the eddy events sampled by the \texttt{eddy} object are applied to the domain; in reality, eddy events are filtered through several rejection tests (omitted from this figure for clarity) before acceptance and application to the domain.}
 	\label{fig:flowchart}
@@
 
-Within the main download package, several directories organize the ODT package.
+This section outlines the process a user goes through in order to successfully build the ODT code and run a simulation.
+For more details, please see the package documentation.
+ODT is a standalone, self-contained package, and users interact with its files primarily via the command line rather than a graphical interface.
+
+Within the main download package, several directories organize the ODT code.
 The \texttt{source}, \texttt{build}, and \texttt{run} directories contain the ODT source code, compilation tools, and run scripts, respectively.
@@
 
-DETAILS GO HERE
+\subsubsection{Building ODT}
+
+The ODT build process is automated with CMake.
+First, the user navigates to the \texttt{build} directory and edits the CMake configuration file.
+The CMake configuration file specifies Cantera's location and must be changed to reflect the local installation location.
+Note that the user must also specify which chemical mechanism the code will compile with.
+In order to run simulations with different chemical mechanisms, the code must be recompiled, including the CMake configuration files, between simulations, whereas this is not required when other variables are changed.
+This is a known inconsistency that we plan to address in future code releases.
+Once the configuration settings are updated, the user runs CMake to apply the changes.
+
+YAML is required in order to process input files.
+If it has not yet been installed, it must be built and installed at this point.
+For convenience, the ODT package automates this process.
+YAML need only be installed once for a given instance of the ODT package.
+Rebuilding the ODT code with CMake does not affect the YAML installation.
+
+Once CMake and YAML have been prepared, the user can build the ODT code with the \texttt{make} command.
+There is no associated \texttt{install} command that needs to be run after the \texttt{make} command.
+The most common errors that occur during the build process concern incorrect file paths or incomplete installation of required packages.
+See the build documentation for troubleshooting help.
+
+Once the code is built, the user may optionally build a local copy of the documentation via Doxygen, which must be previously installed.
+This step is not required in order to run the ODT code.
+As an alternative, documentation can be accessed via \texttt{README} files within the code or at the code repository wiki.
+
+\subsubsection{Input files}
+
+User-modified input files are located within the \texttt{input} directory, which contains subdirectories that correspond to various case types that can be run with ODT.
+At minimum, a case's subdirectory must contain an \texttt{input.yaml} file, but may contain other files or subfolders with supplementary information.
+%ODT has the capability to restart a simulation from a specified time or state.
+To use this function, a raw data file at the required state must be copied to the input case directory and renamed \texttt{restart.dat}.
+For an example, please see the \texttt{jetFlame/flameD} case.
+Note that the user must also change the \texttt{Lrestart} parameter within the \texttt{input.yaml} file in order to use the restart feature.
+
+The \texttt{input} directory also contains the \texttt{gas\textunderscore mechanisms} subdirectory, which contains chemical mechanism files that can be used in reacting flow cases.
+For cases in which a chemical mechanism is not required, the \texttt{not\textunderscore used.xml} mechanism file is specified in \texttt{input.yaml}.
+Note that the chemical mechanism chosen for the case and specified in the input file must match the mechanism specified in the CMake configuration file during the ODT build process.
+
+Input files contain simulation parameters in a human-readable format parsed by YAML.
+Not all of the parameters in an input file may be used in a given simulation.
+Within \texttt{input.yaml}, parameters are organized into sections, several of which are common to all input files.
+Details about individual parameters, including usage and typical values, are covered in the documentation.
+Prior to running a simulation, users must select and modify the appropriate \texttt{input.yaml} file to reflect the desired simulation conditions.
+The default values present in the input files represent general parameters that may be used to run a successful simulation of that case type.
+
+%An overview of possible ODT parameters will be covered here, but does not represent all the possibilities or functions of ODT; please see the associated documentation for more information.
+Input files are divided into sections, several of which are common to all \texttt{input.yaml} files; these are summarized in Table \ref{tab:input_sections}.
+
+%\begin{table}
+%\begin{tabular}{|l|p{4.1in}|}
+%\hline
+%Section 				& Description 	\\
+%\hline
+%\texttt{params}* 		& General parameters, including simulation length, domain size, and ODT parameters ($C$, $Z$, $\beta_{LES}$) \\
+%\texttt{radParams}		& Radiation parameters; only relevant to reacting flow cases (i.e. jet flames) \\
+%\texttt{streamProps}	& Stream properties; used when there are two or more separate streams (i.e. non-premixed jets)\\
+%\texttt{bcCond}* 		& Boundary conditions for velocity and temperature (where required) \\
+%\texttt{initParams} 	& Case-specific initialization parameters, usually flow geometry and stream velocities \\
+%\texttt{dumpTimes}*		& List of simulation time steps at which to output data files \\
+%\hline
+%\end{tabular}
+%\caption{Common sections present in \texttt{input.yaml} files.
+Sections marked with a * should be present in every \texttt{input.yaml} file regardless of case type.
+Sections usually appear in this order, but this is not required.}
+%\label{tab:input_sections}
+%\end{table}
+
+\subsubsection{Running ODT}
+
+To run a simulation, users must then navigate to the \texttt{run} directory, which contains the \texttt{odt.x} executable and several possible run scripts.
+The simplest option is \texttt{runOneRlz.sh}, which runs one realization of ODT in the specified configuration.
+In this run script, the user must alter two variables near the top of the file: \texttt{inputDir}, which specifies which input directory and files to use; and \texttt{caseName}, which provides a name for the simulation and the data files it outputs.
+The \texttt{runManyRlz.sh} script runs many realizations in serial, one after the other; it differs from \texttt{runOneRlz.sh} only in that the user must also alter the \texttt{nRlz} variable, which specifies the number of realizations to run.
+To run the simulation with either \texttt{runOneRlz.sh} or \texttt{runManyRlz.sh}, save the run script and execute it at the command line.
+Users will see some output on the command line, but no data, which is instead output to the \texttt{data} directory.
+
+ODT simulations can also be run in parallel using MPI.
+Two run scripts, \texttt{slrmJob.sh} and \texttt{slrmJob\textunderscore array.sh}, are configured using SLURM \cite{Yoo_2003}, a common workload manager used for massively parallel computing resources.
+This allows many ODT realizations to run in parallel rather than in serial, reducing overall simulation time.
+Individual realizations are independent and do not affect one another, but users must take care with case names and input file changes to ensure that individual realizations or entire cases are not overridden accidentally.
+
+\subsubsection{Data files and post-processing}
+
+For a given simulation, data is output to the \texttt{data} directory, which contains subdirectories for each simulation, specified by the \texttt{caseName} variable in the run script.
+Figure \ref{fig:data_folder_structure} illustrates the structure of the \texttt{data} directory and the locations of files within it.
+Each case folder is subdivided into \texttt{input}, \texttt{runtime}, \texttt{data}, and \texttt{post}.
+The \texttt{input} folder contains a copy of the input files used for the simulation, \texttt{runtime} contains runtime output information, \texttt{data} contains the raw data files, and \texttt{post} contains post-processed data files once they are generated.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../figures/data_folder_structure/data_folder_structure.png} 
+	\caption{Data folder structure and file locations.
+Boxes indicate folders and ovals indicate files.
+For a given simulation, \texttt{caseName} will be replaced with the case name specified in the run script.
+The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number.
+The number attached to \texttt{dmp} files indicates the output time step, or "dump" time, of the data file.
+These correspond to the order of the time steps listed in \texttt{input.yaml}.}
+	\label{fig:data_folder_structure}
+\end{figure}
+
+To use post-processing tools, navigate to the \texttt{post} directory.
+Within the \texttt{post} directory, data processing tools are organized by case type, which is specified in \texttt{input.yaml} and determines case-specific variables and simulation setup parameters (refer to the \texttt{domaincase} object in Figure \ref{fig:flowchart}).
+Each set of post-processing tools is different, but may contain some combination of Python scripts (often coordinated by a \texttt{driver.py} file), experimental data files for comparison and plot generation, or other supplementary files.
+Post-processed data and generated plots are deposited in the \texttt{data} directory, within the appropriate \texttt{caseName/post} folder.
+For more information on using the provided post-processing tools, please refer to the documentation.
 

### 2020-07-17 manuscript/manuscript.tex
Adding text to example sections

@@
 
+To replicate this example case, build the code with the \texttt{CHEMISTRY = SIMPLEDLR} flag in the \texttt{user\textunderscore config} file and edit the desired run script with \texttt{inputDir = "../input/jetFlame/DLR\textunderscore A"} and a new case name such as \texttt{caseName = "jetFlame\textunderscore example"}.
+The input file for this case, located at \texttt{ODT/input/jetFlame/DLR\textunderscore A/input.yaml}, already contains the appropriate parameters and does not need to be modified to match this example case.
+POST PROCESSING INSTRUCTIONS GO HERE.
+
 %Present the major functionalities of the software. 

### 2020-08-31 manuscript/manuscript.tex
Adding figures for DLR example case

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Example Cases}
+\section{Example Case: Canonical Jet Flame}
 \label{sec:examples}
 
-%-----------------------------------------------------------------------------------
-\subsection{Pipe Flow}
-\label{sub:pipeflow}
-
-% TEXT COPIED/MODIFIED FROM CYLINDRICAL ODT PAPER
-First, we present an incompressible pipe flow simulation using the temporal, cylindrical ODT formulation.
+%%-----------------------------------------------------------------------------------
+%\subsection{Pipe Flow}
+%\label{sub:pipeflow}
+%
+%% TEXT COPIED/MODIFIED FROM CYLINDRICAL ODT PAPER
+%First, we present an incompressible pipe flow simulation using the temporal, cylindrical ODT formulation.
 Results for three different friction Reynolds numbers ($Re_\tau$ = 550, 1000, 2000) are compared to DNS results from El Khoury et al.
@@
 Using initial conditions with uniform velocity profiles, simulations were run until a state of developed flow was achieved, at which point data were gathered until statistical convergence for the root mean square (RMS) velocity difference from the mean profiles occurred.
-
-The simulations were performed with ODT parameters $C = 5$ and $Z = 350$ for the temporal ODT formulation. 
-%Additionally, a restriction was imposed on the eddy size range by selecting eddies only up to a maximum normalized size of Le,max/D = 1/3.
+%
+%The simulations were performed with ODT parameters $C = 5$ and $Z = 350$ for the temporal ODT formulation. 
+%%Additionally, a restriction was imposed on the eddy size range by selecting eddies only up to a maximum normalized size of Le,max/D = 1/3.
 This restriction limits the eddy size by construction, as opposed to the large-eddy suppression mechanism commonly used in ODT simulations [27,45].
-The values of C and Z
-%and Le,max/D 
-were adjusted to give good agreement of the ODT results compared to the DNS.
+%The values of C and Z
+%%and Le,max/D 
+%were adjusted to give good agreement of the ODT results compared to the DNS.
 Schmidt et al.
 \cite{Schmidt_2003} showed that higher $Z$ results in the buffer-layer being located further from the wall, and increasing $C$ results in a lower slope of the mean streamwise velocity in the log-layer.
-%and higher Le,max/D gives a smaller mean streamwise velocity in the wake region.
-
-RESULTS AND PLOTS GO HERE
-
-\subsection{Non-reacting Jet }
-\label{sub:nonreactingjet}
-
-% TEXT COPIED/MODIFIED FROM CYLINDRICAL ODT PAPER
-Here, we present ODT simulation results for a non-reacting round, turbulent jet compared to the experimental data of Hussein et al.
+%%and higher Le,max/D gives a smaller mean streamwise velocity in the wake region.
+%
+%RESULTS AND PLOTS GO HERE
+%
+%\subsection{Non-reacting Jet }
+%\label{sub:nonreactingjet}
+%
+%% TEXT COPIED/MODIFIED FROM CYLINDRICAL ODT PAPER
+%Here, we present ODT simulation results for a non-reacting round, turbulent jet compared to the experimental data of Hussein et al.
 \cite{Hussein_1994}.
@@
 In the spatial formulation of ODT, the streamwise velocity must be positive everywhere on the line, so a small minimum velocity of $v_{min} = 0.1$m$\cdot$s$^{-1}$ is specified and added across the entire velocity profile.
-
-ODT simulations were performed with parameters $C = 5.25$, $\beta_{LES} = 3.5$, and $Z=400$.
+%
+%ODT simulations were performed with parameters $C = 5.25$, $\beta_{LES} = 3.5$, and $Z=400$.
 The value of $Z$ is the same as the spatial simulations in \cite{Monson_2016}, and the values of $C$ and $\beta_{LES}$ were adjusted to give good agreement with the experimental data.
@@
 This illustrates a level of robustness in the ODT parameters and suggests that intermediate values could be successfully applied in both configurations.
-
-1024 independent ODT realizations were performed and results were ensemble averaged.
+%
+%1024 independent ODT realizations were performed and results were ensemble averaged.
 All quantities are normalized consistent with jet similarity scaling.
 Downstream locations are normalized by the jet diameter $D$, and radial locations are normalized by $(y-y_0)$, where $y$ is the downstream location and $y_0 = 4D$ is the virtual origin used in \cite{Hussein_1994}.
-
-RESULTS AND PLOTS GO HERE
-
-%In the figure, $v_0$ is the jet exit velocity and $v_{cL}$ is the local mean axial centerline velocity.
+%
+%RESULTS AND PLOTS GO HERE
+%
+%%In the figure, $v_0$ is the jet exit velocity and $v_{cL}$ is the local mean axial centerline velocity.
 Here, $r$ is used to denote both the experimental radial location and the ODT line position $x$.
-
-%It is worth noting that the vrms profile depends somewhat on the ODT parameters selected.
+%
+%%It is worth noting that the vrms profile depends somewhat on the ODT parameters selected.
 Hewson and Kerstein [15] demonstrated that mean centerline values of mixture fraction were insensitive to C and βles provided their ratio was kept constant.
@@
 Plots (b) and (c) show axial location
-
-%The centerline velocity decay and radial profiles show good agreement, as with the previous cases, with a slight improvement in the radial velocity profile.
+%
+%%The centerline velocity decay and radial profiles show good agreement, as with the previous cases, with a slight improvement in the radial velocity profile.
 The vrms profiles are significantly improved along the centerline compared to TMA and TMB.
@@
 
-\subsection{Jet Flame}
-\label{sub:jetflame}
+%\subsection{Jet Flame}
+%\label{sub:jetflame}
 
-% TEXT COPIED FROM CYLINDRICAL ODT PAPER
 ODT is uniquely suited for reacting flow simulations.
@@
 
-RESULTS AND PLOTS GO HERE
+\begin{figure}
+	\begin{center}
+		\begin{tabular}{ccc}
+			(a) & (b) & (c) \\
+			\includegraphics[width=2in]{../figures/cl_uvel_DLR_test_11.pdf} &
+			\includegraphics[width=2in]{../figures/cl_mixf_DLR_test_11.pdf} &
+			\includegraphics[width=2in]{../figures/cl_temp_DLR_test_11.pdf}
+		\end{tabular}
+	\end{center}
+\caption{DLR jet flame example case results}
+\end{figure}
 

### 2020-09-07 manuscript/manuscript.tex
Added y axis labels to DLR figures. Finished text of DLR example case section.

@@
 This simulation uses the experimentally reported velocity profiles and jet dimensions.
-In the non-reacting case, a small minimum velocity was added uniformly to the velocity profile; no such addition is required here because of the slow-moving coflow air stream that issues alongside the reacting jet.
+%In the non-reacting case, a small minimum velocity was added uniformly to the velocity profile; no such addition is required here because of the slow-moving coflow air stream that issues alongside the reacting jet.
 %The ODT simulation includes the buoyant source term but not the streamwise pressure gradient in Eq. (25). 
@@
 \end{align}
-These assumptions are not reasonable for the DLR-A flame, but they allow us to illustrate ODT in a reacting jet configuration with variable properties and heat release, which is the primary purpose of this example case.
-More complex combustion reaction mechanisms are available within the source code and can be accessed by changing the appropriate input file parameter.
+These assumptions are not reasonable for the DLR-A flame, but they allow us to illustrate ODT in a reacting jet configuration with variable properties and heat release.
+More complex combustion reaction mechanisms are available within the source code and can be accessed by changing the appropriate input file parameters.
 
 This simulation uses ODT parameters $C=20$, $\beta_{LES}=17$, and $Z=400$.
-The values of $C$ and $\beta_{LES}$ were adjusted to give good agreement with the experimental data, and the value of $Z$ is the same as it was for the non-reacting jet in Section \ref{sub:nonreactingjet}.
+The values of $C$ and $\beta_{LES}$ were adjusted to give good agreement with the experimental data, and the value of $Z$ is the same as the spatial simulations in \cite{Monson_2016}.
 1024 independent flow realizations were performed in parallel and the results ensemble averaged.
@@
 	\end{center}
-\caption{DLR jet flame example case results}
+	\label{fig:dlr_example_results}
+	\caption{DLR jet flame example case results: (a) mean axial velocity and RMS velocity along the centerline versus downstream location; (b) mean axial mixture fraction and RMS mixture fraction along the centerline versus downstream location; (c) mean axial temperature (K) and RMS temperature (K) along the centerline versus downstream location.}
 \end{figure}
+
+Figure~\ref{fig:dlr_example_results} displays the simulation results: axial mean and centerline values for (a) axial velocity $v$, (b) mixture fraction $\xi$, and (c) temperature $T$.
+The ODT results track the experimental data well for all three variables.
+The centerline temperature peaks about 100 K above the experimental data, but this small difference can be attributed to thermal radiation (which was neglected in this simulation) and the assumption that reactions proceed to the products of complete combustion rather than their equilibrium state.
+The centerline velocity shows a fast initial decrease that can be attributed to diffusion.
+Similarly, the increase in centerline velocity RMS values is delayed; this occurs due to the elapsed time model for large eddy suppression, which limits disturbances in the early stages of the flow to small eddies that occur on the jet edges away from the centerline.
 
@@
 The input file for this case, located at \texttt{ODT/input/jetFlame/DLR\textunderscore A/input.yaml}, already contains the appropriate parameters and does not need to be modified to match this example case.
-POST PROCESSING INSTRUCTIONS GO HERE.
+Please see the code documentation for data post-processing instructions.
 

### 2020-09-18 manuscript/manuscript.tex
DOL edits to manuscript and references; deleting manuscript.pdf, which can be compiled as needed.

@@
 \restylefloat{table}
+
+\usepackage{hyperref}
 
@@
 \hline
-C2 & Permanent link to code/repository used for this code version & $github.com/BYUignite/ODT$ \\
+C2 & Permanent link to code/repository used for this code version & \href{https://github.com/BYUignite/ODT}{https://github.com/BYUignite/ODT} \\
 \hline
@@
 \hline
-C8 & If available Link to developer documentation/manual & N/A \\
+C8 & If available Link to developer documentation/manual & \href{https://byuignite.github.io/ODT/doxygen/html/style_guide.html}{style guide} \\
 \hline
-C9 & Support email for questions & davidlignellbyu.edu \\
+C9 & Support email for questions & davidlignell@byu.edu \\
 \hline
@@
 The one-dimensional turbulence model (ODT) functionally reverses the LES approach, modeling large-scale turbulent advection and directly resolving small-scale flow structures, simulating the full range of length and time scales in a single dimension.
-Because large-scale structures are much easier to study and model than small-scale structures, ODT mitigates or sidesteps many of the subgrid modeling issues that complicate LES.
+Depending on the configuration, large-scale structures can be easier to model than small-scale structures (especially when reaction is present.
+ODT's direct resolution (in one dimension) of fine scales removes subgrid modeling issues that complicate LES.
 Previous studies show that ODT can attain accuracy comparable to DNS at a fraction of the computational cost \cite{Lignell_2015,Abboud_2015}, making it an attractive tool for simulating turbulent flows.
@@
 \end{equation}
-Here, $j_{\beta}$ is the diffusion flux of scalar $\beta$ across the cell face area $A_x$ where the subscripts $e$ and $w$ refer to the "east" and "west" faces of the grid cell, respectively.
+Here, $j_{\beta}$ is the diffusion flux of scalar $\beta$ across the cell face area $A_x$ where the subscripts $e$ and $w$ refer to the ``east" and ``west" faces of a given grid cell, respectively.
 $S_{\beta}$ is the Lagrangian source term derived from the conservation law for $\beta$, $\rho$ represents mass density, and $V$ represents cell volume.
-In practice, we refer to the left hand term on the right side of Equation~\ref{eq:transport} as the "mixing term" and the right hand term on the right side of Equation~\ref{eq:transport} as the "source term".
-The generic transport equation differs slightly in the spatial formulation of ODT, but its form is the same, so we omit it here for brevity.
+In practice, we refer to the left hand term on the right side of Equation~\ref{eq:transport} as the ``mixing term" and the right hand term on the right side of Equation~\ref{eq:transport} as the ``source term".
+The generic transport equation differs slightly in the spatial formulation of ODT, but its form is similar, so we omit it here for brevity.
 The system of ordinary differential equations (ODEs) that results is well behaved at all grid points and in all geometries in their finite-volume forms.
@@
 Eddy events occur as a Poisson process in accordance with their eddy rates, where a given eddy event of size $l$ and location $x_0$ has an eddy timescale $t$ and an associated eddy rate $1/t$.
-Three user-defined ODT parameters control the eddy event process: the eddy rate parameter $C$ scales the rate of occurrence of the eddies; the viscous penalty parameter $Z$ suppresses small eddies; and the large eddy suppression parameter $\beta$ constrains eddies such that they do not reach over the elapsed simulation time.
+Three user-defined ODT parameters control the eddy event process: the eddy rate parameter $C$ scales the rate of occurrence of the eddies; the viscous penalty parameter $Z$ suppresses small eddies; and the large eddy suppression parameter $\beta_{LES}$ constrains eddies to those with timescales proportional to the elapsed simulation time.
 Sampled eddies that do not fit the defined parameters are rejected and not applied to the domain.
 
-Eddy events modify domain variables using triplet maps, as illustrated for a cylindrical domain in Figure~\ref{fig:tripletmap}.
-For a region of eddy size $l$, the domain is copied to create three map images; the three images are then placed back to back with the middle image inverted to maintain continuity, and the composite is reapplied to the domain.
-This process applies to all transported variables on the domain.
-Applied properly, the triplet map increases scalar gradients and decreases length scales consistent with the application of turbulent eddies in real flows, conserves all quantities and their statistical moments, and maintains continuity in property profiles.
-Subsequent eddies in the same region will result in a cascade of scales, and eddy rates depend on eddy size and the local kinetic energy such that they follow turbulent cascade scaling laws.
+Eddy events modify domain variables using ``triplet maps", as illustrated for a cylindrical domain in Figure~\ref{fig:tripletmap}.
+In an eddy region of size $l$, transported property profiles are modified (mapped) by making three copies, compressing each spatially by a factor of three, then lining these up with the middle copy spatially reversed.
+This map is continuous and conservers all quantities and statistical moments, increases scalar gradients and decreases length scales consistent with turbulent eddies in real flows.
+Subsequent eddies in the same region will result in a cascade of scales.
+The eddy rates, used in the sampling and selection of eddies depend on eddy size and the local kinetic energy consistent with turbulent scaling laws.
 
@@
 Eddy events occur concurrently with diffusive advancement via solution of the system of unsteady one-dimensional transport equations.
-In this way, the ODT code marches in time or space until it reaches its end point.
+In this way, the ODT code marches in time (or space) until it reaches its end point.
 Due to the stochastic nature of eddy events, each ODT simulation, or realization, is different, even when it is provided with the same input parameters.
-In order to obtain statistically stable data for a given set of parameters, we run many realizations with the same input parameters and time-average them.
+In order to obtain statistically stable data for a given set of parameters, we run many realizations with the same input parameters, and then gather statistics over these realizations.
 This is done via post-processing tools, which are provided in the ODT package.
@@
 Three primary objects handle the code's main functions: the \texttt{solver}, \texttt{micromixer}, and \texttt{eddy} objects.
-The \texttt{solver} coordinates the ODT solution process, marching along the simulation time and invoking diffusive advancement and eddy events when appropriate.
+The \texttt{solver} coordinates the ODT solution process, marching along the simulation time and invoking diffusive advancement and eddy events.
 The \texttt{micromixer} handles diffusive advancement by setting step sizes, interacting with the transported domain variables, and solving the system of ODEs defined by Equation~\ref{eq:transport} (or its equivalent in the spatial formulation).
-The \texttt{micromixer} includes three solution methods that can be specified in \texttt{input.yaml}, each appropriate for various case types: a first-order explicit Euler method (pictured in Figure~\ref{fig:flowchart}); a first-order semi-implicit method that uses CVODE~\cite{Hindmarsh_2020} to advance coupled ODEs in individual grid cells, integrated sequentially; and a second-order Strang splitting method \cite{Strang_1968} good for treating stiff chemistry.
-In reacting flow cases, chemical kinetics are handled by Cantera \cite{Goodwin_2018}, which uses transported variable values---enthalpy and gas species composition, for instance---to specify local scalar values such as gas temperature or density, which can affect flow properties.
+The \texttt{micromixer} includes three solution methods that can be specified in \texttt{input.yaml}: a first-order explicit Euler method (pictured in Figure~\ref{fig:flowchart}); a first-order semi-implicit method; and a second order Strang splitting method~\cite{Strang_1968}.
+The latter two methods are useful for treating stiff chemistry, with source terms integrated using CVODE~\cite{Hindmarsh_2020}.
+In reacting flow cases, enthalpy and chemisal species are transported, with physical properties and kinetic rates computed with Cantera~\cite{Goodwin_2018}.
 The \texttt{micromixer} is also the code's primary point of interaction with the \texttt{mesher} object (not pictured in Figure~\ref{fig:flowchart}), which manages the adaptive grid functions.
@@
 The ODT build process is automated with CMake.
-First, the user navigates to the \texttt{build} directory and edits the CMake configuration file.
+The user navigates to the \texttt{build} directory and edits the CMake configuration file.
 The CMake configuration file specifies Cantera's location and must be changed to reflect the local installation location.
-Note that the user must also specify which chemical mechanism the code will compile with.
-In order to run simulations with different chemical mechanisms, the code must be recompiled, including the CMake configuration files, between simulations, whereas this is not required when other variables are changed.
-This is a known inconsistency that we plan to address in future code releases.
+For reacting flows, the chemical reation rates can be computed by Cantera (the default), or a from a user-specified function, specified at compile time.
 Once the configuration settings are updated, the user runs CMake to apply the changes.
@@
 
-Once CMake and YAML have been prepared, the user can build the ODT code with the \texttt{make} command.
-There is no associated \texttt{install} command that needs to be run after the \texttt{make} command.
-The most common errors that occur during the build process concern incorrect file paths or incomplete installation of required packages.
+Once CMake and YAML have been prepared, the user can build the ODT code with the \texttt{make} command, which places the code executable in the \texttt{run} directory.
+The most common errors that occur during the build process involve incorrect file paths or incomplete installation of required packages.
 See the build documentation for troubleshooting help.
@@
 This step is not required in order to run the ODT code.
-As an alternative, documentation can be accessed via \texttt{README} files within the code or at the code repository wiki.
+As an alternative, documentation can be accessed at the code repository wiki.
 
@@
 User-modified input files are located within the \texttt{input} directory, which contains subdirectories that correspond to various case types that can be run with ODT.
-At minimum, a case's subdirectory must contain an \texttt{input.yaml} file, but may contain other files or subfolders with supplementary information.
+At minimum, a case's subdirectory must contain an \texttt{input.yaml} file, but may contain other files, or subfolders with supplementary information.
 %ODT has the capability to restart a simulation from a specified time or state.
@@
 Input files contain simulation parameters in a human-readable format parsed by YAML.
-Not all of the parameters in an input file may be used in a given simulation.
+Details about individual parameters, including usage and typical values, are covered in the documentation.
 Within \texttt{input.yaml}, parameters are organized into sections, several of which are common to all input files.
-Details about individual parameters, including usage and typical values, are covered in the documentation.
-Prior to running a simulation, users must select and modify the appropriate \texttt{input.yaml} file to reflect the desired simulation conditions.
-The default values present in the input files represent general parameters that may be used to run a successful simulation of that case type.
+Parameter values present in the provided input files may be considered defaults that may be used to run a successful simulation of that case type.
+General code parameters are stored in the \texttt{params} class.
+Variables needed in a simulation but not provided in an input file (not recommended), are either given defaults specified in the \texttt{params} class, or result in an error message.
 
@@
 The \texttt{runManyRlz.sh} script runs many realizations in serial, one after the other; it differs from \texttt{runOneRlz.sh} only in that the user must also alter the \texttt{nRlz} variable, which specifies the number of realizations to run.
+Realizations differ by having different random seeds (specified in the input file).
+The random seed can either be randomized, or directly specified.
 To run the simulation with either \texttt{runOneRlz.sh} or \texttt{runManyRlz.sh}, save the run script and execute it at the command line.
@@
 This allows many ODT realizations to run in parallel rather than in serial, reducing overall simulation time.
-Individual realizations are independent and do not affect one another, but users must take care with case names and input file changes to ensure that individual realizations or entire cases are not overridden accidentally.
+Individual realizations are independent (\emph{embarrassingly parallel}), but users must take care with case names and input file changes to ensure that individual realizations or entire cases are not overridden accidentally.
 
@@
 Each case folder is subdivided into \texttt{input}, \texttt{runtime}, \texttt{data}, and \texttt{post}.
-The \texttt{input} folder contains a copy of the input files used for the simulation, \texttt{runtime} contains runtime output information, \texttt{data} contains the raw data files, and \texttt{post} contains post-processed data files once they are generated.
+The \texttt{input} folder contains a copy of the input files used for the simulation; \texttt{runtime} contains runtime output information, such as eddy event information ; \texttt{data} contains the raw data files; and \texttt{post} contains post-processed data files once they are generated.
 
@@
 The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number.
-The number attached to \texttt{dmp} files indicates the output time step, or "dump" time, of the data file.
+The number attached to \texttt{dmp} files indicates the output time step, or ``dump" time, of the data file.
 These correspond to the order of the time steps listed in \texttt{input.yaml}.}
@@
 Post-processed data and generated plots are deposited in the \texttt{data} directory, within the appropriate \texttt{caseName/post} folder.
-For more information on using the provided post-processing tools, please refer to the documentation.
+%For more information on using the provided post-processing tools, please refer to the documentation.
 
@@
 \end{align}
-These assumptions are not reasonable for the DLR-A flame, but they allow us to illustrate ODT in a reacting jet configuration with variable properties and heat release.
+These assumptions are reasonable for the DLR-A flame, especially with the purpose of illustrating ODT in a reacting jet configuration with variable properties and heat release.
 More complex combustion reaction mechanisms are available within the source code and can be accessed by changing the appropriate input file parameters.
@@
 			(a) & (b) & (c) \\
-			\includegraphics[width=2in]{../figures/cl_uvel_DLR_test_11.pdf} &
-			\includegraphics[width=2in]{../figures/cl_mixf_DLR_test_11.pdf} &
-			\includegraphics[width=2in]{../figures/cl_temp_DLR_test_11.pdf}
+			\includegraphics[width=1.7in]{../figures/cl_uvel_DLR_test_11.pdf} &
+			\includegraphics[width=1.7in]{../figures/cl_mixf_DLR_test_11.pdf} &
+			\includegraphics[width=1.7in]{../figures/cl_temp_DLR_test_11.pdf}
 		\end{tabular}
@@
 To replicate this example case, build the code with the \texttt{CHEMISTRY = SIMPLEDLR} flag in the \texttt{user\textunderscore config} file and edit the desired run script with \texttt{inputDir = "../input/jetFlame/DLR\textunderscore A"} and a new case name such as \texttt{caseName = "jetFlame\textunderscore example"}.
-The input file for this case, located at \texttt{ODT/input/jetFlame/DLR\textunderscore A/input.yaml}, already contains the appropriate parameters and does not need to be modified to match this example case.
-Please see the code documentation for data post-processing instructions.
+The input file for this case, located at \texttt{ODT/input/jetFlame/DLR\textunderscore A/input.yaml}, contains the appropriate parameters and does not need to be modified to match this example case.
+See the code documentation for data post-processing instructions.
 
@@
 %No conflict of interest exists:
-We wish to confirm that there are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.
+There are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.
 
@@
 
-Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.
+Software information is provided in Table~\ref{t:software}.
+
+%Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.
 
@@
 \hline
-S1 & Current software version & 2.1 \\
+S1 & Current software version & 1.0 \\
 \hline
-S2 & Permanent link to executables of this version  & For example: $https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
+S2 & Permanent link to executables of this version  & For example: \href{https://github.com/BYUignite/ODT}{https://github.com/BYUignite/ODT} \\
 \hline
@@
 \hline
-S6 & If available, link to user manual - if formally published include a reference to the publication in the reference list & For example: $http://mozart.github.io/documentation/$ \\
+S6 & If available, link to user manual - if formally published include a reference to the publication in the reference list & \href{https://byuignite.github.io/ODT/doxygen/html/index.html}{https://byuignite.github.io/ODT/doxygen/html/index.html}\\
 \hline
@@
 \caption{Software metadata (optional)}
+\label{t:software}
 \end{table}

### 2020-09-18 manuscript/manuscript.tex
Flow charts converted to PDF instead of PNG. References updated.

@@
 	\centering
-	\includegraphics[width=\textwidth]{../figures/odt_flow_chart/odt_flow_chart.png} 
+	\includegraphics[width=\textwidth]{../figures/odt_flow_chart.pdf} 
 	\caption{Structural outline of the ODT code, including its major class objects.
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figures/data_folder_structure/data_folder_structure.png} 
+	\includegraphics[width=\textwidth]{../figures/data_folder_structure.pdf} 
 	\caption{Data folder structure and file locations.

### 2020-09-18 manuscript/manuscript.tex
Replacing triplet map figure, adding Monson reference.

--- 2020-09-18 manuscript/manuscript.tex
@@
 
-Eddy events modify domain variables using ``triplet maps", as illustrated for a cylindrical domain in Figure~\ref{fig:tripletmap}.
+Eddy events modify domain variables using ``triplet maps", as illustrated in Figure~\ref{fig:tripletmap}.
 In an eddy region of size $l$, transported property profiles are modified (mapped) by making three copies, compressing each spatially by a factor of three, then lining these up with the middle copy spatially reversed.
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figures/tripletmap/tripletmap.png} 
-	\caption{Schematic diagram of a cylindrical triplet map, adapted from~\cite{Lignell_2018}.
-Before the triplet map, the domain contains three grid cells of equal volume, while after the triplet map has been applied, the domain contains nine cells.
-The nine final cells are labeled according to the cells from which they originated and shaded to indicate that three map images were combined to create the final composite.}
+	\includegraphics[width=\textwidth]{../figures/tripletmap/tripmap.pdf} 
+    \caption{Schematic diagram of a triplet map.
+From left to right: (first pane) simulation of a single ``eddy", a two-dimensional Kelvin-Helmholz instability with a vertical white line-of-sight; (second pane) mixture fraction profile along the indicated line-of-sight before and after the eddy showing increased gradients and surface area; (third pane) a triplet map operates on a profile to produce a mapped profile with three copies, compressed and lined up, with the middle copy spatially inverted; (fourth pane) illustrative eddy event sizes and locations with corresponding temperature profile for a single ODT realization of a wall fire, adapted from \cite{Monson_2016}.}
 	\label{fig:tripletmap}

### 2020-09-21 manuscript/manuscript.tex
abstract

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
-Write this last. About 100 words. 
+%
+One-Dimensional Turbulence (ODT) is an accurate and computationally efficient technique for modeling turbulent flows.
+ODT has been applied to a wide range of flow problems including reaction, multiphase, differential diffusion, heat release, buoyancy, and wall flows.
+Applications include use as a standalone model and as a closure for Large Eddy Simulation (LES).
+Its strength lies in the ability to capture a full range of turbulent length and time scales.
+ODT is somewhat complicated, with a strong coupling between the model formulation and its implementation.
+We present a modern, open-source, object-oriented C++ implementation of ODT.
+This code can be used as a starting point to understand, apply, and extend the model, greatly aiding its further use and application in turbulence research.
+%
 \end{abstract}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-09-21 manuscript/manuscript.tex
Impact section added.

@@
 
-Questions to answer in this section (from SoftwareX template)
-\begin{enumerate}
-	\item How can new research questions be pursued with this software?
-		\begin{itemize}
-			\item possibility of parametric studies (much harder with DNS/LES/RANS)
-			\item study of late-flame soot and radiation interactions, soot emissions as smoke
-			\item comparative radiation model studies?
-		\end{itemize}
-	\item How does the software improve pursuit of existing research questions?
-		\begin{itemize}
-			\item late-flame behavior becomes easier to study
-			\item validation of LES subgrid models
-			\item soot stuff, especially late in the flame (because soot moves slowly compared to gas species and therefore short simulation times like in DNS aren't enough to study it effectively)
-		\end{itemize}
-	\item How does the software change the daily practice of its users?
-		\begin{itemize}
-			\item cases take hours or days rather than weeks using supercomputer resources
-			\item test cases can be run on local computers (unlike something like DNS) and as background tasks without disrupting other tasks
-			\item ODT as a tool complements other approaches, can cover blind spots and be used in validation
-		\end{itemize}
-	\item How widespread is the software? Who uses it? (Within and outside of intended research area and/or group.)
-		\begin{itemize}
-			\item BYU group
-			\item JCH at Sandia
-			\item Chalmers group in Sweden (Marco Fistler, etc.)
-			\item German university group (Heiko Schmidt, Juan Media, Marten Klein, etc.)
-			\item TO DO: find other groups who have used or currently use ODT
-		\end{itemize}
-	\item How is the software used in commercial settings (if any)? Has it led to creation of spin-off companies?
-		\begin{itemize}
-			\item No commercial use (I think). 
-		\end{itemize}
-\end{enumerate}
+The ODT model formulation is somewhat complex and is difficult to cleanly separate from its implementation.
+For instance, while the triplet map can be represented mathmatically, it is usually implemented as we described previously.
+That description assumed an adaptive grid with variable cell sizes.
+Alternative formulations are used for fixed grids.
+Furthermore, the model itself is complex and difficult to implement.
+These challenges present barriers for practitioners who wish to use the model.
+The code presented aims to reduce these barriers by providing an open-source, well-documented code that can be used directly, or modified to suit particular research aims.
+New research questions that could be persued include soot-flame-radiation-chemsitry interactions, multi-phase reacting flows (such as diesel sprays) using Lagrangian particles, and coupled near-wall heat and momentum transfer, to name a few.
+The code presented has been demonstrated to be extensible to such systems.
+These extensions are facilitated by the object-oriented structure, including the domain variables.
+For example, the code has be extended to solve steady laminar flamelets \cite{Peters_1984}, requiring inheritance from the \textt{solver}, \texttt{micromixer}, and \texttt{dv} (domain variable) classes.
+
+The structure of the ODT code, using an adaptive mesh, and a Lagrangian formulation for diffusive advancement of transport equations has several advantages.
+These include simplicity of formulation, and computational efficiency.
+The adaptive mesh minimizes the number of computational cells required, and can be adapted on any variable of interested.
+(Older versions of the code even made use of multiple coupled computational grids for different scalars.) This is especially important for flows with complex and expensive chemistry, and flows with widely varying resolution demands (such as near-wall flows).
+The Lagrangian formulation, implies that cell faces move with fluid velocity (such as is present during, e.g., flame expansion).
+This treatment is inherently stable, removing the need for complex (and diffusive) hyberbolic conservation law treatements and their associated CFL constraints.
+The conservation equations, as in Eq.
+(\ref{eq:transport}), are similarly simplified.
+
+The code has been run on Linux, Mac, and Windows machines, including on parallel clusters of up to 512 processor cores.
+Several research groups have used the code and contributed to its development.
+These include groups at Sandia National Laboratories, Brandenburg University of Technology Cottbus-Senftenberg, Chalmers University, and Combustion Science and Engineering, Inc.
+The latter company is the only one known to use the code in a commercial setting, though use was on a combustion research project.
+
+%Questions to answer in this section (from SoftwareX template)
+%\begin{enumerate}
+%	\item How can new research questions be pursued with this software?
+%		\begin{itemize}
+%			\item possibility of parametric studies (much harder with DNS/LES/RANS)
+%			\item study of late-flame soot and radiation interactions, soot emissions as smoke
+%			\item comparative radiation model studies?
+%		\end{itemize}
+%	\item How does the software improve pursuit of existing research questions?
+%		\begin{itemize}
+%			\item late-flame behavior becomes easier to study
+%			\item validation of LES subgrid models
+%			\item soot stuff, especially late in the flame (because soot moves slowly compared to gas species and therefore short simulation times like in DNS aren't enough to study it effectively)
+%		\end{itemize}
+%	\item How does the software change the daily practice of its users?
+%		\begin{itemize}
+%			\item cases take hours or days rather than weeks using supercomputer resources
+%			\item test cases can be run on local computers (unlike something like DNS) and as background tasks without disrupting other tasks
+%			\item ODT as a tool complements other approaches, can cover blind spots and be used in validation
+%		\end{itemize}
+%	\item How widespread is the software? Who uses it? (Within and outside of intended research area and/or group.)
+%		\begin{itemize}
+%			\item BYU group
+%			\item JCH at Sandia
+%			\item Chalmers group in Sweden (Marco Fistler, etc.)
+%			\item German university group (Heiko Schmidt, Juan Media, Marten Klein, etc.)
+%			\item TO DO: find other groups who have used or currently use ODT
+%		\end{itemize}
+%	\item How is the software used in commercial settings (if any)? Has it led to creation of spin-off companies?
+%		\begin{itemize}
+%			\item No commercial use (I think). 
+%		\end{itemize}
+%\end{enumerate}
 
@@
 \label{sec:conclusion}
-
-Write this part next to last
-%Set out the conclusion of this original software publication.
 

### 2020-09-21 manuscript/manuscript.tex
adding missing reference and bug: textt --> texttt

@@
 These extensions are facilitated by the object-oriented structure, including the domain variables.
-For example, the code has be extended to solve steady laminar flamelets \cite{Peters_1984}, requiring inheritance from the \textt{solver}, \texttt{micromixer}, and \texttt{dv} (domain variable) classes.
+For example, the code has be extended to solve steady laminar flamelets \cite{Peters_1984}, requiring inheritance from the \texttt{solver}, \texttt{micromixer}, and \texttt{dv} (domain variable) classes.
 

### 2020-09-21 manuscript/manuscript.tex
conclusions section added, spell checked paper.

@@
 Turbulent flows characterize the vast majority of fluid flows in practical engineering applications, and simulations of turbulent flows provide researchers with valuable insights into complex systems, particularly reacting turbulent flows such as combustion processes.
-Turbulence is a complex phemonenon that affects the full range of a flow's length and time scales.
+Turbulence is a complex phenomenon that affects the full range of a flow's length and time scales.
 As a result, resolving the entire flow field by numerically solving the Navier-Stokes equations of fluid flow, as is done in direct numerical simulations (DNS), requires substantial computational resources.
@@
 
-Early applications of ODT focused on homogenous turbulence, wakes, and mixing layers \cite{Kerstein_1999,Kerstein_2000,Kerstein_2001}.
+Early applications of ODT focused on homogeneous turbulence, wakes, and mixing layers \cite{Kerstein_1999,Kerstein_2000,Kerstein_2001}.
 Later extension to variable-density flows and a spatial downstream coordinate system facilitated its growth and application to more complex flows, including combustion in jet flames \cite{Echekki_2001,Hewson_2001,Hewson_2002,Lignell_2012,Punati_2011,Abdelsamie_2017,Lignell_2017, Goshayeshi_2015}, counterflow flames \cite{Jozefik_2015}, wall fires \cite{Monson_2016}, and sooting flames \cite{Lignell_2015,Hewson_2006,Hewson_2009,Lignell_2015b,Ricks_2010}, as well as other particle flows \cite{Sun_2017,Schmidt_2009,Sun_2014,Fistler_2017}.
@@
 In an eddy region of size $l$, transported property profiles are modified (mapped) by making three copies, compressing each spatially by a factor of three, then lining these up with the middle copy spatially reversed.
-This map is continuous and conservers all quantities and statistical moments, increases scalar gradients and decreases length scales consistent with turbulent eddies in real flows.
+This map is continuous and conserves all quantities and statistical moments, increases scalar gradients and decreases length scales consistent with turbulent eddies in real flows.
 Subsequent eddies in the same region will result in a cascade of scales.
@@
     \caption{Schematic diagram of a triplet map.
-From left to right: (first pane) simulation of a single ``eddy", a two-dimensional Kelvin-Helmholz instability with a vertical white line-of-sight; (second pane) mixture fraction profile along the indicated line-of-sight before and after the eddy showing increased gradients and surface area; (third pane) a triplet map operates on a profile to produce a mapped profile with three copies, compressed and lined up, with the middle copy spatially inverted; (fourth pane) illustrative eddy event sizes and locations with corresponding temperature profile for a single ODT realization of a wall fire, adapted from \cite{Monson_2016}.}
+From left to right: (first pane) simulation of a single ``eddy", a two-dimensional Kelvin-Helmholtz instability with a vertical white line-of-sight; (second pane) mixture fraction profile along the indicated line-of-sight before and after the eddy showing increased gradients and surface area; (third pane) a triplet map operates on a profile to produce a mapped profile with three copies, compressed and lined up, with the middle copy spatially inverted; (fourth pane) illustrative eddy event sizes and locations with corresponding temperature profile for a single ODT realization of a wall fire, adapted from \cite{Monson_2016}.}
 	\label{fig:tripletmap}
@@
 The CMake configuration file specifies Cantera's location and must be changed to reflect the local installation location.
-For reacting flows, the chemical reation rates can be computed by Cantera (the default), or a from a user-specified function, specified at compile time.
+For reacting flows, the chemical reaction rates can be computed by Cantera (the default), or a from a user-specified function, specified at compile time.
 Once the configuration settings are updated, the user runs CMake to apply the changes.
@@
 ODT simulations can also be run in parallel using MPI.
-Two run scripts, \texttt{slrmJob.sh} and \texttt{slrmJob\textunderscore array.sh}, are configured using SLURM \cite{Yoo_2003}, a common workload manager used for massively parallel computing resources.
+Two run scripts, \texttt{slrmJob.sh} and \texttt{slrmJob\textunderscore array.sh}, are configured using Slurm \cite{Yoo_2003}, a common workload manager used for massively parallel computing resources.
 This allows many ODT realizations to run in parallel rather than in serial, reducing overall simulation time.
@@
 The ODT model formulation is somewhat complex and is difficult to cleanly separate from its implementation.
-For instance, while the triplet map can be represented mathmatically, it is usually implemented as we described previously.
+For instance, while the triplet map can be represented mathematically, it is usually implemented as we described previously.
 That description assumed an adaptive grid with variable cell sizes.
@@
 The code presented aims to reduce these barriers by providing an open-source, well-documented code that can be used directly, or modified to suit particular research aims.
-New research questions that could be persued include soot-flame-radiation-chemsitry interactions, multi-phase reacting flows (such as diesel sprays) using Lagrangian particles, and coupled near-wall heat and momentum transfer, to name a few.
+New research questions that could be pursued include soot-flame-radiation-chemistry interactions, multi-phase reacting flows (such as diesel sprays) using Lagrangian particles, and coupled near-wall heat and momentum transfer, to name a few.
 The code presented has been demonstrated to be extensible to such systems.
@@
 The Lagrangian formulation, implies that cell faces move with fluid velocity (such as is present during, e.g., flame expansion).
-This treatment is inherently stable, removing the need for complex (and diffusive) hyberbolic conservation law treatements and their associated CFL constraints.
+This treatment is inherently stable, removing the need for complex (and diffusive) hyperbolic conservation law treatments and their associated CFL constraints.
 The conservation equations, as in Eq.
@@
 
+An implementation of the One-Dimensional Turbulence model has been presented.
+The code is open-source and uses is based on an object-oriented C++ framework.
+The code was motivated as an advanced model for turbulent reacting flow research.
+The build process (using CMake), was described, along with the directory structure, input file format, output data, and run and post-processing.
+A reacting jet example was given along with comparison to experimental data.
+Access to a proven, documented code, and a modern build procedure will aid researchers in applying and extending the model.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section*{Acknowledgements}
-\label{acknoledgements}
+\label{acknowledgements}
 
 This work was supported in part by the National Science Foundation under Grant No. CBET-1403403.
+%TODO, we probably need to add some acknowlegements here for those who contributed to the code.
 

### 2020-09-24 manuscript/manuscript.tex
Edits to paper. Fixes capitalization in references. Fixes to figure references.

@@
 %
-One-Dimensional Turbulence (ODT) is an accurate and computationally efficient technique for modeling turbulent flows.
+One-dimensional turbulence (ODT) is an accurate and computationally efficient technique for modeling turbulent flows.
 ODT has been applied to a wide range of flow problems including reaction, multiphase, differential diffusion, heat release, buoyancy, and wall flows.
-Applications include use as a standalone model and as a closure for Large Eddy Simulation (LES).
+Applications include use as a standalone model and as a closure for large-eddy simulation (LES).
 Its strength lies in the ability to capture a full range of turbulent length and time scales.
-ODT is somewhat complicated, with a strong coupling between the model formulation and its implementation.
+The ODT model is strongly coupled with its implementation, complicating its formulations.
 We present a modern, open-source, object-oriented C++ implementation of ODT.
-This code can be used as a starting point to understand, apply, and extend the model, greatly aiding its further use and application in turbulence research.
+This code can be used as a starting point to understand, apply, and extend the ODT model, enabling its further application to turbulent flow research.
 %
@@
 turbulence \sep reacting flows \sep one-dimensional turbulence
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
 
@@
 \hline
-C6 & Software code languages, tools, and services used & C++, Python 3.x, Yaml,  \\
+C6 & Software code languages, tools, and services used & C++, Python 3.x, YAML,  \\
 \hline
@@
 \hline
-C8 & If available Link to developer documentation/manual & \href{https://byuignite.github.io/ODT/doxygen/html/style_guide.html}{style guide} \\
+C8 & If available Link to developer documentation/manual & \href{https://byuignite.github.io/ODT/doxygen/html/style_guide.html}{ODT style guide} \\
 \hline
@@
 
-%The permanent link to code/repository or the zip archive should include the following requirements: 
-%\begin{itemize}
-%	\item README.txt and LICENSE.txt.
-%	\item Source code in a src/ directory, not the root of the repository.
-%	\item TO DO: Tag corresponding with the version of the software that is reviewed.
-%	\item TO DO: Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
-%\end{itemize}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 DNS is a powerful research tool, but its high computational cost makes it intractable for simulating most practical engineering flows.
-In order to achieve numerical solutions to practical flow problems, researchers can use alternative frameworks that model turbulence rather than resolving it directly.
+In order to achieve numerical solutions to practical flow problems, researchers use alternative frameworks that model turbulence rather than resolving it directly.
 
 Large-eddy simulations (LES) address the problem of wide-ranging length and time scales by combining  direct resolution of grid-scale quantities, as in DNS, with subgrid modeling of smaller turbulence structures.
-The more complex the flow, the more modeling is required; for example, a jet flame simulation might require subgrid modeling for the combustion chemistry, radiative heat transfer, or soot chemistry in addition to turbulence structures, all of which form a tightly coupled system in which each model interacts heavily with the others.
+The more complex the flow, the more modeling is required; for example, a jet flame simulation might require subgrid modeling for the combustion chemistry, radiative heat transfer, and soot chemistry in addition to turbulence structures, all of which form a tightly coupled system in which each model interacts heavily with the others.
 While subgrid modeling makes LES more computationally affordable than DNS, it can introduce empiricism into simulations, which can lead to inaccurate results.
@@
 The one-dimensional turbulence model (ODT) functionally reverses the LES approach, modeling large-scale turbulent advection and directly resolving small-scale flow structures, simulating the full range of length and time scales in a single dimension.
-Depending on the configuration, large-scale structures can be easier to model than small-scale structures (especially when reaction is present.
-ODT's direct resolution (in one dimension) of fine scales removes subgrid modeling issues that complicate LES.
+Depending on the configuration, large-scale structures can be easier to model than small-scale structures, especially in reacting flows.
+ODT's direct resolution of fine scales in one dimension bypasses subgrid modeling issues that complicate LES.
 Previous studies show that ODT can attain accuracy comparable to DNS at a fraction of the computational cost \cite{Lignell_2015,Abboud_2015}, making it an attractive tool for simulating turbulent flows.
-Because the ODT model is one-dimensional, it is limited to homogeneous or boundary-layer flows, such as jets, wakes, and mixing layers; these types of flows, however, are common in nature and central to turbulence research.
+Because the ODT model is one-dimensional, it is limited to homogeneous or boundary-layer flows, such as jets, wakes, and mixing layers, but these types of flows are common in nature and central to turbulence research.
 ODT's computational efficiency and resolution of a full range of scales make it a valuable tool that complements experimental studies and other simulation tools like DNS and LES.
@@
 The ODT code presented here is a pared down version of the development code, representing the fundamental aspects of the ODT model and its most reliable functions.
-The example cases in Section~\ref{sec:examples} are a representative sample of the ODT code's capabilities as it is presented here.
+The example case in Section~\ref{sec:examples} is a representative sample of the ODT code's capabilities as it is presented here.
 Future releases will expand this code's functionality with additional features currently in development.
-
-%Questions to answer in this section (from SoftwareX template)
-%\begin{enumerate}
-%	\item What's the scientific background and motivation for this software?
-%	\item Why is this important? What problems does it solve?
-%	\item How has the software contributed (and/or how will it contribute in the future) to the process of scientific discovery? Cite papers using the software.
-%	\item In what experimental setting might someone use this software?
-%	\item What related work is there in the literature?
-%	\item What algorithms, other code/software, or ideas are used? Cite them. 
-%\end{enumerate}
 
@@
 The system of ordinary differential equations (ODEs) that results is well behaved at all grid points and in all geometries in their finite-volume forms.
-For details on transport equation derivation and use in both the temporal and spatial formulations of ODT, see Lignell et al.~\cite{Lignell_2018}.
+For details on transport equation derivation and use in both the temporal and spatial formulations of ODT, see~\cite{Lignell_2018}.
 
@@
 Eddy events modify domain variables using ``triplet maps", as illustrated in Figure~\ref{fig:tripletmap}.
-In an eddy region of size $l$, transported property profiles are modified (mapped) by making three copies, compressing each spatially by a factor of three, then lining these up with the middle copy spatially reversed.
-This map is continuous and conserves all quantities and statistical moments, increases scalar gradients and decreases length scales consistent with turbulent eddies in real flows.
+In an eddy region of size $l$, transported property profiles are modified (mapped) by making three copies, compressing each spatially by a factor of three, and realigning them with the middle copy spatially reversed.
+This map is continuous, conserves all quantities and statistical moments, increases scalar gradients, and decreases length scales consistent with turbulent eddies in real flows.
 Subsequent eddies in the same region will result in a cascade of scales.
-The eddy rates, used in the sampling and selection of eddies depend on eddy size and the local kinetic energy consistent with turbulent scaling laws.
+The eddy rates, used to sample and select eddy events, depend on eddy size and the local kinetic energy consistent with turbulent scaling laws.
 
 \begin{figure}
-	\centering
+		\begin{tabular}{llll}
+			\hspace{40pt}(a) & \hspace{100pt} (b) & \hspace{70pt} (c) & \hspace{50pt}(d) 
+		\end{tabular}
+	\begin{center}
+		\begin{tabular}{c}
 			\includegraphics[width=\textwidth]{../figures/tripletmap/tripmap.pdf} 
+		\end{tabular}
+	\end{center}
     \caption{Schematic diagram of a triplet map.
-From left to right: (first pane) simulation of a single ``eddy", a two-dimensional Kelvin-Helmholtz instability with a vertical white line-of-sight; (second pane) mixture fraction profile along the indicated line-of-sight before and after the eddy showing increased gradients and surface area; (third pane) a triplet map operates on a profile to produce a mapped profile with three copies, compressed and lined up, with the middle copy spatially inverted; (fourth pane) illustrative eddy event sizes and locations with corresponding temperature profile for a single ODT realization of a wall fire, adapted from \cite{Monson_2016}.}
+From left to right: (a) simulation of a single ``eddy", a two-dimensional Kelvin-Helmholtz instability with a vertical white line-of-sight; (b) mixture fraction profile along the indicated line-of-sight before and after the eddy showing increased gradients and surface area; (c) a triplet map operates on a profile to produce a mapped profile with three copies, compressed and lined up, with the middle copy spatially inverted; (d) illustrative eddy event sizes and locations with corresponding temperature profile for a single ODT realization of a wall fire, adapted from \cite{Monson_2016}.}
 \label{fig:tripletmap}
@@
 Eddy events occur concurrently with diffusive advancement via solution of the system of unsteady one-dimensional transport equations.
-In this way, the ODT code marches in time (or space) until it reaches its end point.
+In this way, the ODT code marches in time or space until it reaches the simulation end point.
 Due to the stochastic nature of eddy events, each ODT simulation, or realization, is different, even when it is provided with the same input parameters.
-In order to obtain statistically stable data for a given set of parameters, we run many realizations with the same input parameters, and then gather statistics over these realizations.
+In order to obtain statistically stable data for a given set of parameters, we run many realizations with the same input parameters and then gather statistics over these realizations.
 This is done via post-processing tools, which are provided in the ODT package.
@@
 \begin{figure}
-	\centering
+	\begin{center}
 		\includegraphics[width=\textwidth]{../figures/odt_flow_chart.pdf}
+	\end{center}
 	\caption{Structural outline of the ODT code, including its major class objects.
@@
 The \texttt{micromixer} handles diffusive advancement by setting step sizes, interacting with the transported domain variables, and solving the system of ODEs defined by Equation~\ref{eq:transport} (or its equivalent in the spatial formulation).
-The \texttt{micromixer} includes three solution methods that can be specified in \texttt{input.yaml}: a first-order explicit Euler method (pictured in Figure~\ref{fig:flowchart}); a first-order semi-implicit method; and a second order Strang splitting method~\cite{Strang_1968}.
+The \texttt{micromixer} includes three solution methods that can be specified in \texttt{input.yaml}: a first-order explicit Euler method (pictured in Figure~\ref{fig:flowchart}), a first-order semi-implicit method, and a second order Strang splitting method~\cite{Strang_1968}.
 The latter two methods are useful for treating stiff chemistry, with source terms integrated using CVODE~\cite{Hindmarsh_2020}.
-In reacting flow cases, enthalpy and chemisal species are transported, with physical properties and kinetic rates computed with Cantera~\cite{Goodwin_2018}.
+In reacting flow cases, enthalpy and chemical species mass fractions are transported, and physical properties and kinetic rates are computed with Cantera~\cite{Goodwin_2018}.
 The \texttt{micromixer} is also the code's primary point of interaction with the \texttt{mesher} object (not pictured in Figure~\ref{fig:flowchart}), which manages the adaptive grid functions.
 Finally, the \texttt{eddy} object manages eddy event selection and implementation, which proceeds as described in Section~\ref{sub:model_description}.
-
-%Things to put in this section (from SoftwareX template)
-%\begin{itemize}
-%	\item overview of overall software architecture
-%	\item optional: pictorial overview
-%	\item implementation details
-%\end{itemize}
 
@@
 This section outlines the process a user goes through in order to successfully build the ODT code and run a simulation.
+ODT is a standalone, self-contained package, and users interact with its files primarily via the command line rather than a graphical interface.
 For more details, please see the package documentation.
-ODT is a standalone, self-contained package, and users interact with its files primarily via the command line rather than a graphical interface.
 
@@
 The \texttt{source}, \texttt{build}, and \texttt{run} directories contain the ODT source code, compilation tools, and run scripts, respectively.
-The \texttt{input} directory contains subdirectories corresponding to several possible case types, each populated with an appropriate input files.
+The \texttt{input} directory contains subdirectories corresponding to several possible case types, each populated with the appropriate input files.
 The \texttt{data} directory, initially empty, holds the raw data files and runtime information generated by ODT, as well as post-processed data files generated from within the \texttt{post} directory.
-Finally, the \texttt{doc} directory contains documentation optionally generated by Doxygen \cite{vanHeesch_2018} during the build process.
+Finally, the \texttt{docs} directory contains documentation optionally generated by Doxygen \cite{vanHeesch_2018} during the build process.
 
@@
 The CMake configuration file specifies Cantera's location and must be changed to reflect the local installation location.
-For reacting flows, the chemical reaction rates can be computed by Cantera (the default), or a from a user-specified function, specified at compile time.
+For reacting flows, the chemical reaction rates can be computed by Cantera (default), or a from a user-specified function, specified at compile time.
 Once the configuration settings are updated, the user runs CMake to apply the changes.
@@
 At minimum, a case's subdirectory must contain an \texttt{input.yaml} file, but may contain other files, or subfolders with supplementary information.
-%ODT has the capability to restart a simulation from a specified time or state.
-To use this function, a raw data file at the required state must be copied to the input case directory and renamed \texttt{restart.dat}.
-For an example, please see the \texttt{jetFlame/flameD} case.
-Note that the user must also change the \texttt{Lrestart} parameter within the \texttt{input.yaml} file in order to use the restart feature.
 
@@
 Input files contain simulation parameters in a human-readable format parsed by YAML.
+Within \texttt{input.yaml}, parameters are organized into sections, several of which are common to all input files.
+Parameter values present in the provided input files may be considered defaults that can be used to run a successful simulation of that case type.
+General code parameters are stored in the \texttt{params} class.
+Variables needed in a simulation but not provided in an input file (not recommended), are either given defaults specified in the \texttt{params} class or result in an error message.
 Details about individual parameters, including usage and typical values, are covered in the documentation.
-Within \texttt{input.yaml}, parameters are organized into sections, several of which are common to all input files.
-Parameter values present in the provided input files may be considered defaults that may be used to run a successful simulation of that case type.
-General code parameters are stored in the \texttt{params} class.
-Variables needed in a simulation but not provided in an input file (not recommended), are either given defaults specified in the \texttt{params} class, or result in an error message.
-
-%An overview of possible ODT parameters will be covered here, but does not represent all the possibilities or functions of ODT; please see the associated documentation for more information.
-Input files are divided into sections, several of which are common to all \texttt{input.yaml} files; these are summarized in Table \ref{tab:input_sections}.
-
-%\begin{table}
-%\begin{tabular}{|l|p{4.1in}|}
-%\hline
-%Section 				& Description 	\\
-%\hline
-%\texttt{params}* 		& General parameters, including simulation length, domain size, and ODT parameters ($C$, $Z$, $\beta_{LES}$) \\
-%\texttt{radParams}		& Radiation parameters; only relevant to reacting flow cases (i.e. jet flames) \\
-%\texttt{streamProps}	& Stream properties; used when there are two or more separate streams (i.e. non-premixed jets)\\
-%\texttt{bcCond}* 		& Boundary conditions for velocity and temperature (where required) \\
-%\texttt{initParams} 	& Case-specific initialization parameters, usually flow geometry and stream velocities \\
-%\texttt{dumpTimes}*		& List of simulation time steps at which to output data files \\
-%\hline
-%\end{tabular}
-%\caption{Common sections present in \texttt{input.yaml} files.
-Sections marked with a * should be present in every \texttt{input.yaml} file regardless of case type.
-Sections usually appear in this order, but this is not required.}
-%\label{tab:input_sections}
-%\end{table}
 
@@
 The \texttt{runManyRlz.sh} script runs many realizations in serial, one after the other; it differs from \texttt{runOneRlz.sh} only in that the user must also alter the \texttt{nRlz} variable, which specifies the number of realizations to run.
-Realizations differ by having different random seeds (specified in the input file).
-The random seed can either be randomized, or directly specified.
+Each realization has a different seed value, which can be randomized or directly specified in the input file.
 To run the simulation with either \texttt{runOneRlz.sh} or \texttt{runManyRlz.sh}, save the run script and execute it at the command line.
@@
 This allows many ODT realizations to run in parallel rather than in serial, reducing overall simulation time.
-Individual realizations are independent (\emph{embarrassingly parallel}), but users must take care with case names and input file changes to ensure that individual realizations or entire cases are not overridden accidentally.
+Individual realizations are independent (embarrassingly parallel), but users must take care with case names and input file changes to ensure that individual realizations or entire cases are not overridden accidentally.
 
@@
 Each case folder is subdivided into \texttt{input}, \texttt{runtime}, \texttt{data}, and \texttt{post}.
-The \texttt{input} folder contains a copy of the input files used for the simulation; \texttt{runtime} contains runtime output information, such as eddy event information ; \texttt{data} contains the raw data files; and \texttt{post} contains post-processed data files once they are generated.
+The \texttt{input} folder contains a copy of the input files used for the simulation; \texttt{runtime} contains runtime output, including eddy event information; \texttt{data} contains the raw data files; and \texttt{post} contains post-processed data files once they are generated.
 
@@
 
-To use post-processing tools, navigate to the \texttt{post} directory.
+To use post-processing tools, users navigate to the \texttt{post} directory.
 Within the \texttt{post} directory, data processing tools are organized by case type, which is specified in \texttt{input.yaml} and determines case-specific variables and simulation setup parameters (refer to the \texttt{domaincase} object in Figure \ref{fig:flowchart}).
@@
 Post-processed data and generated plots are deposited in the \texttt{data} directory, within the appropriate \texttt{caseName/post} folder.
-%For more information on using the provided post-processing tools, please refer to the documentation.
 
@@
 
-%%-----------------------------------------------------------------------------------
-%\subsection{Pipe Flow}
-%\label{sub:pipeflow}
-%
-%% TEXT COPIED/MODIFIED FROM CYLINDRICAL ODT PAPER
-%First, we present an incompressible pipe flow simulation using the temporal, cylindrical ODT formulation.
-Results for three different friction Reynolds numbers ($Re_\tau$ = 550, 1000, 2000) are compared to DNS results from El Khoury et al.
-\cite{ElKhoury_2013} ($Re_\tau$ = 550, 1000) and Chin et al.
-\cite{Chin_2014} ($Re_\tau$ = 2000) for a pipe diameter of $D=2.0$ m and flow density of 1.0 kg$\cdot$m$^{-3}$.
-Friction velocity values of 1 m$\cdot$s$^{-1}$ ($Re_\tau = 550, 1000$) and 2 m$\cdot$s$^{-1}$ ($Re_\tau = 2000$) were assumed and used to calculate the mean pressure gradient driving the flow.
-Using initial conditions with uniform velocity profiles, simulations were run until a state of developed flow was achieved, at which point data were gathered until statistical convergence for the root mean square (RMS) velocity difference from the mean profiles occurred.
-%
-%The simulations were performed with ODT parameters $C = 5$ and $Z = 350$ for the temporal ODT formulation. 
-%%Additionally, a restriction was imposed on the eddy size range by selecting eddies only up to a maximum normalized size of Le,max/D = 1/3.
-This restriction limits the eddy size by construction, as opposed to the large-eddy suppression mechanism commonly used in ODT simulations [27,45].
-%The values of C and Z
-%%and Le,max/D 
-%were adjusted to give good agreement of the ODT results compared to the DNS.
-Schmidt et al.
-\cite{Schmidt_2003} showed that higher $Z$ results in the buffer-layer being located further from the wall, and increasing $C$ results in a lower slope of the mean streamwise velocity in the log-layer.
-%%and higher Le,max/D gives a smaller mean streamwise velocity in the wake region.
-%
-%RESULTS AND PLOTS GO HERE
-%
-%\subsection{Non-reacting Jet }
-%\label{sub:nonreactingjet}
-%
-%% TEXT COPIED/MODIFIED FROM CYLINDRICAL ODT PAPER
-%Here, we present ODT simulation results for a non-reacting round, turbulent jet compared to the experimental data of Hussein et al.
-\cite{Hussein_1994}.
-The jet consists of air issuing into air through a 1 in (0.0254 m) diameter duct with a uniform exit velocity of 56.2 m$\cdot$s$^{-1}$ and a reported Reynolds number of 95,500.
-The ODT simulations use this diameter and velocity with a kinematic viscosity of $1.534\cdot10^{-5}$ m$^2$s$^{-1}$, resulting in a Reynolds number of 93,056.
-The initial velocity profile in the ODT simulations is a modified top-hat profile in which a hyperbolic tangent function of width $\delta$ = 0.1D is used on either side of the jet to smooth the transition between the jet and the free stream.
-In the spatial formulation of ODT, the streamwise velocity must be positive everywhere on the line, so a small minimum velocity of $v_{min} = 0.1$m$\cdot$s$^{-1}$ is specified and added across the entire velocity profile.
-%
-%ODT simulations were performed with parameters $C = 5.25$, $\beta_{LES} = 3.5$, and $Z=400$.
-The value of $Z$ is the same as the spatial simulations in \cite{Monson_2016}, and the values of $C$ and $\beta_{LES}$ were adjusted to give good agreement with the experimental data.
-Note the close agreement of the $C$ and $Z$ parameters here to the optimal values used for the pipe flow simulations ($C = 5$ and $Z = 350$).
-This illustrates a level of robustness in the ODT parameters and suggests that intermediate values could be successfully applied in both configurations.
-%
-%1024 independent ODT realizations were performed and results were ensemble averaged.
-All quantities are normalized consistent with jet similarity scaling.
-Downstream locations are normalized by the jet diameter $D$, and radial locations are normalized by $(y-y_0)$, where $y$ is the downstream location and $y_0 = 4D$ is the virtual origin used in \cite{Hussein_1994}.
-%
-%RESULTS AND PLOTS GO HERE
-%
-%%In the figure, $v_0$ is the jet exit velocity and $v_{cL}$ is the local mean axial centerline velocity.
-Here, $r$ is used to denote both the experimental radial location and the ODT line position $x$.
-%
-%%It is worth noting that the vrms profile depends somewhat on the ODT parameters selected.
-Hewson and Kerstein [15] demonstrated that mean centerline values of mixture fraction were insensitive to C and βles provided their ratio was kept constant.
-In these simulations, however, higher values of RMS fluctuations were observed at lower values of βles.
-Figure 9 shows results for TMA similar to those in Fig.
-8 with varying C and βles.
-Each of the three cases has C/βles = 2, with C = 7, 5, and 3.
-Plots (b) and (c) show axial location
-%
-%%The centerline velocity decay and radial profiles show good agreement, as with the previous cases, with a slight improvement in the radial velocity profile.
-The vrms profiles are significantly improved along the centerline compared to TMA and TMB.
-The centerline anomaly is not completely removed, however, since implemented eddies are still subject to the geometric distortion of the TMB map, whose influence is felt by the τ−1 calculation for subsequent eddy events.
-e
-
-%\subsection{Jet Flame}
-%\label{sub:jetflame}
-
-ODT is uniquely suited for reacting flow simulations.
+ODT is uniquely suited to reacting flow simulations.
 Here, we present illustrative ODT simulation results of a round, turbulent jet flame based on and compared to the experimental DLR-A flame of Meier et al.
@@
 This simulation uses the experimentally reported velocity profiles and jet dimensions.
-%In the non-reacting case, a small minimum velocity was added uniformly to the velocity profile; no such addition is required here because of the slow-moving coflow air stream that issues alongside the reacting jet.
-%The ODT simulation includes the buoyant source term but not the streamwise pressure gradient in Eq. (25). 
 The fuel was diluted with N$_2$ in the experimental flame to minimize radiative heat losses, and radiation is ignored in the simulation.
@@
 \end{align}
-These assumptions are reasonable for the DLR-A flame, especially with the purpose of illustrating ODT in a reacting jet configuration with variable properties and heat release.
+These assumptions are reasonable for illustrating ODT in the DLR-A reacting jet configuration with variable properties and heat release.
 More complex combustion reaction mechanisms are available within the source code and can be accessed by changing the appropriate input file parameters.
@@
 	\end{center}
+	\caption{DLR jet flame example case results: (a) mean axial velocity and RMS velocity along the centerline versus downstream location; (b) mean axial mixture fraction and RMS mixture fraction along the centerline versus downstream location; (c) mean axial temperature (K) and RMS temperature (K) along the centerline versus downstream location.}
 \label{fig:dlr_example_results}
-	\caption{DLR jet flame example case results: (a) mean axial velocity and RMS velocity along the centerline versus downstream location; (b) mean axial mixture fraction and RMS mixture fraction along the centerline versus downstream location; (c) mean axial temperature (K) and RMS temperature (K) along the centerline versus downstream location.}
 \end{figure}
@@
 
-%Present the major functionalities of the software. 
-%\begin{itemize}
-%	\item simulating turbulent flow cases, reacting or nonreacting flows
-%	\item can simulate laminar flow cases too
-%	\item does these things a whole lot faster than other methods do (LES, DNS especially)
-%	\item testing LES subgrid modeling assumptions
-%	\item simulating cases that DNS can't get to because needed simulation length is too long (i.e. late-flame phenomena)
-%\end{itemize}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:impact}
+The ODT model is complex, challenging to implement, and difficult to cleanly separate from its implementation, all of which presents barriers to practitioners who wish to use the model.
+For instance, triplet mapa can be represented mathematically but are usually implemented as previously described, assuming an adaptive grid with variable cell sizes.
+Alternative formulations are used for fixed grids.
+The code presented here reduces these barriers by providing an open-source, well-documented, modularly styled code that can be used directly or modified to suit particular research goals.
+Its structure facilitates addressing new research questions, such as soot-flame-radiation-chemistry interactions, multi-phase reacting flows using Lagrangian particle models (such as diesel sprays), and coupled near-wall heat and momentum transfer.
+The code presented here has been extended to and demonstrated in such systems already, facilitated by the object-oriented structure.
+For example, this code has been extended to solve steady laminar flamelets \cite{Peters_1984}, requiring inheritance from the \texttt{solver}, \texttt{micromixer}, and \texttt{dv} (domain variable) classes.
 
-The ODT model formulation is somewhat complex and is difficult to cleanly separate from its implementation.
-For instance, while the triplet map can be represented mathematically, it is usually implemented as we described previously.
-That description assumed an adaptive grid with variable cell sizes.
-Alternative formulations are used for fixed grids.
-Furthermore, the model itself is complex and difficult to implement.
-These challenges present barriers for practitioners who wish to use the model.
-The code presented aims to reduce these barriers by providing an open-source, well-documented code that can be used directly, or modified to suit particular research aims.
-New research questions that could be pursued include soot-flame-radiation-chemistry interactions, multi-phase reacting flows (such as diesel sprays) using Lagrangian particles, and coupled near-wall heat and momentum transfer, to name a few.
-The code presented has been demonstrated to be extensible to such systems.
-These extensions are facilitated by the object-oriented structure, including the domain variables.
-For example, the code has be extended to solve steady laminar flamelets \cite{Peters_1984}, requiring inheritance from the \texttt{solver}, \texttt{micromixer}, and \texttt{dv} (domain variable) classes.
+The structure of the ODT code, using an adaptive mesh and a Lagrangian formulation for diffusive advancement of transport equations, has several advantages, including simplicity of formulation and computational efficiency.
+The adaptive mesh minimizes the number of computational cells required and can be adapted to any variable of interest.
+This is especially important for flows with complex and expensive chemistry and flows with widely varying resolution demands such as near-wall flows.
+The Lagrangian formulation implies that cell faces move with fluid velocity (such as is present during flame expansion, for example).
+This treatment is inherently stable, removing the need for complex and diffusive hyperbolic conservation law treatments and their associated CFL constraints.
+The conservation equations, as in Equation \ref{eq:transport}, are similarly simplified.
 
-The structure of the ODT code, using an adaptive mesh, and a Lagrangian formulation for diffusive advancement of transport equations has several advantages.
-These include simplicity of formulation, and computational efficiency.
-The adaptive mesh minimizes the number of computational cells required, and can be adapted on any variable of interested.
-(Older versions of the code even made use of multiple coupled computational grids for different scalars.) This is especially important for flows with complex and expensive chemistry, and flows with widely varying resolution demands (such as near-wall flows).
-The Lagrangian formulation, implies that cell faces move with fluid velocity (such as is present during, e.g., flame expansion).
-This treatment is inherently stable, removing the need for complex (and diffusive) hyperbolic conservation law treatments and their associated CFL constraints.
-The conservation equations, as in Eq.
-(\ref{eq:transport}), are similarly simplified.
-
-The code has been run on Linux, Mac, and Windows machines, including on parallel clusters of up to 512 processor cores.
+The code has been run on Linux, Mac, and Windows machines, including parallel clusters of up to 512 processor cores.
 Several research groups have used the code and contributed to its development.
 These include groups at Sandia National Laboratories, Brandenburg University of Technology Cottbus-Senftenberg, Chalmers University, and Combustion Science and Engineering, Inc.
-The latter company is the only one known to use the code in a commercial setting, though use was on a combustion research project.
+The latter company is the only organization known to use the code in a commercial setting, though on a combustion research project.
 
@@
 
-An implementation of the One-Dimensional Turbulence model has been presented.
-The code is open-source and uses is based on an object-oriented C++ framework.
-The code was motivated as an advanced model for turbulent reacting flow research.
-The build process (using CMake), was described, along with the directory structure, input file format, output data, and run and post-processing.
-A reacting jet example was given along with comparison to experimental data.
-Access to a proven, documented code, and a modern build procedure will aid researchers in applying and extending the model.
+A clean and extensible implementation of the one-dimensional turbulence (ODT) model has been presented in an open-source, object-oriented C++ framework, motivated by advanced turbulent reacting flow research.
+The build process, directory structure, input file format, run process, and post-processing procedure were described in detail, including a representative reacting jet example case.
+Access to a proven, documented code and a modern build procedure will aid researchers in applying and extending the model to new research questions.
 

### 2020-10-02 manuscript/manuscript.tex
Web links, mechanisms.

@@
 \hline
-C8 & If available Link to developer documentation/manual & \href{https://byuignite.github.io/ODT/doxygen/html/style_guide.html}{ODT style guide} \\
+C8 & If available Link to developer documentation/manual & \href{https://github.com/BYUignite/ODT}{ODT style guide} \\
 \hline
@@
 These assumptions are reasonable for illustrating ODT in the DLR-A reacting jet configuration with variable properties and heat release.
-More complex combustion reaction mechanisms are available within the source code and can be accessed by changing the appropriate input file parameters.
 
@@
 \hline
-S6 & If available, link to user manual - if formally published include a reference to the publication in the reference list & \href{https://byuignite.github.io/ODT/doxygen/html/index.html}{https://byuignite.github.io/ODT/doxygen/html/index.html}\\
+S6 & If available, link to user manual - if formally published include a reference to the publication in the reference list & \href{https://github.com/BYUignite/ODT}{https://github.com/BYUignite/ODT}\\
 \hline

### 2020-10-02 submissions/initial_submission/manuscript.tex
initial submission

--- 2020-10-02 manuscript/manuscript.tex
@@
 		\begin{tabular}{c}
-			\includegraphics[width=\textwidth]{../figures/tripletmap/tripmap.pdf} 
+            \includegraphics[width=\textwidth]{fig_tripmap.pdf} 
 		\end{tabular}
@@
 	\begin{center}
-		\includegraphics[width=\textwidth]{../figures/odt_flow_chart.pdf}
+        \includegraphics[width=\textwidth]{fig_odt_flow_chart.pdf}
 	\end{center}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figures/data_folder_structure.pdf} 
+    \includegraphics[width=\textwidth]{fig_data_folder_structure.pdf} 
 	\caption{Data folder structure and file locations.
@@
 			(a) & (b) & (c) \\
-			\includegraphics[width=1.7in]{../figures/cl_uvel_DLR_test_11.pdf} &
-			\includegraphics[width=1.7in]{../figures/cl_mixf_DLR_test_11.pdf} &
-			\includegraphics[width=1.7in]{../figures/cl_temp_DLR_test_11.pdf}
+            \includegraphics[width=1.7in]{fig_cl_uvel_DLR_test_11.pdf} &
+            \includegraphics[width=1.7in]{fig_cl_mixf_DLR_test_11.pdf} &
+            \includegraphics[width=1.7in]{fig_cl_temp_DLR_test_11.pdf}
 		\end{tabular}
@@
 
-\bibliographystyle{elsarticle-num} 
-\bibliography{references}
+\begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\expandafter\ifx\csname href\endcsname\relax
+  \def\href#1#2{#2} \def\path#1{#1}\fi
+
+\bibitem{Lignell_2015}
+D.~O. Lignell, G.~C. Fredline, A.~D. Lewis, Comparison of one-dimensional
+  turbulence and direct numerical simulations of soot formation and transport
+  in a nonpremixed ethylene jet flame 35~(2) (2015) 1199--1206.
+\newblock \href {http://dx.doi.org/10.1016/j.proci.2014.05.046}
+  {\path{doi:10.1016/j.proci.2014.05.046}}.
+
+\bibitem{Abboud_2015}
+A.~W. Abboud, C.~Schulz, T.~Saad, S.~T. Smith, D.~D. Harris, D.~O. Lignell, A
+  numerical comparison of precipitating turbulent flows between large-eddy
+  simulation and one-dimensional turbulence 61~(10) (2015) 3185--3197.
+\newblock \href {http://dx.doi.org/10.1002/aic.14870}
+  {\path{doi:10.1002/aic.14870}}.
+
+\bibitem{Kerstein_1999}
+A.~R. Kerstein, One-dimensional turbulence: model formulation and application
+  to homogeneous turbulence, shear flows, and buoyant stratified flows 392
+  (1999) 277--334.
+\newblock \href {http://dx.doi.org/10.1017/S0022112099005376}
+  {\path{doi:10.1017/S0022112099005376}}.
+
+\bibitem{Kerstein_2000}
+A.~R. Kerstein, T.~D. Dreeben, Prediction of turbulent free shear flow
+  statistics using a simple stochastic model 12~(2) (2000) 418--424.
+\newblock \href {http://dx.doi.org/10.1063/1.870319}
+  {\path{doi:10.1063/1.870319}}.
+
+\bibitem{Kerstein_2001}
+A.~R. Kerstein, W.~T. Ashurst, S.~Wunsch, V.~Nilsen, One-dimensional
+  turbulence: vector formulation and application to free shear flows 447 (2001)
+  85--109.
+\newblock \href {http://dx.doi.org/10.1017/S0022112001005778}
+  {\path{doi:10.1017/S0022112001005778}}.
+
+\bibitem{Echekki_2001}
+T.~Echekki, A.~R. Kerstein, T.~D. Dreeben, J.-Y. Chen, `one-dimensional
+  turbulence' simulation of turbulent jet diffusion flames: model formulation
+  and illustrative applications 125~(3) (2001) 1083--1105.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00228-0}
+  {\path{doi:10.1016/S0010-2180(01)00228-0}}.
+
+\bibitem{Hewson_2001}
+J.~C. Hewson, A.~R. Kerstein, Stochastic simulation of transport and chemical
+  kinetics in turbulent
+  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2 }flames 5~(4)
+  (2001) 669--697.
+\newblock \href {http://dx.doi.org/10.1088/1364-7830/5/4/309}
+  {\path{doi:10.1088/1364-7830/5/4/309}}.
+
+\bibitem{Hewson_2002}
+J.~C. Hewson, A.~R. Kerstein, Local extinction and reignition in nonpremixed
+  turbulent {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2} jet
+  flames 174~(5-6) (2002) 35--66.
+\newblock \href {http://dx.doi.org/10.1080/713713031}
+  {\path{doi:10.1080/713713031}}.
+
+\bibitem{Lignell_2012}
+D.~O. Lignell, D.~S. Rappleye, One-dimensional-turbulence simulation of flame
+  extinction and reignition in planar ethylene jet flames 159~(9) (2012)
+  2930--2943.
+\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2012.03.018}
+  {\path{doi:10.1016/j.combustflame.2012.03.018}}.
+
+\bibitem{Punati_2011}
+N.~Punati, J.~C. Sutherland, A.~R. Kerstein, E.~R. Hawkes, J.~H. Chen, An
+  evaluation of the one-dimensional turbulence model: comparison with direct
+  numerical simulations of {CO}/{H}\textsubscript{2 }jets with extinction and
+  reignition 33~(1) (2011) 1515--1522.
+\newblock \href {http://dx.doi.org/10.1016/j.proci.2010.06.127}
+  {\path{doi:10.1016/j.proci.2010.06.127}}.
+
+\bibitem{Abdelsamie_2017}
+A.~Abdelsamie, D.~O. Lignell, D.~Th{\'e}venin, Comparison between {ODT} and
+  {DNS} for ignition occurrence in turbulent premixed jet combustion:
+  safety-relevant applications 231~(10) (2017) 1709--1735.
+\newblock \href {http://dx.doi.org/10.1515/zpch-2016-0902}
+  {\path{doi:10.1515/zpch-2016-0902}}.
+
+\bibitem{Lignell_2017}
+D.~O. Lignell, V.~B. Lansinger, A.~R. Kerstein, A cylindrical formulation of
+  the one-dimensional turbulence ({ODT}) model for turbulent jet flames, in:
+  AIChE Annual Meeting 2017, {American Institute of Chemical Engineers}, 2017.
+
+\bibitem{Goshayeshi_2015}
+B.~Goshayeshi, J.~C. Sutherland, Prediction of oxy-coal flame stand-off using
+  high-fidelity thermochemical models and the one-dimensional turbulence model
+  35~(3) (2015) 2829--2837.
+\newblock \href {http://dx.doi.org/10.1016/j.proci.2014.07.003}
+  {\path{doi:10.1016/j.proci.2014.07.003}}.
+
+\bibitem{Jozefik_2015}
+Z.~Jozefik, A.~R. Kerstein, H.~Schmidt, S.~Lyra, H.~Kolla, J.~H. Chen,
+  One-dimensional turbulence modeling of a turbulent counterflow flame with
+  comparison to {DNS} 162~(8) (2015) 2999--3015.
+\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2015.05.010}
+  {\path{doi:10.1016/j.combustflame.2015.05.010}}.
+
+\bibitem{Monson_2016}
+E.~I. Monson, D.~O. Lignell, M.~A. Finney, C.~Werner, Z.~Jozefik, A.~R.
+  Kerstein, R.~S. Hintze, Simulation of ethylene wall fires using the
+  spatially-evolving one-dimensional turbulence model 52~(1) (2016) 167--196.
+\newblock \href {http://dx.doi.org/10.1007/s10694-014-0441-2}
+  {\path{doi:10.1007/s10694-014-0441-2}}.
+
+\bibitem{Hewson_2006}
+J.~C. Hewson, A.~J. Ricks, S.~R. Tieszen, A.~R. Kerstein, R.~O. Fox,
+  Conditional-moment closure with differential diffusion for soot evolution in
+  fire, in: Center for Turbulence Research, Proceedings of the Summer Program
+  2006, {Stanford University}, 2006.
+
+\bibitem{Hewson_2009}
+J.~C. Hewson, A.~J. Ricks, S.~R. Tieszen, A.~R. Kerstein, R.~O. Fox, On the
+  transport of soot relative to a flame: modeling differential diffusion for
+  soot evolution in fire, in: H.~Bockhorn, A.~D'Anna, A.~F. Sarofim, H.~Wang
+  (Eds.), Combustion Generated Fine Carbonaceous Particles, {KIT Scientific
+  Publishing}, 2009, pp. 571--588.
+
+\bibitem{Lignell_2015b}
+D.~O. Lignell, J.~C. Hewson, One-dimensional turbulence simulation: overview
+  and application to soot formation in nonpremixed flames, in: SIAM Conference
+  on Computational Science and Engineering, 2015.
+
+\bibitem{Ricks_2010}
+A.~J. Ricks, J.~C. Hewson, A.~R. Kerstein, J.~P. Gore, S.~R. Tieszen, W.~T.
+  Ashurst, A spatially developing one-dimensional turbulence ({ODT}) study of
+  soot and enthalpy evolution in meter-scale buoyant turbulent flames 182~(1)
+  (2010) 60--101.
+\newblock \href {http://dx.doi.org/10.1080/00102200903297003}
+  {\path{doi:10.1080/00102200903297003}}.
+
+\bibitem{Sun_2017}
+G.~Sun, J.~C. Hewson, D.~O. Lignell, Evaluation of stochastic particle
+  dispersion modeling in turbulent round jets 89 (2017) 108--122.
+\newblock \href {http://dx.doi.org/10.1016/j.ijmultiphaseflow.2016.10.005}
+  {\path{doi:10.1016/j.ijmultiphaseflow.2016.10.005}}.
+
+\bibitem{Schmidt_2009}
+J.~R. Schmidt, J.~O.~L. Wendt, A.~R. Kerstein, Non-equilibrium wall deposition
+  of inertial particles in turbulent flow 137~(2) (2009) 233--257.
+\newblock \href {http://dx.doi.org/10.1007/s10955-009-9844-8}
+  {\path{doi:10.1007/s10955-009-9844-8}}.
+
+\bibitem{Sun_2014}
+G.~Sun, D.~O. Lignell, J.~C. Hewson, C.~R. Gin, Particle dispersion in
+  homogeneous turbulence using the one-dimensional turbulence model 26~(10)
+  (2014) 103301.
+\newblock \href {http://dx.doi.org/10.1063/1.4896555}
+  {\path{doi:10.1063/1.4896555}}.
+
+\bibitem{Fistler_2017}
+M.~Fistler, D.~O. Lignell, A.~R. Kerstein, M.~Oevermann, Numerical studies of
+  turbulent particle-laden jets using spatial approach of one-dimensional
+  turbulence, in: ILASS-Europe 28th Conference on Liquid Atomization and Spray
+  Systems, 2017.
+
+\bibitem{Cao_2008}
+S.~Cao, T.~Echekki, A low-dimensional stochastic closure model for combustion
+  large-eddy simulation 9.
+\newblock \href {http://dx.doi.org/10.1080/14685240701790714}
+  {\path{doi:10.1080/14685240701790714}}.
+
+\bibitem{Schmidt_2003}
+R.~C. Schmidt, A.~R. Kerstein, S.~Wunsch, V.~Nilsen, Near-wall {LES} closure
+  based on one-dimensional turbulence modeling 186~(1) (2003) 317--355.
+\newblock \href {http://dx.doi.org/10.1016/S0021-9991(03)00071-8}
+  {\path{doi:10.1016/S0021-9991(03)00071-8}}.
+
+\bibitem{Schmidt_2010}
+R.~C. Schmidt, A.~R. Kerstein, R.~McDermott, {ODTLES}: A multi-scale model for
+  3{D} turbulent flow based on one-dimensional turbulence modeling 199~(13-16)
+  (2010) 865--880.
+\newblock \href {http://dx.doi.org/10.1016/j.cma.2008.05.028}
+  {\path{doi:10.1016/j.cma.2008.05.028}}.
+
+\bibitem{GonzalezJuez_2011}
+E.~Gonzalez-Juez, A.~R. Kerstein, D.~O. Lignell, Fluxes across double-diffusive
+  interfaces: a one-dimensional-turbulence study 677 (2011) 218--254.
+\newblock \href {http://dx.doi.org/10.1017/jfm.2011.78}
+  {\path{doi:10.1017/jfm.2011.78}}.
+
+\bibitem{GonzalezJuez_2013}
+E.~Gonzalez-Juez, A.~R. Kerstein, D.~O. Lignell, Reactive {R}ayleigh--{T}aylor
+  turbulent mixing: a one-dimensional-turbulence study 107~(5) (2013) 506--525.
+\newblock \href {http://dx.doi.org/10.1080/03091929.2012.736504}
+  {\path{doi:10.1080/03091929.2012.736504}}.
+
+\bibitem{Wunsch_2001}
+S.~Wunsch, A.~R. Kerstein, A model for layer formation in stably stratified
+  turbulence 13~(3) (2001) 702--712.
+\newblock \href {http://dx.doi.org/10.1063/1.1344182}
+  {\path{doi:10.1063/1.1344182}}.
+
+\bibitem{Lignell_2018}
+D.~O. Lignell, V.~B. Lansinger, J.~Medina, M.~Klein, A.~R. Kerstein,
+  H.~Schmidt, M.~Fistler, M.~Oevermann, One-dimensional turbulence modeling for
+  cylindrical and spherical flows: model formulation and application 32~(4)
+  (2018) 495--520.
+\newblock \href {http://dx.doi.org/10.1007/s00162-018-0465-1}
+  {\path{doi:10.1007/s00162-018-0465-1}}.
+
+\bibitem{Klein_2018}
+M.~Klein, D.~O. Lignell, H.~Schmidt, Map-based modeling of turbulent
+  convection: application of the one-dimensional turbulence model to planar and
+  spherical geometries, in: International Conference on Rayleigh-Benard
+  Turbulence, 2018.
+
+\bibitem{Klein_2019}
+M.~Klein, D.~O. Lignell, H.~Schmidt, Stochastic modeling of temperature and
+  velocity statistics in spherical-shell convection, in: EGU Conference on
+  Recent developments in Geophysical Fluid Dynamics, 2019.
+
+\bibitem{Ashurst_2005}
+W.~T. Ashurst, A.~R. Kerstein, One-dimensional turbulence: variable-density
+  formulation and application to mixing layers 17~(2).
+\newblock \href {http://dx.doi.org/10.1063/1.1847413}
+  {\path{doi:10.1063/1.1847413}}.
+
+\bibitem{Lignell_2013}
+D.~O. Lignell, A.~R. Kerstein, G.~Sun, E.~I. Monson, Mesh adaption for
+  efficient multiscale implementation of one-dimensional turbulence 27~(3-4)
+  (2013) 273--295.
+\newblock \href {http://dx.doi.org/10.1007/s00162-012-0267-9}
+  {\path{doi:10.1007/s00162-012-0267-9}}.
+
+\bibitem{Cengel_2010}
+Y.~A. {\c{C}}engel, J.~M. Cimbala, Fluid Mechanics, 2nd Edition, {\c{C}}engel
+  series in engineering thermal-fluid sciences, {McGraw-Hill Higher Education},
+  2010.
+
+\bibitem{Beder_2008}
+J.~Beder, \href{https://github.com/jbeder/yaml-cpp/}{yaml-cpp v0.6.3} (2008).
+\newline\urlprefix\url{https://github.com/jbeder/yaml-cpp/}
+
+\bibitem{Strang_1968}
+G.~Strang, On the construction and comparison of difference schemes 5~(3)
+  (1968) 506--517.
+\newblock \href {http://dx.doi.org/10.1137/0705041}
+  {\path{doi:10.1137/0705041}}.
+
+\bibitem{Hindmarsh_2020}
+A.~C. Hindmarsh, R.~Serban, D.~R. Reynolds,
+  \href{https://computing.llnl.gov/projects/sundials/cvode}{{CVODE}},
+  https://computing.llnl.gov/sites/default/files/public/cv{\_}guide.pdf (2020).
+\newline\urlprefix\url{https://computing.llnl.gov/projects/sundials/cvode}
+
+\bibitem{Goodwin_2018}
+D.~G. Goodwin, R.~L. Speth, H.~K. Moffat, B.~W. Weber,
+  \href{https://cantera.org/}{Cantera} (2018).
+\newblock \href {http://dx.doi.org/10.5281/zenodo.1174508}
+  {\path{doi:10.5281/zenodo.1174508}}.
+\newline\urlprefix\url{https://cantera.org/}
+
+\bibitem{vanHeesch_2018}
+D.~{van Heesch}, \href{https://www.doxygen.nl/}{Doxygen} (2018).
+\newline\urlprefix\url{https://www.doxygen.nl/}
+
+\bibitem{Yoo_2003}
+A.~B. Yoo, M.~A. Jette, M.~Grondona, Slurm: simple linux utility for resource
+  management, in: D.~G. Feitelson, L.~Rudolph, U.~Schwiegelshohn (Eds.), Job
+  Scheduling Strategies For Parallel Processing, Vol. 2862 of Lecture notes in
+  computer science, 0302-9743, Springer, 2003, pp. 44--60.
+\newblock \href {http://dx.doi.org/10.1007/10968987-3}
+  {\path{doi:10.1007/10968987-3}}.
+
+\bibitem{Meier_2000}
+W.~Meier, R.~S. Barlow, Y.-L. Chen, J.-Y. Chen,
+  \href{https://tnfworkshop.org/data-archives/simplejet/dlrflames/}{Raman/{R}ayleigh/{LIF}
+  measurements in a turbulent
+  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2 }jet diffusion
+  flame: experimental techniques and turbulence--chemistry interaction} 123~(3)
+  (2000) 326--343.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(00)00171-1}
+  {\path{doi:10.1016/S0010-2180(00)00171-1}}.
+\newline\urlprefix\url{https://tnfworkshop.org/data-archives/simplejet/dlrflames/}
+
+\bibitem{Pitsch_2000}
+H.~Pitsch, Unsteady flamelet modeling of differential diffusion in turbulent
+  jet diffusion flames 123~(3) (2000) 358--374.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(00)00135-8}
+  {\path{doi:10.1016/S0010-2180(00)00135-8}}.
+
+\bibitem{Lindstedt_2005}
+R.~P. Lindstedt, H.~Ozarovsky, Joint scalar transported {PDF} modeling of
+  nonpiloted turbulent diffusion flames 143~(4) (2005) 471--490.
+\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2005.08.030}
+  {\path{doi:10.1016/j.combustflame.2005.08.030}}.
+
+\bibitem{Wang_2011}
+H.~Wang, S.~B. Pope, Large eddy simulation/probability density function
+  modeling of a turbulent
+  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2} jet flame
+  33~(1) (2011) 1319--1330.
+\newblock \href {http://dx.doi.org/10.1016/j.proci.2010.08.004}
+  {\path{doi:10.1016/j.proci.2010.08.004}}.
+
+\bibitem{Fairweather_2004}
+M.~Fairweather, R.~M. Woolley, First-order conditional moment closure modeling
+  of turbulent, nonpremixed methane flames 138~(1-2) (2004) 3--19.
+\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2004.03.001}
+  {\path{doi:10.1016/j.combustflame.2004.03.001}}.
+
+\bibitem{Lee_2008}
+K.~W. Lee, D.~H. Choi, Prediction of {NO} in turbulent diffusion flames using
+  eulerian particle flamelet model 12~(5) (2008) 905--927.
+\newblock \href {http://dx.doi.org/10.1080/13647830802094351}
+  {\path{doi:10.1080/13647830802094351}}.
+
+\bibitem{Lee_2009}
+K.~W. Lee, D.~H. Choi, Analysis of {NO} formation in high temperature diluted
+  air combustion in a coaxial jet flame using an unsteady flamelet model
+  52~(5-6) (2009) 1412--1420.
+\newblock \href {http://dx.doi.org/10.1016/j.ijheatmasstransfer.2008.08.015}
+  {\path{doi:10.1016/j.ijheatmasstransfer.2008.08.015}}.
+
+\end{thebibliography}
 

### 2020-11-10 submissions/response_to_reviews_1.md
reviews and response: initial add of files

## Authors Response to Reviewers
* Original reviewer comments are listed. Author responses are shown in italic text.

**Review 1**

Review of: One-dimensional turbulence (ODT): computationally efficient
modeling and simulation of turbulent flows

This paper presents an easy to use software for the One-dimensional
Turbulence (ODT) model that helps to remove the barrier for researchers
wanting to learn about ODT. The code is easy to understand and change to
suit different requirements. The paper is well-written, the software is
carefully explained, and the example provided demonstrates the use of
the software. I recommend publication subject to some minor edits and
clarifications as noted below.

-   Building OPT:

    -   YAML: specify the name of the needed yaml package is: yaml-cpp

-   Input files: Consider adding a feature that helps to specify the
    dumpTimes. For example, add the capability to parse the following
    values (Start, End, Step ) from the input file rather than
    specifying all the times you want to save the data manually.

-   Running ODT:

    -   The running interface is not trivial and limits the user to a
        predefined data storage location.This may cause problems for
        some users.

    -   My recommendation is to put all these run scripts under a single
        python interface that will allow the user to select the number
        of realization, the number of processes ( when running in
        parallel ), the input file, \... .

        -   consider using python classes for the interface, it will
            make you code much cleaner

        -   check argparse module in python!

-   Data files and Post-processing:

    -   In the paper, you mentioned in line 118 that \<200b\>the package
        contains auxiliary data processing and visualization tools.
        However, later in section 2.3.4 Data files and post-processing
        you mentioned in line 237 that those tools are organized by case
        type meaning that these post-processing tools are specific for
        the input files provided as examples. This may cause confusion
        to the user.

    -   Also, you didn't mention the tools you provided that help the
        user load the data. (ODT/Post/tools)

        -   I recommend that you put these functions under a python
            class that takes as a value the path to the data you saved.
            This will give flexibility to the user to load any data
            stored on his local or remote machines.

        -   Describe those functions in the paper.

    -   Also, I would recommend that the post-processing data examples
        you provided be written in Jupyter notebooks for clarity.

-   Impact:

    -   In the impact section line 298 the reference is missing.

-   Lines 78 and 79: very cumbersome sentence. Suggest you use: the
    first term on the RHS of eq. 1 is\... while the second term is\...

**Review 2**

Reviewer \#2: The paper describes an open-source code for simulating
one-dimensional turbulence (ODT).

As highlighted from the Authors in the impact Section, implementing ODT
is not an easy task hindering the spreading and use of this useful
model. The present open-source tool will be a first step to increase the
popularity of the technique among the scientific community in multiphase
and reactive flows.

The code is easy to read, to eventually modify and to use. The
documentation and the provided examples are clear and exhaustive.

The Reviewer has a personal curiosity on the technique (outside the
scope of the Journal). ODT has been used in combination with Lagrangian
particle models. We know those ( heavy ) particles tend to stay away
from the vortical regions, but if we are in 1-D, what is vorticity?
Should we look to other \"equivalent\" observables?

Minor, a reference appears as \[? \] on page 12.

### 2020-11-10 submissions/response_to_reviews_1.md
updating response to reviewer comments and editing the paper accordingly

@@
 
+***We appreciate the reviewer's and their careful review of the paper.***
+
 -   Building OPT:
@@
     -   YAML: specify the name of the needed yaml package is: yaml-cpp
+    ***We made this clarification in section 2.3.1 as requested.***
 
@@
     -   In the impact section line 298 the reference is missing.
+    ***This has been corrected.***
 
@@
     first term on the RHS of eq. 1 is\... while the second term is\...
+    ***We have reworded this paragraph: rather than jumping into symbol definitions, we note the physical meanings of the two additive terms on the right-hand-side of the equation.
+We also note the generality of the diffusive mixing, and that transport is refered to as mixing, which has relevance to understanding the naming in the source code.
+We then define the variables used.***
 
@@
 
+***We thank the reviewer for their time in performing this review.***
+
 The Reviewer has a personal curiosity on the technique (outside the
@@
 
+***It is true that ODT cannot capture vortex structures, but many relevant aspects of turbulent flows, including turbulent particle dispersion are represented by ODT through the capture of a wide range of length and time scales.
+There are aspects of correlation of turbulence intensity with vortex structures that are relevant, for example.
+For more information, see the discussion on page 111 (section 6.4.2) of Guangyuan Sun's dissertation: https://search.proquest.com/pqdtglobal/docview/1762246838/D46E7CC1A3EA44FAPQ/7?accountid=4488***
+
 Minor, a reference appears as \[? \] on page 12.
+***This has been corrected.**

### 2020-11-10 submissions/revision_1/manuscript.tex
updating response to reviewer comments and editing the paper accordingly

--- 2020-10-02 submissions/initial_submission/manuscript.tex
@@
 \end{equation}
-Here, $j_{\beta}$ is the diffusion flux of scalar $\beta$ across the cell face area $A_x$ where the subscripts $e$ and $w$ refer to the ``east" and ``west" faces of a given grid cell, respectively.
-$S_{\beta}$ is the Lagrangian source term derived from the conservation law for $\beta$, $\rho$ represents mass density, and $V$ represents cell volume.
-In practice, we refer to the left hand term on the right side of Equation~\ref{eq:transport} as the ``mixing term" and the right hand term on the right side of Equation~\ref{eq:transport} as the ``source term".
+The first and second terms on the right-hand-side of this equation are the diffusive transport and source terms, respectively.
+Here, the term \emph{diffusive} is not specific to mass transfer, but may refer to the transport of, e.g., heat, mass, and momentum, depending on the identity of the scalar $\beta$.
+In practice, we refer to the transport term as the ``mixing term`.
+The symbols shown in Equation~\ref{eq:transport} are defined as follows: $j_{\beta}$ is the diffusion flux of scalar $\beta$ across the cell face area $A_x$, where the subscripts $e$ and $w$ refer to the ``east" and ``west" faces of a given grid cell, respectively; $S_{\beta}$ is the Lagrangian source term derived from the conservation law for $\beta$; $\rho$ represents mass density; and $V$ represents cell volume.
 The generic transport equation differs slightly in the spatial formulation of ODT, but its form is similar, so we omit it here for brevity.
@@
 
-YAML is required in order to process input files.
+The \texttt{yaml-cpp} package is required in order to process input files.
 If it has not yet been installed, it must be built and installed at this point.
@@
 
+\bibitem{Peters_1984}
+N.~Peters, Laminar diffusion flamelet models in non-premixed turbulent
+  combustion, Progress in Energy and Combustion Science 10 (1984) 319--339.
+\newblock \href {https://doi.org/10.1016/0360-1285(84)90114-X}
+  {\path{doi:10.1016/0360-1285(84)90114-X}}.
+
 \end{thebibliography}

### 2020-11-11 submissions/response_to_reviews_1.md
response updates: response document and manuscript. Corresponding changes made to the code and code documentation.

@@
     -   YAML: specify the name of the needed yaml package is: yaml-cpp
+
     ***We made this clarification in section 2.3.1 as requested.***
@@
     specifying all the times you want to save the data manually.
+
+    ***We have now included this feature as requested.
+The user can specify times either through the original dumpTimes key, or through a new dumpTimesGen key that includes start, stop, and step variables.
+If both are present in the input file dumpTimesGen takes precedence, unless a negative start time is specified.
+This is demonstrated in the newly modified input file for the channel flow case, with comments to note the behavior and usage.
+We have also edited the paper and code documentation appropriately.
 
@@
 
-    -   In the paper, you mentioned in line 118 that \<200b\>the package
+    -   In the paper, you mentioned in line 118 that the package
         contains auxiliary data processing and visualization tools.
@@
 
+        ***This is a good recommendation.
+We have included a Jupyter notebook for post-processing the channelFlow, pipeFlow, and laminar_mixing_layer cases, with the latter already present.
+These will process the data and show comparison plots with the results.
+The previous stats.py functions are retained for consistency with the demonstration video and the codeocean module.
+The README files are updated.
+We have not made a jupyter notebook for the coldJet or jetFlame cases since these are larger simulations that are meant to be run and post-processed on a parallel processor with a job submission script, and that is how we and previous users have interacted with the code.***
+
 -   Impact:
@@
     -   In the impact section line 298 the reference is missing.
+
     ***This has been corrected.***
@@
     first term on the RHS of eq. 1 is\... while the second term is\...
+
     ***We have reworded this paragraph: rather than jumping into symbol definitions, we note the physical meanings of the two additive terms on the right-hand-side of the equation.
@@
 Minor, a reference appears as \[? \] on page 12.
+
 ***This has been corrected.**

### 2020-11-11 submissions/revision_1/manuscript.tex
response updates: response document and manuscript. Corresponding changes made to the code and code documentation.

@@
 The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number.
-The number attached to \texttt{dmp} files indicates the output time step, or ``dump" time, of the data file.
-These correspond to the order of the time steps listed in \texttt{input.yaml}.}
+The number attached to \texttt{dmp} files indicates the index of the list of ``dump" times included in, or generated from the information in \texttt{input.yaml}.}
 \label{fig:data_folder_structure}
@@
 Within the \texttt{post} directory, data processing tools are organized by case type, which is specified in \texttt{input.yaml} and determines case-specific variables and simulation setup parameters (refer to the \texttt{domaincase} object in Figure \ref{fig:flowchart}).
-Each set of post-processing tools is different, but may contain some combination of Python scripts (often coordinated by a \texttt{driver.py} file), experimental data files for comparison and plot generation, or other supplementary files.
+Each set of post-processing tools is different, but may contain some combination of Jupyter notebooks, Python scripts (often coordinated by a \texttt{driver.py} file), experimental data files for comparison and plot generation, or other supplementary files.
 Post-processed data and generated plots are deposited in the \texttt{data} directory, within the appropriate \texttt{caseName/post} folder.

### 2020-11-12 submissions/response_to_reviews_1.md
revision submitted to journal, adding differences between original and revision.

@@
 This is demonstrated in the newly modified input file for the channel flow case, with comments to note the behavior and usage.
-We have also edited the paper and code documentation appropriately.
+We have also edited the paper and code documentation appropriately.***
 
@@
         python interface that will allow the user to select the number
-        of realization, the number of processes ( when running in
-        parallel ), the input file, \... .
+        of realization, the number of processes (when running in
+        parallel), the input file, \... .
 
@@
         -   check argparse module in python!
+
+    ***We have carefully considered the reviewer's suggestion.
+The running of the code falls into two broad categories: running smaller simulations on a desktop computer, and running larger parallel simulations on Linux clusters.
+The scripts that we have provided are well-documented, and we have also provided a video going through the process.
+In addition, many of our current users are used to the existing interface, and changing this might cause confusion.
+For single desktop jobs, the runOneRlz.sh script is easy to use, with two variables for the user to edit at the top.
+For parallel jobs, users will be familiar with scripts using job submission software (e.g., slurm), and examples are provided that can be edited.
+We will keep this option open.***
 
@@
 
+        ***The reference on line 118 is a short note that post-processing tools are provided.
+The description in section 2.3.4 is more detailed and provides a more complete description.
+We certainly want to avoid confusion.
+We have edited the comment on line 118 to note that the post-processing tools are specific to the case, and include a pointer to the later discussion.***
+
     -   Also, you didn't mention the tools you provided that help the
         user load the data. (ODT/Post/tools)
+
+        ***This is a good comment. We have added a paragraph to the end of section 2.3.4 that describes these tools.***
 
@@
 
+            ***This is a valid suggestion for implementation, and is very similar to the approach that we have chosen.
+Namely, the functions are in a python module and can be easily accessed by importing the module.
+Many of these functions take a single dictionary argument that provides the case name as well as relevant paths (e.g., to the data or post directories of the given case).
+This dictionary is build in the driver script based on the user-supplied case name.
+We have explaned this in the new paragraph in section 2.3.4 noted above.***
+
         -   Describe those functions in the paper.
+        <br>
+        ***Done, as requested.***
 
@@
 
-***This has been corrected.**
+***This has been corrected.***

### 2020-11-12 submissions/differences_initial_vs_revision_1/manuscript.tex
revision submitted to journal, adding differences between original and revision.

--- 2020-11-11 submissions/revision_1/manuscript.tex
@@
 \usepackage{hyperref}
+
+\usepackage{soul}
+\usepackage{color}
 
@@
 \end{equation}
-The first and second terms on the right-hand-side of this equation are the diffusive transport and source terms, respectively.
+\hl{The first and second terms on the right-hand-side of this equation are the diffusive transport and source terms, respectively.
 Here, the term \emph{diffusive} is not specific to mass transfer, but may refer to the transport of, e.g., heat, mass, and momentum, depending on the identity of the scalar $\beta$.
 In practice, we refer to the transport term as the ``mixing term`.
-The symbols shown in Equation~\ref{eq:transport} are defined as follows: $j_{\beta}$ is the diffusion flux of scalar $\beta$ across the cell face area $A_x$, where the subscripts $e$ and $w$ refer to the ``east" and ``west" faces of a given grid cell, respectively; $S_{\beta}$ is the Lagrangian source term derived from the conservation law for $\beta$; $\rho$ represents mass density; and $V$ represents cell volume.
-The generic transport equation differs slightly in the spatial formulation of ODT, but its form is similar, so we omit it here for brevity.
+The symbols shown in} Equation~\ref{eq:transport} \hl{are defined as follows: $j_{\beta}$ is the diffusion flux of scalar $\beta$ across the cell face area $A_x$, where the subscripts $e$ and $w$ refer to the ``east" and ``west" faces of a given grid cell, respectively; $S_{\beta}$ is the Lagrangian source term derived from the conservation law for $\beta$; $\rho$ represents mass density; and $V$ represents cell volume.} The generic transport equation differs slightly in the spatial formulation of ODT, but its form is similar, so we omit it here for brevity.
 The system of ordinary differential equations (ODEs) that results is well behaved at all grid points and in all geometries in their finite-volume forms.
@@
 In order to obtain statistically stable data for a given set of parameters, we run many realizations with the same input parameters and then gather statistics over these realizations.
-This is done via post-processing tools, which are provided in the ODT package.
+This is done via post-processing tools.
+\hl{Post-processing is specific to a given case and the needs of the user.
+Examples of post-processing files are included for different cases provided with the ODT code, as discussed further in Section}~\ref{sec:data_files_post_processing}.
 
@@
 
-The \texttt{yaml-cpp} package is required in order to process input files.
+\hl{The \texttt{yaml-cpp} package} is required in order to process input files.
 If it has not yet been installed, it must be built and installed at this point.
@@
 \subsubsection{Data files and post-processing}
+\label{sec:data_files_post_processing}
 
@@
 The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number.
-The number attached to \texttt{dmp} files indicates the index of the list of ``dump" times included in, or generated from the information in \texttt{input.yaml}.}
+The number attached to \texttt{dmp} files indicates the \hl{index of the list of ``dump" times included in, or generated from the information} in \texttt{input.yaml}.}
 \label{fig:data_folder_structure}
@@
 Within the \texttt{post} directory, data processing tools are organized by case type, which is specified in \texttt{input.yaml} and determines case-specific variables and simulation setup parameters (refer to the \texttt{domaincase} object in Figure \ref{fig:flowchart}).
-Each set of post-processing tools is different, but may contain some combination of Jupyter notebooks, Python scripts (often coordinated by a \texttt{driver.py} file), experimental data files for comparison and plot generation, or other supplementary files.
+Each set of post-processing tools is different, but may contain some combination of \hl{Jupyter notebooks,} Python scripts (often coordinated by a \texttt{driver.py} file), experimental data files for comparison and plot generation, or other supplementary files.
 Post-processed data and generated plots are deposited in the \texttt{data} directory, within the appropriate \texttt{caseName/post} folder.
+
+\hl{As part of the post-processing tools, there is a \texttt{post/tools} directory that contains two files: \texttt{data\_py.py} and \texttt{data\_tools.py}.
+The first of these can be used to convert the text data files generated during a run into binary numpy files.
+This can reduce both the number of data files and the file sizes.
+The number of files is reduced since all code realizations at a given output time are saved in the same binary file.
+The \texttt{data\_tools.py} file is a module that contains a number of functions for processing the data files, such as functions to}
+%
+\begin{itemize}
+    \item \hl{get the data from a given realization,}
+    \item \hl{return the number of realizations,}
+    \item \hl{get a list of the variable names in the data files,}
+    \item \hl{compute axial locations in the spatial ODT formulation,}
+    \item \hl{query a parameter from the input file,}
+    \item \hl{return the stoichiometric mixture fraction for combustion/mixing problems, and}
+    \item \hl{compute the domain bounds.}
+\end{itemize}
+%
+\hl{In addition, a few functions are provided for doing interpolation/extrapolation, and computing probability denisity functions (PDFs), and weighted PDFs.
+Many of these functions take an argument that is a dictionary of case-specific information, such as the case name and paths for key directories.
+This dictionary is set in the post-processing driver script based only on the user-specified case name.
+}
 
@@
 
-This work was supported in part by the National Science Foundation under Grant No. CBET-1403403.
-%TODO, we probably need to add some acknowlegements here for those who contributed to the code.
-
-%Special thanks to Alan R.
+Special thanks to Alan R.
 Kerstein for his significant contributions to model development.
-Additional thanks to Heiko Schmidt, Juan Medina, and Marten Klein of Brandenburg University of Technology Cottbus-Senftenberg, Michael Oevermann and Marco Fistler of Chalmers University of Technology, and Vladimir P.
-Solovjov of Brigham Young University.
+Additional thanks to Heiko Schmidt, Juan Medina, and Marten Klein of Brandenburg University of Technology Cottbus-Senftenberg, Michael Oevermann and Marco Fistler of Chalmers University of Technology, and John Hewson of Sandia National Laboratories for code contributions, and insightful conversations.
 

### 2020-11-30 submissions/differences_initial_vs_revision_2/manuscript.tex
revision 2

--- 2020-11-11 submissions/revision_1/manuscript.tex
@@
 
+%\usepackage{soul}
+%\usepackage{color}
+\usepackage{changes}
+\colorlet{Changes@Color}{yellow}
+
 \journal{SoftwareX}
@@
 %
-One-dimensional turbulence (ODT) is an accurate and computationally efficient technique for modeling turbulent flows.
+    One-dimensional turbulence (ODT) is an accurate and computationally efficient \deleted{technique} \added{model} for \deleted{modeling} \added{simulating} turbulent flows.
 ODT has been applied to a wide range of flow problems including reaction, multiphase, differential diffusion, heat release, buoyancy, and wall flows.
@@
 We present a modern, open-source, object-oriented C++ implementation of ODT.
-This code can be used as a starting point to understand, apply, and extend the ODT model, enabling its further application to turbulent flow research.
+\deleted{This code can be used as a starting point to understand, apply, and extend the ODT model, enabling its further application to turbulent flow research.} \added{The code described here and made available online can be used as a starting point to understand, apply, and extend the ODT model, enabling its further application to turbulent flow research.}
 %
@@
 ODT has also served to complement LES through subgrid modeling studies \cite{Cao_2008,Schmidt_2003,Schmidt_2010} and has been applied to various other flow configurations such as double-diffusive interfaces \cite{GonzalezJuez_2011}, Rayleigh-Taylor mixing \cite{GonzalezJuez_2013}, and stratified turbulence \cite{Wunsch_2001}.
-Most recently, the ODT code was extended to include cylindrical and spherical coordinate systems \cite{Lignell_2018,Klein_2018,Klein_2019}.
+Most recently, \deleted{the ODT code was} \added{ODT implementations have been} extended to include cylindrical and spherical coordinate systems \cite{Lignell_2018,Klein_2018,Klein_2019}.
 
-During the recent implementation of the cylindrical and spherical model formulations, the ODT code was drastically overhauled and reorganized, resulting in its current configuration.
-The ODT code presented here is a pared down version of the development code, representing the fundamental aspects of the ODT model and its most reliable functions.
+\deleted{During the recent implementation of the cylindrical and spherical model formulations, the ODT code was drastically overhauled and reorganized, resulting in its current configuration.
+} \added{Many of the references cited above make use of a particular software implementation of the ODT model, referred to here as the \emph{ODT code}.
+During the recent implementation of the cylindrical and spherical model formulations, this code was drastically overhauled and reorganized.} The ODT code presented here is a pared down version of the development code, representing the fundamental aspects of the ODT model and its most reliable functions.
 The example case in Section~\ref{sec:examples} is a representative sample of the ODT code's capabilities as it is presented here.
@@
 
-The ODT model is described in detail in the literature~\cite{Kerstein_1999,Kerstein_2001,Ashurst_2005,Lignell_2018,Lignell_2013}; only a brief explanation will be given here.
+The ODT model \added{formulation} is described in detail in the literature~\cite{Kerstein_1999,Kerstein_2001,Ashurst_2005,Lignell_2018,Lignell_2013}; only a brief explanation will be given here.
 In ODT, turbulent advection is modeled with stochastic processes called eddy events, which punctuate the solution of unsteady, one-dimensional transport equations for mass, momentum, and enthalpy.
-The ODT code uses a Lagrangian finite-volume formulation for diffusive advancement in which mass stays constant within each grid cell while cell volumes increase or decrease according to cell dilation via an adaptive mesh refinement~\cite{Lignell_2013}.
+The ODT code \added{implementation of the ODT model} uses a Lagrangian finite-volume formulation for diffusive advancement in which mass stays constant within each grid cell while cell volumes increase or decrease according to cell dilation via an adaptive mesh refinement~\cite{Lignell_2013}.
 
@@
 In order to obtain statistically stable data for a given set of parameters, we run many realizations with the same input parameters and then gather statistics over these realizations.
-This is done via post-processing tools, which are provided in the ODT package.
+This is done via post-processing tools.
+Post-processing is specific to a given case and the needs of the user.
+Examples of post-processing files are included for different cases provided with the ODT code, as discussed further in Section~\ref{sec:data_files_post_processing}.
 
@@
 
-The ODT package consists primarily of an object-oriented C++ code responsible for running flow simulation cases and generating data.
+The ODT code package consists primarily of an object-oriented C++ code responsible for running flow simulation cases and generating data.
 The package also contains auxiliary data processing and visualization tools, written mostly in Python.
@@
 This section outlines the process a user goes through in order to successfully build the ODT code and run a simulation.
-ODT is a standalone, self-contained package, and users interact with its files primarily via the command line rather than a graphical interface.
+The ODT \added{code} is a standalone, self-contained package, and users interact with its files primarily via the command line rather than a graphical interface.
 For more details, please see the package documentation.
@@
 The \texttt{input} directory contains subdirectories corresponding to several possible case types, each populated with the appropriate input files.
-The \texttt{data} directory, initially empty, holds the raw data files and runtime information generated by ODT, as well as post-processed data files generated from within the \texttt{post} directory.
+The \texttt{data} directory, initially empty, holds the raw data files and runtime information generated \deleted{by ODT}, as well as post-processed data files generated from within the \texttt{post} directory.
 Finally, the \texttt{docs} directory contains documentation optionally generated by Doxygen \cite{vanHeesch_2018} during the build process.
 
-\subsubsection{Building ODT}
+\subsubsection{Building \deleted{ODT} \added{the ODT code}}
 
-The ODT build process is automated with CMake.
+The ODT \added{code} build process is automated with CMake.
 The user navigates to the \texttt{build} directory and edits the CMake configuration file.
@@
 If it has not yet been installed, it must be built and installed at this point.
-For convenience, the ODT package automates this process.
+For convenience, the ODT \added{code} package automates this process.
 YAML need only be installed once for a given instance of the ODT package.
@@
 
-User-modified input files are located within the \texttt{input} directory, which contains subdirectories that correspond to various case types that can be run with ODT.
+User-modified input files are located within the \texttt{input} directory, which contains subdirectories that correspond to various case types that can be run \deleted{with ODT}.
 At minimum, a case's subdirectory must contain an \texttt{input.yaml} file, but may contain other files, or subfolders with supplementary information.
@@
 For cases in which a chemical mechanism is not required, the \texttt{not\textunderscore used.xml} mechanism file is specified in \texttt{input.yaml}.
-Note that the chemical mechanism chosen for the case and specified in the input file must match the mechanism specified in the CMake configuration file during the ODT build process.
+Note that the chemical mechanism chosen for the case and specified in the input file must match the mechanism specified in the CMake configuration file during the \deleted{ODT} build process.
 
@@
 
-\subsubsection{Running ODT}
+\subsubsection{Running \deleted{ODT} \added{the ODT code}}
 
@@
 
+As part of the post-processing tools, there is a \texttt{post/tools} directory that contains two files: \texttt{data\_py.py} and \texttt{data\_tools.py}.
+The first of these can be used to convert the text data files generated during a run into binary numpy files.
+This can reduce both the number of data files and the file sizes.
+The number of files is reduced since all code realizations at a given output time are saved in the same binary file.
+The \texttt{data\_tools.py} file is a module that contains a number of functions for processing the data files, such as functions to
+%
+\begin{itemize}
+    \item get the data from a given realization,
+    \item return the number of realizations,
+    \item get a list of the variable names in the data files,
+    \item compute axial locations in the spatial ODT formulation,
+    \item query a parameter from the input file,
+    \item return the stoichiometric mixture fraction for combustion/mixing problems, and
+    \item compute the domain bounds.
+\end{itemize}
+%
+In addition, a few functions are provided for doing interpolation/extrapolation, and computing probability denisity functions (PDFs), and weighted PDFs.
+Many of these functions take an argument that is a dictionary of case-specific information, such as the case name and paths for key directories.
+This dictionary is set in the post-processing driver script based only on the user-specified case name.
+
 % reference video that we will eventually make?
@@
 
-ODT is uniquely suited to reacting flow simulations.
+\deleted{ODT} \added{The ODT model} is uniquely suited to reacting flow simulations.
 Here, we present illustrative ODT simulation results of a round, turbulent jet flame based on and compared to the experimental DLR-A flame of Meier et al.
@@
 
-Previous ODT studies of turbulent jet flames have used the temporal planar formulation, but the spatial cylindrical formulation developed recently \cite{Lignell_2018} more closely matches the experimental configuration.
+Previous ODT \deleted{studies} \added{simulations} of turbulent jet flames have used the temporal planar formulation, but the spatial cylindrical formulation developed recently \cite{Lignell_2018} more closely matches the experimental configuration.
 This simulation uses the experimentally reported velocity profiles and jet dimensions.
@@
 Figure~\ref{fig:dlr_example_results} displays the simulation results: axial mean and centerline values for (a) axial velocity $v$, (b) mixture fraction $\xi$, and (c) temperature $T$.
-The ODT results track the experimental data well for all three variables.
+The ODT \added{simulation} results track the experimental data well for all three variables.
 The centerline temperature peaks about 100 K above the experimental data, but this small difference can be attributed to thermal radiation (which was neglected in this simulation) and the assumption that reactions proceed to the products of complete combustion rather than their equilibrium state.
@@
 Alternative formulations are used for fixed grids.
-The code presented here reduces these barriers by providing an open-source, well-documented, modularly styled code that can be used directly or modified to suit particular research goals.
+The \deleted{code} \added{ODT code implementation} presented here reduces these barriers by providing an open-source, well-documented, modularly styled code that can be used directly or modified to suit particular research goals.
 Its structure facilitates addressing new research questions, such as soot-flame-radiation-chemistry interactions, multi-phase reacting flows using Lagrangian particle models (such as diesel sprays), and coupled near-wall heat and momentum transfer.
@@
 
+%\bibliographystyle{elsarticle-num} 
+%\bibliography{references}
+
 \begin{thebibliography}{10}
@@
   turbulence and direct numerical simulations of soot formation and transport
-  in a nonpremixed ethylene jet flame 35~(2) (2015) 1199--1206.
+  in a nonpremixed ethylene jet flame, Proceedings of the Combustion Institute
+  35~(2) (2015) 1199--1206.
 \newblock \href {http://dx.doi.org/10.1016/j.proci.2014.05.046}
@@
   numerical comparison of precipitating turbulent flows between large-eddy
-  simulation and one-dimensional turbulence 61~(10) (2015) 3185--3197.
+  simulation and one-dimensional turbulence, AIChE Journal 61~(10) (2015)
+  3185--3197.
 \newblock \href {http://dx.doi.org/10.1002/aic.14870}
@@
 A.~R. Kerstein, One-dimensional turbulence: model formulation and application
-  to homogeneous turbulence, shear flows, and buoyant stratified flows 392
-  (1999) 277--334.
+  to homogeneous turbulence, shear flows, and buoyant stratified flows, Journal
+  of Fluid Mechanics 392 (1999) 277--334.
 \newblock \href {http://dx.doi.org/10.1017/S0022112099005376}
@@
 A.~R. Kerstein, T.~D. Dreeben, Prediction of turbulent free shear flow
-  statistics using a simple stochastic model 12~(2) (2000) 418--424.
+  statistics using a simple stochastic model, Physics of Fluids 12~(2) (2000)
+  418--424.
 \newblock \href {http://dx.doi.org/10.1063/1.870319}
@@
 A.~R. Kerstein, W.~T. Ashurst, S.~Wunsch, V.~Nilsen, One-dimensional
-  turbulence: vector formulation and application to free shear flows 447 (2001)
-  85--109.
+  turbulence: vector formulation and application to free shear flows, Journal
+  of Fluid Mechanics 447 (2001) 85--109.
 \newblock \href {http://dx.doi.org/10.1017/S0022112001005778}
@@
   turbulence' simulation of turbulent jet diffusion flames: model formulation
-  and illustrative applications 125~(3) (2001) 1083--1105.
+  and illustrative applications, Combustion and Flame 125~(3) (2001)
+  1083--1105.
 \newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00228-0}
@@
   kinetics in turbulent
-  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2 }flames 5~(4)
-  (2001) 669--697.
+  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2 }flames,
+  Combustion Theory and Modelling 5~(4) (2001) 669--697.
 \newblock \href {http://dx.doi.org/10.1088/1364-7830/5/4/309}
@@
   turbulent {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2} jet
-  flames 174~(5-6) (2002) 35--66.
+  flames, Combustion Science and Technology 174~(5-6) (2002) 35--66.
 \newblock \href {http://dx.doi.org/10.1080/713713031}
@@
 D.~O. Lignell, D.~S. Rappleye, One-dimensional-turbulence simulation of flame
-  extinction and reignition in planar ethylene jet flames 159~(9) (2012)
-  2930--2943.
+  extinction and reignition in planar ethylene jet flames, Combustion and Flame
+  159~(9) (2012) 2930--2943.
 \newblock \href {http://dx.doi.org/10.1016/j.combustflame.2012.03.018}
@@
   numerical simulations of {CO}/{H}\textsubscript{2 }jets with extinction and
-  reignition 33~(1) (2011) 1515--1522.
+  reignition, Proceedings of the Combustion Institute 33~(1) (2011) 1515--1522.
 \newblock \href {http://dx.doi.org/10.1016/j.proci.2010.06.127}
@@
   {DNS} for ignition occurrence in turbulent premixed jet combustion:
-  safety-relevant applications 231~(10) (2017) 1709--1735.
+  safety-relevant applications, Zeitschrift fur Physikalische Chemie 231~(10)
+  (2017) 1709--1735.
 \newblock \href {http://dx.doi.org/10.1515/zpch-2016-0902}
@@
 B.~Goshayeshi, J.~C. Sutherland, Prediction of oxy-coal flame stand-off using
-  high-fidelity thermochemical models and the one-dimensional turbulence model
-  35~(3) (2015) 2829--2837.
+  high-fidelity thermochemical models and the one-dimensional turbulence model,
+  Proceedings of the Combustion Institute 35~(3) (2015) 2829--2837.
 \newblock \href {http://dx.doi.org/10.1016/j.proci.2014.07.003}
@@
   One-dimensional turbulence modeling of a turbulent counterflow flame with
-  comparison to {DNS} 162~(8) (2015) 2999--3015.
+  comparison to {DNS}, Combustion and Flame 162~(8) (2015) 2999--3015.
 \newblock \href {http://dx.doi.org/10.1016/j.combustflame.2015.05.010}
@@
   Kerstein, R.~S. Hintze, Simulation of ethylene wall fires using the
-  spatially-evolving one-dimensional turbulence model 52~(1) (2016) 167--196.
+  spatially-evolving one-dimensional turbulence model, Fire Technology 52~(1)
+  (2016) 167--196.
 \newblock \href {http://dx.doi.org/10.1007/s10694-014-0441-2}
@@
   Ashurst, A spatially developing one-dimensional turbulence ({ODT}) study of
-  soot and enthalpy evolution in meter-scale buoyant turbulent flames 182~(1)
-  (2010) 60--101.
+  soot and enthalpy evolution in meter-scale buoyant turbulent flames,
+  Combustion Science and Technology 182~(1) (2010) 60--101.
 \newblock \href {http://dx.doi.org/10.1080/00102200903297003}
@@
 G.~Sun, J.~C. Hewson, D.~O. Lignell, Evaluation of stochastic particle
-  dispersion modeling in turbulent round jets 89 (2017) 108--122.
+  dispersion modeling in turbulent round jets, International Journal of
+  Multiphase Flow 89 (2017) 108--122.
 \newblock \href {http://dx.doi.org/10.1016/j.ijmultiphaseflow.2016.10.005}
@@
 J.~R. Schmidt, J.~O.~L. Wendt, A.~R. Kerstein, Non-equilibrium wall deposition
-  of inertial particles in turbulent flow 137~(2) (2009) 233--257.
+  of inertial particles in turbulent flow, Journal of Statistical Physics
+  137~(2) (2009) 233--257.
 \newblock \href {http://dx.doi.org/10.1007/s10955-009-9844-8}
@@
 G.~Sun, D.~O. Lignell, J.~C. Hewson, C.~R. Gin, Particle dispersion in
-  homogeneous turbulence using the one-dimensional turbulence model 26~(10)
-  (2014) 103301.
+  homogeneous turbulence using the one-dimensional turbulence model, Physics of
+  Fluids 26~(10) (2014) 103301.
 \newblock \href {http://dx.doi.org/10.1063/1.4896555}
@@
 S.~Cao, T.~Echekki, A low-dimensional stochastic closure model for combustion
-  large-eddy simulation 9.
+  large-eddy simulation, Journal of Turbulence 9.
 \newblock \href {http://dx.doi.org/10.1080/14685240701790714}
@@
 R.~C. Schmidt, A.~R. Kerstein, S.~Wunsch, V.~Nilsen, Near-wall {LES} closure
-  based on one-dimensional turbulence modeling 186~(1) (2003) 317--355.
+  based on one-dimensional turbulence modeling, Journal of Computational
+  Physics 186~(1) (2003) 317--355.
 \newblock \href {http://dx.doi.org/10.1016/S0021-9991(03)00071-8}
@@
 R.~C. Schmidt, A.~R. Kerstein, R.~McDermott, {ODTLES}: A multi-scale model for
-  3{D} turbulent flow based on one-dimensional turbulence modeling 199~(13-16)
-  (2010) 865--880.
+  3{D} turbulent flow based on one-dimensional turbulence modeling, Computer
+  Methods in Applied Mechanics and Engineering 199~(13-16) (2010) 865--880.
 \newblock \href {http://dx.doi.org/10.1016/j.cma.2008.05.028}
@@
 E.~Gonzalez-Juez, A.~R. Kerstein, D.~O. Lignell, Fluxes across double-diffusive
-  interfaces: a one-dimensional-turbulence study 677 (2011) 218--254.
+  interfaces: a one-dimensional-turbulence study, Journal of Fluid Mechanics
+  677 (2011) 218--254.
 \newblock \href {http://dx.doi.org/10.1017/jfm.2011.78}
@@
 E.~Gonzalez-Juez, A.~R. Kerstein, D.~O. Lignell, Reactive {R}ayleigh--{T}aylor
-  turbulent mixing: a one-dimensional-turbulence study 107~(5) (2013) 506--525.
+  turbulent mixing: a one-dimensional-turbulence study, Geophysical {\&}
+  Astrophysical Fluid Dynamics 107~(5) (2013) 506--525.
 \newblock \href {http://dx.doi.org/10.1080/03091929.2012.736504}
@@
 S.~Wunsch, A.~R. Kerstein, A model for layer formation in stably stratified
-  turbulence 13~(3) (2001) 702--712.
+  turbulence, Physics of Fluids 13~(3) (2001) 702--712.
 \newblock \href {http://dx.doi.org/10.1063/1.1344182}
@@
   H.~Schmidt, M.~Fistler, M.~Oevermann, One-dimensional turbulence modeling for
-  cylindrical and spherical flows: model formulation and application 32~(4)
-  (2018) 495--520.
+  cylindrical and spherical flows: model formulation and application,
+  Theoretical and Computational Fluid Dynamics 32~(4) (2018) 495--520.
 \newblock \href {http://dx.doi.org/10.1007/s00162-018-0465-1}
@@
 W.~T. Ashurst, A.~R. Kerstein, One-dimensional turbulence: variable-density
-  formulation and application to mixing layers 17~(2).
+  formulation and application to mixing layers, Physics of Fluids 17~(2).
 \newblock \href {http://dx.doi.org/10.1063/1.1847413}
@@
 D.~O. Lignell, A.~R. Kerstein, G.~Sun, E.~I. Monson, Mesh adaption for
-  efficient multiscale implementation of one-dimensional turbulence 27~(3-4)
-  (2013) 273--295.
+  efficient multiscale implementation of one-dimensional turbulence,
+  Theoretical and Computational Fluid Dynamics 27~(3-4) (2013) 273--295.
 \newblock \href {http://dx.doi.org/10.1007/s00162-012-0267-9}
@@
 \bibitem{Strang_1968}
-G.~Strang, On the construction and comparison of difference schemes 5~(3)
-  (1968) 506--517.
+G.~Strang, On the construction and comparison of difference schemes, SIAM
+  Journal on Numerical Analysis 5~(3) (1968) 506--517.
 \newblock \href {http://dx.doi.org/10.1137/0705041}
@@
   {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2 }jet diffusion
-  flame: experimental techniques and turbulence--chemistry interaction} 123~(3)
-  (2000) 326--343.
+  flame: experimental techniques and turbulence--chemistry interaction},
+  Combustion and Flame 123~(3) (2000) 326--343.
 \newblock \href {http://dx.doi.org/10.1016/S0010-2180(00)00171-1}
@@
 H.~Pitsch, Unsteady flamelet modeling of differential diffusion in turbulent
-  jet diffusion flames 123~(3) (2000) 358--374.
+  jet diffusion flames, Combustion and Flame 123~(3) (2000) 358--374.
 \newblock \href {http://dx.doi.org/10.1016/S0010-2180(00)00135-8}
@@
 R.~P. Lindstedt, H.~Ozarovsky, Joint scalar transported {PDF} modeling of
-  nonpiloted turbulent diffusion flames 143~(4) (2005) 471--490.
+  nonpiloted turbulent diffusion flames, Combustion and Flame 143~(4) (2005)
+  471--490.
 \newblock \href {http://dx.doi.org/10.1016/j.combustflame.2005.08.030}
@@
   modeling of a turbulent
-  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2} jet flame
-  33~(1) (2011) 1319--1330.
+  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2} jet flame,
+  Proceedings of the Combustion Institute 33~(1) (2011) 1319--1330.
 \newblock \href {http://dx.doi.org/10.1016/j.proci.2010.08.004}
@@
 M.~Fairweather, R.~M. Woolley, First-order conditional moment closure modeling
-  of turbulent, nonpremixed methane flames 138~(1-2) (2004) 3--19.
+  of turbulent, nonpremixed methane flames, Combustion and Flame 138~(1-2)
+  (2004) 3--19.
 \newblock \href {http://dx.doi.org/10.1016/j.combustflame.2004.03.001}
@@
 K.~W. Lee, D.~H. Choi, Prediction of {NO} in turbulent diffusion flames using
-  eulerian particle flamelet model 12~(5) (2008) 905--927.
+  eulerian particle flamelet model, Combustion Theory and Modelling 12~(5)
+  (2008) 905--927.
 \newblock \href {http://dx.doi.org/10.1080/13647830802094351}
@@
 K.~W. Lee, D.~H. Choi, Analysis of {NO} formation in high temperature diluted
-  air combustion in a coaxial jet flame using an unsteady flamelet model
-  52~(5-6) (2009) 1412--1420.
+  air combustion in a coaxial jet flame using an unsteady flamelet model,
+  International Journal of Heat and Mass Transfer 52~(5-6) (2009) 1412--1420.
 \newblock \href {http://dx.doi.org/10.1016/j.ijheatmasstransfer.2008.08.015}
@@
   combustion, Progress in Energy and Combustion Science 10 (1984) 319--339.
-\newblock \href {https://doi.org/10.1016/0360-1285(84)90114-X}
-  {\path{doi:10.1016/0360-1285(84)90114-X}}.
 

### 2020-11-30 submissions/revision_2/manuscript.tex
revision 2

--- 2020-11-30 submissions/differences_initial_vs_revision_2/manuscript.tex
@@
 
-%\usepackage{soul}
-%\usepackage{color}
-\usepackage{changes}
-\colorlet{Changes@Color}{yellow}
-
 \journal{SoftwareX}
@@
 %
-    One-dimensional turbulence (ODT) is an accurate and computationally efficient \deleted{technique} \added{model} for \deleted{modeling} \added{simulating} turbulent flows.
+One-dimensional turbulence (ODT) is an accurate and computationally efficient model for simulating turbulent flows.
 ODT has been applied to a wide range of flow problems including reaction, multiphase, differential diffusion, heat release, buoyancy, and wall flows.
@@
 We present a modern, open-source, object-oriented C++ implementation of ODT.
-\deleted{This code can be used as a starting point to understand, apply, and extend the ODT model, enabling its further application to turbulent flow research.} \added{The code described here and made available online can be used as a starting point to understand, apply, and extend the ODT model, enabling its further application to turbulent flow research.}
+The code described here and made available online can be used as a starting point to understand, apply, and extend the ODT model, enabling its further application to turbulent flow research.
 %
@@
 ODT has also served to complement LES through subgrid modeling studies \cite{Cao_2008,Schmidt_2003,Schmidt_2010} and has been applied to various other flow configurations such as double-diffusive interfaces \cite{GonzalezJuez_2011}, Rayleigh-Taylor mixing \cite{GonzalezJuez_2013}, and stratified turbulence \cite{Wunsch_2001}.
-Most recently, \deleted{the ODT code was} \added{ODT implementations have been} extended to include cylindrical and spherical coordinate systems \cite{Lignell_2018,Klein_2018,Klein_2019}.
+Most recently, ODT implementations have been extended to include cylindrical and spherical coordinate systems \cite{Lignell_2018,Klein_2018,Klein_2019}.
 
-\deleted{During the recent implementation of the cylindrical and spherical model formulations, the ODT code was drastically overhauled and reorganized, resulting in its current configuration.
-} \added{Many of the references cited above make use of a particular software implementation of the ODT model, referred to here as the \emph{ODT code}.
-During the recent implementation of the cylindrical and spherical model formulations, this code was drastically overhauled and reorganized.} The ODT code presented here is a pared down version of the development code, representing the fundamental aspects of the ODT model and its most reliable functions.
+Many of the references cited above make use of a particular software implementation of the ODT model, referred to here as the \emph{ODT code}.
+During the recent implementation of the cylindrical and spherical model formulations, this code was drastically overhauled and reorganized.
+The ODT code presented here is a pared down version of the development code, representing the fundamental aspects of the ODT model and its most reliable functions.
 The example case in Section~\ref{sec:examples} is a representative sample of the ODT code's capabilities as it is presented here.
@@
 
-The ODT model \added{formulation} is described in detail in the literature~\cite{Kerstein_1999,Kerstein_2001,Ashurst_2005,Lignell_2018,Lignell_2013}; only a brief explanation will be given here.
+The ODT model formulation is described in detail in the literature~\cite{Kerstein_1999,Kerstein_2001,Ashurst_2005,Lignell_2018,Lignell_2013}; only a brief explanation will be given here.
 In ODT, turbulent advection is modeled with stochastic processes called eddy events, which punctuate the solution of unsteady, one-dimensional transport equations for mass, momentum, and enthalpy.
-The ODT code \added{implementation of the ODT model} uses a Lagrangian finite-volume formulation for diffusive advancement in which mass stays constant within each grid cell while cell volumes increase or decrease according to cell dilation via an adaptive mesh refinement~\cite{Lignell_2013}.
+The ODT code implementation of the ODT model uses a Lagrangian finite-volume formulation for diffusive advancement in which mass stays constant within each grid cell while cell volumes increase or decrease according to cell dilation via an adaptive mesh refinement~\cite{Lignell_2013}.
 
@@
 This section outlines the process a user goes through in order to successfully build the ODT code and run a simulation.
-The ODT \added{code} is a standalone, self-contained package, and users interact with its files primarily via the command line rather than a graphical interface.
+The ODT code is a standalone, self-contained package, and users interact with its files primarily via the command line rather than a graphical interface.
 For more details, please see the package documentation.
@@
 The \texttt{input} directory contains subdirectories corresponding to several possible case types, each populated with the appropriate input files.
-The \texttt{data} directory, initially empty, holds the raw data files and runtime information generated \deleted{by ODT}, as well as post-processed data files generated from within the \texttt{post} directory.
+The \texttt{data} directory, initially empty, holds the raw data files and runtime information generated, as well as post-processed data files generated from within the \texttt{post} directory.
 Finally, the \texttt{docs} directory contains documentation optionally generated by Doxygen \cite{vanHeesch_2018} during the build process.
 
-\subsubsection{Building \deleted{ODT} \added{the ODT code}}
+\subsubsection{Building the ODT code}
 
-The ODT \added{code} build process is automated with CMake.
+The ODT code build process is automated with CMake.
 The user navigates to the \texttt{build} directory and edits the CMake configuration file.
@@
 If it has not yet been installed, it must be built and installed at this point.
-For convenience, the ODT \added{code} package automates this process.
+For convenience, the ODT code package automates this process.
 YAML need only be installed once for a given instance of the ODT package.
@@
 
-User-modified input files are located within the \texttt{input} directory, which contains subdirectories that correspond to various case types that can be run \deleted{with ODT}.
+User-modified input files are located within the \texttt{input} directory, which contains subdirectories that correspond to various case types that can be run.
 At minimum, a case's subdirectory must contain an \texttt{input.yaml} file, but may contain other files, or subfolders with supplementary information.
@@
 For cases in which a chemical mechanism is not required, the \texttt{not\textunderscore used.xml} mechanism file is specified in \texttt{input.yaml}.
-Note that the chemical mechanism chosen for the case and specified in the input file must match the mechanism specified in the CMake configuration file during the \deleted{ODT} build process.
+Note that the chemical mechanism chosen for the case and specified in the input file must match the mechanism specified in the CMake configuration file during the build process.
 
@@
 
-\subsubsection{Running \deleted{ODT} \added{the ODT code}}
+\subsubsection{Running the ODT code}
 
@@
 
-\deleted{ODT} \added{The ODT model} is uniquely suited to reacting flow simulations.
+The ODT model is uniquely suited to reacting flow simulations.
 Here, we present illustrative ODT simulation results of a round, turbulent jet flame based on and compared to the experimental DLR-A flame of Meier et al.
@@
 
-Previous ODT \deleted{studies} \added{simulations} of turbulent jet flames have used the temporal planar formulation, but the spatial cylindrical formulation developed recently \cite{Lignell_2018} more closely matches the experimental configuration.
+Previous ODT simulations of turbulent jet flames have used the temporal planar formulation, but the spatial cylindrical formulation developed recently \cite{Lignell_2018} more closely matches the experimental configuration.
 This simulation uses the experimentally reported velocity profiles and jet dimensions.
@@
 Figure~\ref{fig:dlr_example_results} displays the simulation results: axial mean and centerline values for (a) axial velocity $v$, (b) mixture fraction $\xi$, and (c) temperature $T$.
-The ODT \added{simulation} results track the experimental data well for all three variables.
+The ODT simulation results track the experimental data well for all three variables.
 The centerline temperature peaks about 100 K above the experimental data, but this small difference can be attributed to thermal radiation (which was neglected in this simulation) and the assumption that reactions proceed to the products of complete combustion rather than their equilibrium state.
@@
 Alternative formulations are used for fixed grids.
-The \deleted{code} \added{ODT code implementation} presented here reduces these barriers by providing an open-source, well-documented, modularly styled code that can be used directly or modified to suit particular research goals.
+The ODT code implementation presented here reduces these barriers by providing an open-source, well-documented, modularly styled code that can be used directly or modified to suit particular research goals.
 Its structure facilitates addressing new research questions, such as soot-flame-radiation-chemistry interactions, multi-phase reacting flows using Lagrangian particle models (such as diesel sprays), and coupled near-wall heat and momentum transfer.
